### 2020-05-27 paper.tex
Abstract

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{pgfplots}
\pgfplotsset{compat=1.9}

\pgfplotsset{
    % #1: index in the group(0,1,2,...)
    % #2: number of plots of that group
    bar group size/.style 2 args={
        /pgf/bar shift={%
                % total width = n*w + (n-1)*skip
                % -> subtract half for centering
                -0.5*(#2*\pgfplotbarwidth + (#2-1)*\pgfkeysvalueof{/pgfplots/bar group skip})  + 
                % the '0.5*w' is for centering
                (.5+#1)*\pgfplotbarwidth + #1*\pgfkeysvalueof{/pgfplots/bar group skip}},%
    },
    bar group skip/.initial=2pt,
    plot 0/.style={blue,fill=blue!30!white,mark=none},%
    plot 1/.style={red,fill=red!30!white,mark=none},%
    plot 2/.style={brown!60!black,fill=brown!30!white,mark=none},%
    plot 3/.style={brown!60!black,fill=brown!30!white,mark=none},%
}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\makeatletter
\newcommand\fs@norules{\def\@fs@cfont{\bfseries}\let\@fs@capt\floatc@ruled
    \def\@fs@pre{}%
    \def\@fs@post{}%
    \def\@fs@mid{\kern3pt}%
    \let\@fs@iftopcapt\iftrue}
\makeatother

\tikzstyle{startstop} = [ellipse,minimum width=2cm, minimum height=1cm, text centered, draw=black, fill=white]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=2cm, minimum height=1cm, text centered, draw=black, fill=white]
\tikzstyle{process} = [rectangle, minimum width=1cm, minimum height=1cm, text centered, draw=black, fill=white]
\tikzstyle{decision} = [diamond, minimum width=2cm, minimum height=1cm, text centered, draw=black, fill=white]
\tikzstyle{arrow} = [thick,->,>=stealth]

\newcommand\T{\rule{0pt}{2.6ex}}       % Top strut
\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Improved Global Routing Using A-Star Algorithm\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AUTHORS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author{\IEEEauthorblockN{AbdElrahman Elshafei\IEEEauthorrefmark{1}, Hossam Ahmed\IEEEauthorrefmark{2}, Mahmoud Mohamed\IEEEauthorrefmark{3} and Muhanad Atef\IEEEauthorrefmark{4}}
\IEEEauthorblockA{Computer Engineering Dept.,
Faculty of Engineering, Cairo University\\
Cairo, Egypt\\
\IEEEauthorrefmark{1}abdelrahman.elshafei98@gmail.com,
\IEEEauthorrefmark{2}hossamahmed201515@gmail.com,
\IEEEauthorrefmark{3}mmmacmp@gmail.com,
\IEEEauthorrefmark{4}muhanad.atef23@gmail.com}}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
    In this paper we want to improve routing by improving global routing, this can be done by using A-Star algorithm, which will reduce time taken in this process and achieve the minimum wire length, many comparisons are taken in this paper with different algorithms to find the optimum algorithm to be used to achieve both minimum wire length and minimum time taken. From the comparisons of the paper we can find that using any algorithm is a trade off as when we decrease time taken, the wire length is increased and vice versa, so we cannot find an algorithm which is better from the other algorithms in general but we can say that using A-Star algorithm is a good approach to be used in global routing as it decreases the routing time however it is not the the best achieveable time but it is better than many other algorithms, and it is the best algorithm to achieve the minimum wire length with this complexity.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% KEY WORDS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{IEEEkeywords}
VLSI Routing, Global Routing, Routing Algorithms, Fast Global Routing, Fast Routing Algorithms, Routing Algoritms Comparisons.
\end{IEEEkeywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% INTRODUCTION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Scheduling is a crucial part of many real-time applications such as scheduling airlines and railways communications, product manufacturing processes, data packets routing in computer networks and pipe networks. Operating systems multiprocessing environments are no different from those mediums mentioned, where processes compete over CPU utilization. This brought to existence the need for scheduling algorithms to justly assign processes to available CPUs in favour of optimizing performance measures, in particular, to maximize overall CPU utilization and throughput, and to minimize response time, waiting time and turnaround time. A schedular could be preemptive where it can temporarily interrupt a process without its cooperation and assign the CPU resources to a different process with the intention to assign them back to the former process, such operation is called context switching, or it could be non-preemptive (cooperative) by not being able to context switch between processes. Various preemptive and non-preemptive scheduling disciplines exist such as, first come, first serve (FCFS), shortest job first (SJF), shortest remaining time first (SRTF), round-robin (RR), multilevel queue and multilevel feedback queue. In FCFS, processes are non-preemptively executed according to their arrival time. In SJF, the CPU is assigned to the process with the smallest burst time. SRTF is a preemptive version of SJF where at each iteration, the process with the least remaining burst time takes control of the CPU. Round-robin preemptively assigns the CPU to each process in the ready queue for a static amount of time called quantum and executes them in an FCFS fashion. Multilevel queue algorithm partitions the ready queue into several queues to which processes are perpetually assigned and are executed according to another scheduling algorithm (e.g. RR). Processes cannot move from one queue to another. However, in a multilevel feedback queue algorithm, processes that don't terminate in one queue, due to having CPU burst time more than the time quantum assigned to their particular queue, are shifted to a lower priority queue. Due to the fact that long processes eventually sink to the lowest priority queue, they are conventionally carried out using FCFS to prevent starvation. Several papers discuss different methods to optimize the algorithms mentioned, each come with their set of advantages and drawbacks. One of many is \cite{b2}, whose approach achieves better average response time but at the cost of hindering the scheduling process due to recalculating time quantum for each queue using a recurrent neural network. In this paper, we attempted to implement the best of all worlds.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RELATED WORK %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Related Work}

Several papers proposed various types of approaches to improve the overall efficiency of the multilevel feedback queue scheduling algorithm. The chosen quantum time for each queue plays a major role. Hence, it is essential to choose a proper method to compute the time quantum value to minimize response time and maximize overall performance. In \cite{b2}, an algorithm is introduced for minimizing the response time. In this algorithm, a Recurrent Neural Network (RNN) is used to determine both the number of queues and the optimized time quantum value for each queue. The RNN generates an effective model to compute the time quantum value. Their proposed intelligent version of the MLFQ offers good results, however, it suffers from a few drawbacks, the first being the direct proportionality of its network learning time and the amount of input data, and the second is the possibility of experiencing initial overhead at the first iterations of the algorithm. Our approach proposes an improved version of MLFQ that utilizes an altered version of RR named shortest remaining burst round-robin (SRBRR) introduced in \cite{b3} which avoids the cost of learning time and overhead time in \cite{b2}. Regarding the various approaches to improve the MLFQ algorithm, those attempts dealt with starvation by assigning different quantum values to the ready queues depending on their priority. Our approach also deals with starvation by boosting processes from lower priority queues to higher ones according to certain criteria.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROPOSED APPROACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Proposed Approach}

For a multilevel feedback queue scheduling algorithm, three parameters are considered. The first is the chosen scheduling algorithm for each queue, especially the last queue as its scheduling algorithm is expected to treat starvation. The second is the criteria according to which a process is promoted, this technique is also known as Aging. The third is the criteria according to which a process is demoted. In our proposed algorithm, there are 5 queues sorted in ascending order in line with their priority number, 1 being the highest priority and 5 being the lowest. Each queue uses a modified version of the round-robin scheduling algorithm stated in \cite{b3}. In \cite{b3}, processes are sorted in ascending order according to their burst time and are assigned a time quantum that equals the median burst time of those processes. This algorithm provides better turnaround time and waiting time than the standard static quantum RR algorithm whose quantum, if set too short, leads to many context switches and, if set too long, morphs the algorithm into an FCFS algorithm. The proposed alteration on the stated algorithm in \cite{b3} is that each queue quantum time equals the median burst time multiplied by a factor matching the queue number. Hence, the gradual increase of quantum time as priority decreases. For clarification, a queue with priority equal $2$ has the following processes denoted by their burst time: $100$, $300$, $550$, $600$, $620$, $700$, $720$, $900$ and $1200$, the median value is $620$, since we are in a queue whose priority equals $2$, therefore the quantum slice value according to the proposed approach equals $1240$ as in $620 * 2$. If processes of a certain queue didn't terminate after assigning the quantum time value, they are shifted to the next lower priority queue. After introducing new processes into a queue, the quantum time slice is recalculated. Processes age whenever they are in a queue whose priority is one less than that currently getting scheduled and satisfies the following inequality:
\begin{equation}
\frac{waiting \; time \; of \; P}{burst \; time \; of \; P} >= 1\label{eq1}
\end{equation}

Those procedures are repeated for all the generated queues until all processes reach the lowest priority queue where they are rescheduled until their completion.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FLOWCHART %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Pseudocode Flowchart of the Proposed Approach}
\begin{tikzpicture}[node distance=2.2cm]

    \node (start) [startstop] {Start};
    \node (in1) [io, below of=start, text width = 2cm] {Read Processes Data};
    \node (dec1) [decision, below of=in1, text width = 2cm, yshift=-1cm] {All processes are finished};
    \node (pro1) [process, below of=dec1, text width= 3cm, yshift = -1cm] {Iterate on queues $Q$};
    \node (pro2) [process, below of=pro1, text width = 3cm] {Assign eligable processes to the current queue};
    \node (out1) [io, left of=dec1, text width = 2cm, xshift= -2cm] {Print avg. waiting time, avg. turnaround time, throughput};
    \node (end) [startstop, below of=out1, yshift=-1cm] {End};
    \node (dec2) [decision, below of=pro2, text width = 2cm, yshift=-2cm] {A process $P$ in the subsequent queue is boostable};

    \node (pro3) [process, left of=dec2, text width= 3cm, xshift= -2.5cm] {Promote $P$ to current queue};
    \node (pro4) [process, below of=dec2, text width= 3cm, yshift=-2.2cm] {Calculate the quantum time value $\phi$};
    \node (pro5) [process, below of=pro4, text width= 3cm] {Schedule processes in current queue};

    \draw [arrow] (start) -- (in1);
    \draw [arrow] (in1) -- (dec1);
    % \draw [arrow] (pro1) -- (dec1);
    \draw [arrow] (dec1) -- node[anchor=west, above] {Yes} (out1);
    \draw [arrow] (out1) -- (end);
    \draw [arrow] (dec1) -- node[anchor=south, left] {No} (pro1);
    \draw [arrow] (pro1) -- (pro2);
    \draw [arrow] (pro2) -- (dec2);
    \draw [arrow] (dec2) -- node[anchor=west,above] {Yes} (pro3);
    \draw [arrow] (pro3.north) -- ++ (0,3.7) -- ++ (3.1,0);
    \draw [arrow] (dec2) -- node[anchor=south, left] {No} (pro4);
    \draw [arrow] (pro4) -- (pro5);
    \draw [arrow] (pro5.east) -- ++ (1.2,0) -- ++(0,16.2) -- ++(-1.3,0);
    \end{tikzpicture}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALGORITHM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Proposed Algorithm}
% \floatstyle{norules}
\restylefloat{algorithm}
\begin{algorithm}[H]
    \caption{Developed Multilevel Feedback Queue Scheduling Algorithm}
    \hspace*{\algorithmicindent} \textbf{Input:} Number of processes $n$, processes priority $\alpha$\\
    \hspace*{\algorithmicindent} burst time values $\beta$, arrival time values $\sigma$, \\
    \hspace*{\algorithmicindent} context switching cost $\epsilon$\\
    \hspace*{\algorithmicindent} \textbf{Output:} Average turnaround time, average waiting time,\\
    \hspace*{\algorithmicindent} throughput
    \begin{algorithmic}[1]
    \Procedure {DMLFQ}{}
    % Return  Average waiting time, throughput
    \Statex Declaration and Initialisation:
    \State Queue $Q_{i}$ where $i \in \{1, 2, 3, 4, 5\}$
    \State Turnaround time values $\tau$
    \State Finish time values $\lambda$
    \State Waiting time values $\theta$
    \State Remaining time values $\mu = \beta$
    \State Quantum time value $\phi$
    \State Number of context switches $\delta$
        \State$time = 0$
        \While{$\exists P \in Q$}
            \For{$i = 1$ to $5$}
                \For{$j = 1$ to $n$}
                    \If{$\sigma_{j} <= time$ and $\alpha_{j}$ equals $i$}
                        \State \textit{\textbf{Assign}} $P_{j}$ to $Q_{i}$
                    \EndIf
                    \State $waitingTime = time - \sigma_{j}$
                    \If{$i < 5$ and $waitingTime/\mu_{j} >= 1$ and $\alpha_{j}$ equals $i + 1$ and  $\sigma_{j} <= time$}
                        \State \textit{\textbf{Assign}} $P_{j}$ to $Q_{i}$
                    \EndIf
                \EndFor
                \State Sort $Q_{i}$ in ascending order according to remaining time values
                \State $\phi = median\; value\; of\; Q_{i} * i$
                \algrenewcommand\algorithmicfor{\textbf{foreach}}
                \For{$P_{j} \in Q_{i}$}
                    \If{$\mu_{j} <= \phi$}
                        \State $time = time + \mu_{j}$
                        \State $\lambda_{j} = time$
                        \State \textit{\textbf{Remove}} $P_{j}$ from $Q_{i}$
                    \Else
                        \State $time = time + \phi$
                        \State $\mu_{j} = \mu_{j} - \phi$
                        \If{$i < 5$}
                            \State $\alpha_{j} = \alpha_{j} + 1$
                        \EndIf
                    \EndIf
                    \If{Previous process $\neq P_{j}$}
                        \State $time = time + \epsilon$
                        \State $\delta = \delta + 1$
                    \EndIf
                \EndFor
                \algrenewcommand\algorithmicfor{\textbf{for}}
            \EndFor
        \EndWhile
        \For{$i = 1$ to $n$}
            $\tau_{j} = \lambda_{j} - \sigma_{j}$, $\theta_{j} = \tau_{j} - \beta_{j}$
        \EndFor
        \State \textbf{return} average of $\theta$, average of $\tau$, $n/time$
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EXPERIMENTAL ANALYSIS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experimental Analysis}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ASSUMPTIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Assumptions}

The proposed scheduling algorithm is software simulated using a Python script which simulates scheduling independent CPU-bound processes on a single processor environment which guarantees that no more than a single process is getting scheduled at any arbitrary moment. Each process is assumed to have its own predetermined burst time, arrival time and the queue to which each one belongs. The proposed approach is non-preemptive. For the sake of giving an example, if a process was lately introduced to a queue denoted by $Q_{i}$ prior to the current queue getting scheduled, it won't get scheduled until the current queue, its subsequent queues and the queues prior to $Q_{i}$ get scheduled.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% I/O %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Experimental Scheme}

On one hand, the input arguments to the proposed algorithm implementation are the number of processes to be scheduled, their burst time, their arrival time and the queue where each one belongs. On the other hand, output parameters are the average waiting time, average turnaround time and throughput. The following equations are used to calculate the previously mentioned output parameters:

\begin{equation}
    Average\; Waiting\; Time =  \frac{Total \; Waiting \; Time}{Number \; of \; Processes} \label{eq2}
\end{equation}

\begin{equation}
    Average\; Turnaround\; Time =  \frac{Total \; Turnaround \; Time}{Number \; of \; Processes} \label{eq3}
\end{equation}

\begin{equation}
    Throughput =  \frac{Number \; of \; Executed \; Processes}{Total \; Execution \; Time} \label{eq4}
\end{equation}

% \vspace{4mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PERFORMANCE METRICS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Performance Metrics}

As a means to have a concrete, viable evaluation of either the proposed algorithm or any other scheduling algorithm, the output parameters are taken into consideration for analysis. Since the average waiting time indicates the average time that a  process had to starve for, therefore the lower the average waiting time is the better. The same principle applies to the average turnaround time and the number of context switches, as the former implies the average time spent by the process since its arrival time to its completion and the latter costs time as the CPU is assigned back and forth between different processes. Contrarily to the prior metrics, the larger the throughput is the better as it indicates the number of processes that are completely executed per unit time.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SIMULATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Simulation}

For the sake of showcasing the proposed algorithm, a number of processes, their predetermined burst time values and their arrival time values are taken as input to the Python simulation script. Suppose that the input to the script is according to the following table:

\begin{table}[H]
    \caption{}
    \centering
     \begin{tabular}{||c c c c||} 
     \hline
     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
     \hline
     \hline
     1 & 0 & 60 & 1 \T \B \\ 
     \hline
     2 & 0 & 50 & 1 \T \B \\
     \hline
     3 & 0 & 40 & 2 \T \B \\
     \hline
     4 & 0 & 30 & 2 \T \B \\
     \hline
     5 & 0 & 10 & 3 \T \B \\ 
     \hline
     6 & 0 & 210 & 3 \T \B \\ 
     \hline
     7 & 0 & 200 & 3 \T \B \\ 
     \hline
     \end{tabular}
     \label{table1}
\end{table}

According to the proposed algorithm, the time quanta calculated are as follows:

\begin{table}[H]
    \caption{}
    \centering
     \begin{tabular}{||c c||} 
     \hline
     \textit{\textbf{Queue}} & \textit{\textbf{Quantum Value}} \T \B \\ 
     \hline
     \hline
     1 & 55 \T \B \\ 
     \hline
     2 & 40 \T \B \\
     \hline
     3 & 615 \T \B \\
     \hline
     4 & 0 \T \B \\
     \hline
     5 & 0 \T \B \\ 
     \hline
     \end{tabular}
\end{table}

All processes are sorted in ascending order according to their remaining time and are scheduled by assigning the time quantum calculated for their respective queue. The time spent scheduling a particular queue is the waiting time for its subsequent queues.

The scheduling process goes as follows:

\begin{figure}[H]
        \begin{center}
        \begin{tabular}{|c|c|}
         \hline
            $P_{2}$ & $P_{1}$\T\B\\ 
         \hline
        \end{tabular}
        \end{center}
        \begin{center}
            \begin{tabular}{c c c}
                   0 & 50 & 105\\ 
            \end{tabular}
        \end{center}
    \caption{$Q_{1}$ Gantt Chart}
\end{figure}

Considering that each process in $Q_{1}$ is assigned a quantum value of $50$, as we reach the last process in $Q_{1}$, the total time elapsed equals $105$, which happens to be the time that all the other processes in the subsequent queues had to wait for, hence the addition of their waiting time by a value of $105$ units of time.

\begin{figure}[H]
    \begin{center}
    \begin{tabular}{|c|c|c|c|}
     \hline
        $P_{1}$ & $P_{5}$ & $P_{4}$ & $P_{3}$\T\B\\ 
     \hline
    \end{tabular}
    \end{center}
    \begin{center}
        \begin{tabular}{c c c c c}
               105 & 110 & 120 & 150 & 190\\ 
        \end{tabular}
    \end{center}
\caption{$Q_{2}$ Gantt Chart}
\end{figure}

Even though $P_{5}$ is initially assigned to $Q_{3}$ as in Table \ref{table1}, it was promoted to $Q_{2}$ due to satisfying inequality (\ref{eq1}).

\begin{figure}[H]
    \begin{center}
    \begin{tabular}{|c|c|}
     \hline
        P7 & P6\T\B\\ 
     \hline
    \end{tabular}
    \end{center}
    \begin{center}
        \begin{tabular}{c c c}
               190 & 390 & 600\\ 
        \end{tabular}
    \end{center}
\caption{$Q_{3}$ Gantt Chart}
\end{figure}

Whenever processes reach the lowest queue precompletion, they are scheduled using the RR scheduling algorithm with a relatively large quantum time value which is in most cases similar to using the FCFS algorithm because, as the time quantum value of an RR algorithm tends to infinity which could practically be a very large number relative to the available processes remaining time values, the algorithm tends to morph into the FCFS algorithm. This procedure is iterated until all the processes are finished. Simulation results are shown in the table below:

\begin{table}[H]
    \caption{}
    \centering
     \begin{tabular}{||c c c||} 
     \hline
     \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}} & \textit{\textbf{Throughput}}\T \B \\ 
     \hline
     \hline
     230 & 144.3 & 0.011667 \T \B \\ 
     \hline
     \end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% COMPARISONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Performance Comparisons}

To assess the performance of the proposed algorithm implementation, multiple test cases are addressed and analyzed in seven different experiments. In each experiment, the output of the proposed algorithm implementation is compared to the output of another scheduling algorithm implementation addressed in a different paper, such as standard MLFQ algorithm with static quantum RR and other variants of MLFQ algorithms and RR algorithms.

\subsubsection{Experiment 1}

In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in \cite{b4}. The first uses a static version of the RR algorithm for scheduling each queue, while the second variant uses a dynamic version of the RR algorithm for doing so.

\begin{table}[H]
    \caption{Experiment 1 Input}
    \centering
     \begin{tabular}{||c c c c||} 
     \hline
     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
     \hline
     \hline
     1 & 1 & 25 & 1 \T \B \\ 
     \hline
     2 & 5 & 70 & 1 \T \B \\
     \hline
     3 & 6 & 84 & 1 \T \B \\
     \hline
     4 & 7 & 17 & 1 \T \B \\
     \hline
     5 & 8 & 35 & 1 \T \B \\ 
     \hline
     \end{tabular}
\end{table}

\begin{table}[H]
    \caption{Experiment 1 Results}
    \centering
    \begin{tabular}{||c c c||}
        \hline
        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
    \hline
    \hline
    \textbf{Proposed Algorithm} & 115 & 68.8 \T \B\\ \hline
    \textbf{Dynamic RR MLFQ} & 150.8 & 107.6\T \B\\ \hline
    \textbf{Static RR MLFQ} & 161.4 & 116.2 \T \B\\ \hline
     \end{tabular}
\end{table}

\subsubsection{Experiment 2}

In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in \cite{b4}. The first uses a static version of the SJFRR algorithm for scheduling each queue, while the second variant uses a dynamic version of the SJFRR algorithm for doing so.

\begin{table}[H]
    \caption{Experiment 2 Input}
    \centering
     \begin{tabular}{||c c c c||} 
     \hline
     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
     \hline
     \hline
     1 & 1 & 25 & 1 \T \B \\ 
     \hline
     2 & 5 & 70 & 1 \T \B \\
     \hline
     3 & 6 & 84 & 1 \T \B \\
     \hline
     4 & 7 & 17 & 1 \T \B \\
     \hline
     5 & 8 & 35 & 1 \T \B \\ 
     \hline
     \end{tabular}
\end{table}

\begin{table}[H]
    \caption{Experiment 2 Results}
    \centering
    \begin{tabular}{||c c c||}
        \hline
        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
    \hline
    \hline
    \textbf{Proposed Algorithm} & 115 & 68.8 \T \B\\ \hline
    \textbf{Dyn. SJFRR MLFQ} & 134 & 91.8\T \B\\ \hline
    \textbf{Stat. SJFRRMLFQ} & 143.4 & 98.2 \T \B\\ \hline
     \end{tabular}
\end{table}

\subsubsection{Experiment 3}

In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in \cite{b5}. The first uses a static version of the SJFRR algorithm for scheduling each queue, while the second variant uses a dynamic version of the SJFRR algorithm for doing so.

\begin{table}[H]
    \caption{Experiment 3 Input}
    \centering
     \begin{tabular}{||c c c c||} 
     \hline
     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
     \hline
     \hline
     1 & 0 & 8 & 1 \T \B \\ 
     \hline
     2 & 3 & 133 & 3 \T \B \\
     \hline
     3 & 2 & 21 & 2 \T \B \\
     \hline
     4 & 8 & 39 & 2 \T \B \\
     \hline
     5 & 19 & 67 & 2 \T \B \\ 
     \hline
     6 & 33 & 114 & 3 \T \B \\ 
     \hline
     7 & 33 & 54 & 2 \T \B \\ 
     \hline
     \end{tabular}
\end{table}

\begin{table}[H]
    \caption{Experiment 3 Results}
    \centering
    \begin{tabular}{||c c c||}
        \hline
        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
    \hline
    \hline
    \textbf{Proposed Algorithm} & 151 & 88.7 \T \B\\ \hline
    \textbf{Dyn. SJFRR MLFQ} & 252 & 119 \T \B\\ \hline
    \textbf{Stat. SJFRR MLFQ} & 351 & 228 \T \B\\ \hline
     \end{tabular}
\end{table}

\subsubsection{Experiment 4}

In this experiment, the proposed algorithm is compared against multiple variants of the MLFQ algorithm that are stated in \cite{b6}: standard MLFQ algorithm, a priority-based MLFQ algorithm and a vague logic-based MLFQ algorithm.

\begin{table}[H]
    \caption{Experiment 4 Input}
    \centering
     \begin{tabular}{||c c c c||} 
     \hline
     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
     \hline
     \hline
     1 & 0 & 40 & 1 \T \B \\ 
     \hline
     2 & 0 & 30 & 1 \T \B \\
     \hline
     3 & 0 & 50 & 1 \T \B \\
     \hline
     4 & 2 & 70 & 1 \T \B \\
     \hline
     5 & 4 & 25 & 1 \T \B \\ 
     \hline
     6 & 6 & 60 & 1 \T \B \\ 
     \hline
     7 & 7 & 45 & 1 \T \B \\ 
     \hline
     \end{tabular}
\end{table}

\begin{table}[H]
    \caption{Experiment 4 Results}
    \centering
    \begin{tabular}{||c c c||}
        \hline
        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
    \hline
    \hline
    \textbf{Proposed Algorithm} & 185.85 & 140.14 \T \B\\ \hline
    \textbf{VMLFQ} & 190 & 170 \T \B\\ \hline
    \textbf{MLFQ} & 232.14 & 175 \T \B\\ \hline
    \textbf{PMLFQ} & 240 & 180 \T \B\\ \hline
     \end{tabular}
\end{table}

\subsubsection{Experiment 5}

This experiment is the same as the previous one, but with a different input test case.

\begin{table}[H]
    \caption{Experiment 5 Input}
    \centering
     \begin{tabular}{||c c c c||} 
     \hline
     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
     \hline
     \hline
     1 & 0 & 90 & 1 \T \B \\ 
     \hline
     2 & 0 & 30 & 1 \T \B \\
     \hline
     3 & 0 & 28 & 1 \T \B \\
     \hline
     4 & 0 & 57 & 1 \T \B \\
     \hline
     5 & 0 & 73 & 1 \T \B \\ 
     \hline
     6 & 0 & 19 & 1 \T \B \\ 
     \hline
     7 & 0 & 42 & 1 \T \B \\ 
     \hline
     8 & 0 & 67 & 1 \T \B \\ 
     \hline
     \end{tabular}
\end{table}

\begin{table}[H]
    \caption{Experiment 5 Results}
    \centering
    \begin{tabular}{||c c c||}
        \hline
        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
    \hline
    \hline
    \textbf{Proposed Algorithm} & 212.5 & 161.75 \T \B\\ \hline
    \textbf{VMLFQ} & 260 & 225 \T \B\\ \hline
    \textbf{MLFQ} & 290 & 240 \T \B\\ \hline
    \textbf{PMLFQ} & 300 & 245 \T \B\\ \hline
     \end{tabular}
\end{table}

\subsubsection{Experiment 6}

In this experiment, the proposed algorithm is compared against two variants of the RR algorithm stated in \cite{b3}. The first is a static version of the RR algorithm with a constant quantum value of $25$ for scheduling each queue while the second uses a dynamic version of the RR algorithm called SRBRR for doing so.

\begin{table}[H]
    \caption{Experiment 6 Input}
    \centering
     \begin{tabular}{||c c c c||} 
     \hline
     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
     \hline
     \hline
     1 & 0 & 13 & 1 \T \B \\ 
     \hline
     2 & 0 & 35 & 1 \T \B \\
     \hline
     3 & 0 & 46 & 1 \T \B \\
     \hline
     4 & 0 & 63 & 1 \T \B \\
     \hline
     5 & 0 & 97 & 1 \T \B \\ 
     \hline
     \end{tabular}
\end{table}

\begin{table}[H]
    \caption{Experiment 6 Results}
    \centering
    \begin{tabular}{||c c c||}
        \hline
        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
    \hline
    \hline
    \textbf{Proposed Algorithm} & 113.2 & 62.4 \T \B\\ \hline
    \textbf{Dynamic SRBRR} & 122.4 & 71.6 \T \B\\ \hline
    \textbf{Static RR} & 148.2 & 97.4 \T \B\\ \hline
     \end{tabular}
\end{table}

\subsubsection{Experiment 7}

This experiment is the same as the previous one, but with a different input test case. Note that for this test case, a process queue number is irrelevant to both the RR algorithm and the SRBRR algorithm mentioned in \cite{b3}.

\begin{table}[H]
    \caption{Experiment 7 Input}
    \centering
     \begin{tabular}{||c c c c||} 
     \hline
     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
     \hline
     \hline
     1 & 0 & 54 & 1 \T \B \\ 
     \hline
     2 & 0 & 99 & 3 \T \B \\
     \hline
     3 & 0 & 5 & 2 \T \B \\
     \hline
     4 & 0 & 27 & 2 \T \B \\
     \hline
     5 & 0 & 32 & 2 \T \B \\ 
     \hline
     \end{tabular}
\end{table}

\begin{table}[H]
    \caption{Experiment 7 Results}
    \centering
    \begin{tabular}{||c c c||}
        \hline
        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
    \hline
    \hline
    \textbf{Dynamic SRBRR} & 93.6 & 50.2 \T \B\\ \hline
    \textbf{Proposed Algorithm} & 106.8 & 63.4 \T \B\\ \hline
    \textbf{Static RR} & 152.2 & 108.8 \T \B\\ \hline
     \end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% OBSERVATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Observation}

From the above simulations of different test cases and multiple performance comparisons that involved as many as 11 different scheduling algorithms not including this paper algorithm, it is clear that the average turnaround time and the average waiting time of the proposed algorithm is less than or – in few occasions  – nearly equal to those of the stated algorithms. With that said, the proposed algorithm is arguably advantageous over those algorithms, considering even the case in which it underperformed compared to the SRBRR algorithm, it is still favourable due to the capability to separate processes into categories based on their need for the processor and other advantages of the MLFQ algorithm. The performance of the proposed algorithm compared to other algorithms is further illustrated in the following graphs:

\begin{figure}[H]
    \begin{center}
\begin{tikzpicture}
    \begin{axis}[
        width=0.475*\textwidth,
        symbolic x coords={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
        ylabel=Avg. Turnaround Time,
        enlargelimits=0.15,
        legend style={at={(0.5,-0.25)}, anchor=north,legend columns=1},
        ybar,
        xtick={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
        x tick label style={rotate=45,anchor=east},
        bar width=3pt,
        cycle list name=color list
    ]

    \addplot[plot 0,bar group size={0}{3}, red]
    coordinates {(Exp. 1,115) (Exp. 2,115) (Exp. 3,151) (Exp. 6,113.2) (Exp. 7,106.8)};
    \addplot[plot 1,bar group size={1}{3}, green]
    coordinates {(Exp. 1,150.8)};
    \addplot[plot 2,bar group size={2}{3}, blue]
    coordinates {(Exp. 1,161.4)};

    \addplot[plot 1,bar group size={1}{3}, black]
    coordinates {(Exp. 2,134)};
    \addplot[plot 2,bar group size={2}{3}, brown]
    coordinates {(Exp. 2,143.4)};

    \addplot[plot 1,bar group size={1}{3}, teal]
    coordinates {(Exp. 3,252)};
    \addplot[plot 2,bar group size={2}{3}, violet]
    coordinates {(Exp. 3,351)};

    \addplot[plot 0,bar group size={0}{4}, red]
    coordinates {(Exp. 4,185.85) (Exp. 5,212.5)};
    \addplot[plot 1,bar group size={1}{4}, lime]
    coordinates {(Exp. 4,190) (Exp. 5,260)};
    \addplot[plot 2,bar group size={2}{4}, orange]
    coordinates {(Exp. 4,232.14) (Exp. 5,290)};
    \addplot[plot 3,bar group size={3}{4}, olive]
    coordinates {(Exp. 4,240) (Exp. 5,300)};

    \addplot[plot 1,bar group size={1}{3}, cyan]
    coordinates {(Exp. 6,122.4) (Exp. 7,93.6)};
    \addplot[plot 2,bar group size={2}{3}, magenta]
    coordinates {(Exp. 6,148.2) (Exp. 7,152.2)};

    \legend{Proposed Algorithm,Dynamic RR MLFQ, Static RR MLFQ, Dyn. SJFRR MLFQ of \cite{b4},  Stat. SJFRR MLFQ of \cite{b4}, Dyn. SJFRR MLFQ of \cite{b5}, Stat. SJFRR MLFQ of \cite{b5}, VMLFQ, MLFQ, PMLFQ, Dynamic SRBRR, Static RR}
    \end{axis}
\end{tikzpicture}
\end{center}
\caption{Comparison graph for average turnaround time}
\vspace{45mm}
\end{figure}

\begin{figure}[H]
    \begin{center}
\begin{tikzpicture}
    \begin{axis}[
        width=0.475*\textwidth,
        symbolic x coords={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
        ylabel=Avg. Waiting Time,
        enlargelimits=0.15,
        legend style={at={(0.5,-0.25)}, anchor=north,legend columns=1},
        ybar,
        xtick={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
        x tick label style={rotate=45,anchor=east},
        bar width=3pt,
        cycle list name=color list
    ]

    \addplot[plot 0,bar group size={0}{3}, red]
    coordinates {(Exp. 1,68.8) (Exp. 2,68.8) (Exp. 3,88.7) (Exp. 6,62.4) (Exp. 7,63.4)};
    \addplot[plot 1,bar group size={1}{3}, green]
    coordinates {(Exp. 1,107.6)};
    \addplot[plot 2,bar group size={2}{3}, blue]
    coordinates {(Exp. 1,116.2)};

    \addplot[plot 1,bar group size={1}{3}, black]
    coordinates {(Exp. 2,91.8)};
    \addplot[plot 2,bar group size={2}{3}, brown]
    coordinates {(Exp. 2,98.2)};

    \addplot[plot 1,bar group size={1}{3}, teal]
    coordinates {(Exp. 3,119)};
    \addplot[plot 2,bar group size={2}{3}, violet]
    coordinates {(Exp. 3,228)};

    \addplot[plot 0,bar group size={0}{4}, red]
    coordinates {(Exp. 4,140.14) (Exp. 5,161.75)};
    \addplot[plot 1,bar group size={1}{4}, lime]
    coordinates {(Exp. 4,170) (Exp. 5,225)};
    \addplot[plot 2,bar group size={2}{4}, orange]
    coordinates {(Exp. 4,175) (Exp. 5,240)};
    \addplot[plot 3,bar group size={3}{4}, olive]
    coordinates {(Exp. 4,180) (Exp. 5,245)};

    \addplot[plot 1,bar group size={1}{3}, cyan]
    coordinates {(Exp. 6,71.6) (Exp. 7,50.2)};
    \addplot[plot 2,bar group size={2}{3}, magenta]
    coordinates {(Exp. 6,97.2) (Exp. 7,108.8)};

    \legend{Proposed Algorithm,Dynamic RR MLFQ, Static RR MLFQ, Dyn. SJFRR MLFQ of \cite{b4},  Stat. SJFRR MLFQ of \cite{b4}, Dyn. SJFRR MLFQ of \cite{b5}, Stat. SJFRR MLFQ of \cite{b5}, VMLFQ, MLFQ, PMLFQ, Dynamic SRBRR, Static RR}
    \end{axis}
\end{tikzpicture}
\end{center}
\caption{Comparison graph for average waiting time}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CONCLUSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion and Future Work}

The goal of this paper is to tackle different shortcomings associated with the standard MLFQ scheduling algorithm as well as its variants discussed in several papers. To resolve these deficiencies, we introduced different adjustable policies and techniques. It is evidently clear that those methods yield better CPU performance and optimize utilization by reducing the average waiting time as well as the average turnaround time. Despite experimenting numerous combinations of the parameters and scheduling policies by which the proposed MLFQ algorithm operates, we can say that there is yet a large room for experiment and improvement through finding better methods and policies which would make the algorithm more adaptable to the nature of the submitted processes and overall more enhanced. For instance, adjusting the criteria by which the schedular decides whether to promote a process might further lessen starvation. Making the proposed algorithm preemptive might also aid mitigating starvation and render overall better performance. The possibilities are limitless.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{00}

\bibitem{b1} H.S. Behera, Reena Kumari Naik, Suchilagna Parida, ``Improved multilevel feedback queue scheduling using dynamic time quantum and its performance analysis'', \textit{International Journal of Computer Science and Information Technologies}, vol. 3, no. 2, 2012, pp. 3801-3807.

\bibitem{b2} MohammadReza EffatParvar, Karim Faez, Mehdi EffatParvar, Mehdi Zarei, Saeed Safari, ``An intelligent MLFQ scheduling algorithm (IMLFQ) with fault tolerant mechanism'', \textit{Sixth International Conference on Intelligent Systems Design and Applications}, vol. 3, 2006, pp. 80–85.

\bibitem{b3} Rakesh Mohanty, H. S. Behera, Khusbu Patwari, Monisha Dash, ``Design and performance evaluation of a new proposed shortest remaining burst round robin (SRBRR) scheduling algorithm'', \textit{International Symposium on Computer Engineering \& Technology}, vol. 17, 2010.

\bibitem{b4} S. K. Dwivedi and R. Gupta, ``A simulator based performance analysis of multilevel feedback queue scheduling'', \textit{2014 International Conference on Computer and Communication Technology (ICCCT)}, Allahabad, 2014, pp. 341-346.

\bibitem{b5} Malhar Thombare, Rajiv Sukhwani, Priyam Shah, Sheetal Chaudhari, Pooja Raundale, ``Efficient implementation of multilevel feedback queue scheduling'', \textit{2016 International Conference on Wireless Communications, Signal Processing and Networking (WiSPNET)}, Chennai, 2016, pp. 1950–1954.

\bibitem{b6} S. Raheja, R. Dadhich, and S. Rajpalc, ``Designing of vague logic based multilevel feedback queue scheduler'', \textit{Egyptian Informatics Journal}, vol. 17, 2016, pp. 125-137.

\bibitem{b7} A. Alsheikhy, R. Ammar and R. Elfouly, ``An improved dynamic Round Robin scheduling algorithm based on a variant quantum time'', \textit{2015 11th International Computer Engineering Conference (ICENCO)}, Cairo, 2015, pp. 98-104.

\bibitem{b8} M. K. Mishra and F. Rashid, ``An improved round robin CPU scheduling algorithm with varying time quantum'', \textit{International Journal of Computer Science, Engineering and Applications  (IJCSEA)}, vol. 4, 2014.

\bibitem{b9} A. Singh, P. Goyal and S. Batra, ``An optimized round robin scheduling algorithm for CPU scheduling'', \textit{International Journal on Computer Science and Engineering}, 2010, pp. 2383-2385.

\bibitem{b10} Dipto Biswas, Md. Samsuddoha, ``Determining proficient time quantum to  improve the performance  of  round  robin  scheduling  algorithm'', \textit{International  Journal  of  Modern  Education  and  Computer Science(IJMECS)}, vol. 11, 2019, pp. 33-40.

\bibitem{b11} K. Hoganson and J. Brown, ``Real-time scheduling with MLFQ-RT multilevel feedback queue with starvation mitigation'', \textit{2017 International Conference on Engineering, Technology and Innovation (ICE/ITMC)}, Funchal, 2017, pp. 155-160.

\end{thebibliography}

\end{document}

### 2020-05-27 code/A_Star_Algorithm/a_star.cpp
add a star algorithm

@@ -1,0 +1,144 @@
+#include <bits/stdc++.h>
+#include <thread>
+#include <pthread.h>
+using namespace std;
+
+int ROW, COL;
+typedef pair<int, int> ii;
+struct Grid
+{
+    ii parent = {-1, -1};
+    double f = FLT_MAX, g = FLT_MAX, h = FLT_MAX; // f = g + h
+};
+#define fi first
+#define se second
+#define mp make_pair
+typedef vector<vector<int>> VVI;
+typedef vector<vector<bool>> VVB;
+typedef vector<vector<Grid>> VVG;
+typedef pair<double, pair<int, int>> dii;
+
+auto is_valid = [](int r, int c) { return (r >= 0) && (r < ROW) && (c >= 0) && (c < COL); };
+auto not_blocked = [](VVI &grid, int r, int c) { return grid[r][c] != 0; };
+auto is_dst = [](int r, int c, ii dst) { return r == dst.fi && c == dst.se; };
+auto calc_h = [](int r, int c, ii dst) { return ((double)sqrt((r - dst.fi) * (r - dst.fi) + (c - dst.se) * (c - dst.se))); };
+
+void get_path(const VVG &cells, ii dst)
+{
+    printf("Path: ");
+    int r = dst.fi, c = dst.se;
+    stack<ii> path;
+    // partent (i, j)
+    while (!(cells[r][c].parent.fi == r && cells[r][c].parent.se == c))
+    {
+        path.push(mp(r, c));
+        int tmp_r = cells[r][c].parent.fi, tmp_c = cells[r][c].parent.se;
+        r = tmp_r, c = tmp_c;
+    }
+    path.push(mp(r, c)); // push source
+    while (!path.empty())
+    {
+        ii p = path.top();
+        path.pop();
+        printf("(%d,%d) ", p.fi, p.se);
+    }
+    printf("\n");
+}
+
+bool try_go_to(VVI &grid, int &i, int &j, int iNew, int jNew, VVG &cells, set<dii> &pq, VVB &visited, ii &dst, bool &dstFound)
+{
+    double fNew, hNew, gNew;
+    if (is_valid(iNew, jNew))
+    {
+        if (is_dst(iNew, jNew, dst))
+        {
+            cells[iNew][jNew].parent = {i, j};
+            get_path(cells, dst);
+            dstFound = true;
+            return true;
+        }
[…]

### 2020-05-27 code/A_Star_Algorithm/a_star.cpp
remove one boolean in a star routing

@@ -45,7 +45,7 @@ void get_path(const VVG &cells, ii dst)
     printf("\n");
 }
 
-bool try_go_to(VVI &grid, int &i, int &j, int iNew, int jNew, VVG &cells, set<dii> &pq, VVB &visited, ii &dst, bool &dstFound)
+bool try_go_to(VVI &grid, int &i, int &j, int iNew, int jNew, VVG &cells, set<dii> &pq, VVB &visited, ii &dst)
 {
     double fNew, hNew, gNew;
     if (is_valid(iNew, jNew))
@@ -54,7 +54,6 @@ bool try_go_to(VVI &grid, int &i, int &j, int iNew, int jNew, VVG &cells, set<di
         {
             cells[iNew][jNew].parent = {i, j};
             get_path(cells, dst);
-            dstFound = true;
             return true;
         }
         else if (!visited[iNew][jNew] && not_blocked(grid, iNew, jNew))
@@ -91,7 +90,6 @@ void a_star(VVI &grid, ii src, ii dst)
         return;
     }
 
-    bool dstFound = false;
     VVG cells(ROW, vector<Grid>(COL));
     VVB visited(ROW, vector<bool>(COL, false));
     int i = src.fi, j = src.se;      // source to i,j
@@ -104,21 +102,20 @@ void a_star(VVI &grid, ii src, ii dst)
         pq.erase(pq.begin());
         i = p.se.fi, j = p.se.se;
         visited[i][j] = true;
-        bool finished = try_go_to(grid, i, j, i - 1, j, cells, pq, visited, dst, dstFound); // North
+        bool finished = try_go_to(grid, i, j, i - 1, j, cells, pq, visited, dst); // North
         if (finished)
             return;
-        finished = try_go_to(grid, i, j, i + 1, j, cells, pq, visited, dst, dstFound); // South
+        finished = try_go_to(grid, i, j, i + 1, j, cells, pq, visited, dst); // South
         if (finished)
             return;
-        finished = try_go_to(grid, i, j, i, j - 1, cells, pq, visited, dst, dstFound); // West
+        finished = try_go_to(grid, i, j, i, j - 1, cells, pq, visited, dst); // West
         if (finished)
             return;
-        finished = try_go_to(grid, i, j, i, j + 1, cells, pq, visited, dst, dstFound); // East
+        finished = try_go_to(grid, i, j, i, j + 1, cells, pq, visited, dst); // East
[…]

### 2020-05-27 code/A_Star_Algorithm/a_star.cpp
minor change in a star algo

@@ -5,11 +5,13 @@ using namespace std;
 
 int ROW, COL;
 typedef pair<int, int> ii;
+
 struct Grid
 {
     ii parent = {-1, -1};
     double f = FLT_MAX, g = FLT_MAX, h = FLT_MAX; // f = g + h
 };
+
 #define fi first
 #define se second
 #define mp make_pair

### 2020-05-28 paper.tex
Update References

@@
 \usepackage{pgfplots}
+\usepackage{subfigure}
+
 \pgfplotsset{compat=1.9}
@@
 
-Scheduling is a crucial part of many real-time applications such as scheduling airlines and railways communications, product manufacturing processes, data packets routing in computer networks and pipe networks.
-Operating systems multiprocessing environments are no different from those mediums mentioned, where processes compete over CPU utilization.
-This brought to existence the need for scheduling algorithms to justly assign processes to available CPUs in favour of optimizing performance measures, in particular, to maximize overall CPU utilization and throughput, and to minimize response time, waiting time and turnaround time.
-A schedular could be preemptive where it can temporarily interrupt a process without its cooperation and assign the CPU resources to a different process with the intention to assign them back to the former process, such operation is called context switching, or it could be non-preemptive (cooperative) by not being able to context switch between processes.
-Various preemptive and non-preemptive scheduling disciplines exist such as, first come, first serve (FCFS), shortest job first (SJF), shortest remaining time first (SRTF), round-robin (RR), multilevel queue and multilevel feedback queue.
-In FCFS, processes are non-preemptively executed according to their arrival time.
-In SJF, the CPU is assigned to the process with the smallest burst time.
-SRTF is a preemptive version of SJF where at each iteration, the process with the least remaining burst time takes control of the CPU.
-Round-robin preemptively assigns the CPU to each process in the ready queue for a static amount of time called quantum and executes them in an FCFS fashion.
-Multilevel queue algorithm partitions the ready queue into several queues to which processes are perpetually assigned and are executed according to another scheduling algorithm (e.g.
-RR).
-Processes cannot move from one queue to another.
-However, in a multilevel feedback queue algorithm, processes that don't terminate in one queue, due to having CPU burst time more than the time quantum assigned to their particular queue, are shifted to a lower priority queue.
-Due to the fact that long processes eventually sink to the lowest priority queue, they are conventionally carried out using FCFS to prevent starvation.
-Several papers discuss different methods to optimize the algorithms mentioned, each come with their set of advantages and drawbacks.
-One of many is \cite{b2}, whose approach achieves better average response time but at the cost of hindering the scheduling process due to recalculating time quantum for each queue using a recurrent neural network.
-In this paper, we attempted to implement the best of all worlds.
+Routing is considered a critical step in physical design process. Until now we have not achieved the optimum solution for VLSI routing.It is exactly done in two steps:
+\begin{enumerate}
+    \item Global routing.
+    \item Detailed routing.
+\end{enumerate}
+We first run a global routing which is the responsible for making an approximate routing for the whole circuit in order to be used as a guide for detailed routing, then we run a detailed routing to make the exact routing for the system.
+That means if global or detailed routing is improved the whole routing process is improved, but there are many problems we have to overcome to make a correct routing process.
+First of all we have to take into consideration the scale, as millions of wires are exist in a small chip area which means that many kilometers of wires are placed in a very small area, so we have to minimize total wire length as much as we can, also we know that as the wire length increases the resistance increases as well which means more delay in the chip.
+We can find another problem as circuits are done in nano-scale which means that its geometric will be complex.
+Another problem that routing algorithm have to be applicable for more than one layer with different costs.
+We also have to take into consideration the direction of wires in every layer (vertical | horizontal) and no diagonal pathes, then to go from source 'S' to target 'T'
+
+\begin{figure} 
+\centering  
+\subfigure[First iteration] {
+    \begin{tikzpicture}
+        [
+            box/.style={rectangle,draw=black,thick, minimum size=0.5cm},
+        ]
+
+    \foreach \x in {0,0.5,...,2.5}{
+        \foreach \y in {0,0.5,...,2.5}
+            \node[box] at (\x,\y){};
+    }
+
+    \node[box,fill=green] at (3,3){A};  
+    \node[box,fill=red  ] at (2,2){};  
+    \node[box,fill=blue ] at (1,1){};  
+    \end{tikzpicture}
+}
+\subfigure[Second iteration] {
+    \begin{tikzpicture}
+        [
+            box/.style={rectangle,draw=black,thick, minimum size=0.5cm},
+        ]
+
+    \foreach \x in {0,0.5,...,2.5}{
+        \foreach \y in {0,0.5,...,2.5}
+            \node[box] at (\x,\y){};
+    }
+
+    \node[box,fill=green] at (3,3){A};  
+    \node[box,fill=red  ] at (2,2){};  
+    \node[box,fill=blue ] at (1,1){};  
+    \end{tikzpicture}
+}
+\subfigure[Third iteration] {
+    \begin{tikzpicture}
+        [
+            box/.style={rectangle,draw=black,thick, minimum size=0.5cm},
+        ]
+
+    \foreach \x in {0,0.5,...,2.5}{
+        \foreach \y in {0,0.5,...,2.5}
+            \node[box] at (\x,\y){};
+    }
+
+    \node[box,fill=green] at (3,3){A};  
+    \node[box,fill=red  ] at (2,2){};  
+    \node[box,fill=blue ] at (1,1){};  
+    \end{tikzpicture}
+}
+\subfigure[After N iteration] {
+    \begin{tikzpicture}
+        [
+            box/.style={rectangle,draw=black,thick, minimum size=0.5cm},
+        ]
+
+    \foreach \x in {0,0.5,...,2.5}{
+        \foreach \y in {0,0.5,...,2.5}
+            \node[box] at (\x,\y){};
+    }
+
+    \node[box,fill=green] at (3,3){A};  
+    \node[box,fill=red  ] at (2,2){};  
+    \node[box,fill=blue ] at (1,1){};  
+    \end{tikzpicture}
+}
+
+\end{figure}
 
@@
 
-\bibitem{b1} H.S.
-Behera, Reena Kumari Naik, Suchilagna Parida, ``Improved multilevel feedback queue scheduling using dynamic time quantum and its performance analysis'', \textit{International Journal of Computer Science and Information Technologies}, vol.
-3, no.
-2, 2012, pp.
-3801-3807.
-
-\bibitem{b2} MohammadReza EffatParvar, Karim Faez, Mehdi EffatParvar, Mehdi Zarei, Saeed Safari, ``An intelligent MLFQ scheduling algorithm (IMLFQ) with fault tolerant mechanism'', \textit{Sixth International Conference on Intelligent Systems Design and Applications}, vol.
-3, 2006, pp.
-80–85.
-
-\bibitem{b3} Rakesh Mohanty, H.
-S.
-Behera, Khusbu Patwari, Monisha Dash, ``Design and performance evaluation of a new proposed shortest remaining burst round robin (SRBRR) scheduling algorithm'', \textit{International Symposium on Computer Engineering \& Technology}, vol.
-17, 2010.
-
-\bibitem{b4} S.
-K.
-Dwivedi and R.
-Gupta, ``A simulator based performance analysis of multilevel feedback queue scheduling'', \textit{2014 International Conference on Computer and Communication Technology (ICCCT)}, Allahabad, 2014, pp.
-341-346.
-
-\bibitem{b5} Malhar Thombare, Rajiv Sukhwani, Priyam Shah, Sheetal Chaudhari, Pooja Raundale, ``Efficient implementation of multilevel feedback queue scheduling'', \textit{2016 International Conference on Wireless Communications, Signal Processing and Networking (WiSPNET)}, Chennai, 2016, pp.
-1950–1954.
-
-\bibitem{b6} S. Raheja, R. Dadhich, and S. Rajpalc, ``Designing of vague logic based multilevel feedback queue scheduler'', \textit{Egyptian Informatics Journal}, vol. 17, 2016, pp. 125-137.
-
-\bibitem{b7} A.
-Alsheikhy, R.
-Ammar and R.
-Elfouly, ``An improved dynamic Round Robin scheduling algorithm based on a variant quantum time'', \textit{2015 11th International Computer Engineering Conference (ICENCO)}, Cairo, 2015, pp.
-98-104.
-
-\bibitem{b8} M.
-K.
-Mishra and F.
-Rashid, ``An improved round robin CPU scheduling algorithm with varying time quantum'', \textit{International Journal of Computer Science, Engineering and Applications  (IJCSEA)}, vol.
-4, 2014.
-
-\bibitem{b9} A.
-Singh, P.
-Goyal and S.
-Batra, ``An optimized round robin scheduling algorithm for CPU scheduling'', \textit{International Journal on Computer Science and Engineering}, 2010, pp.
-2383-2385.
-
-\bibitem{b10} Dipto Biswas, Md.
-Samsuddoha, ``Determining proficient time quantum to  improve the performance  of  round  robin  scheduling  algorithm'', \textit{International  Journal  of  Modern  Education  and  Computer Science(IJMECS)}, vol.
-11, 2019, pp.
-33-40.
-
-\bibitem{b11} K.
-Hoganson and J.
-Brown, ``Real-time scheduling with MLFQ-RT multilevel feedback queue with starvation mitigation'', \textit{2017 International Conference on Engineering, Technology and Innovation (ICE/ITMC)}, Funchal, 2017, pp.
-155-160.
+\bibitem{b1} Muhammet Mustafa Ozdal and M.
+D.
+F.
+Wong, "Archer: a history-driven global routing algorithm," \textit{2007 IEEE/ACM International Conference on Computer-Aided Design}, San Jose, CA, 2007, pp.
+488-495, doi: 10.1109/ICCAD.2007.4397312.
 

### 2020-05-28 paper.tex
Introduction

@@
 
-Routing is considered a critical step in physical design process. Until now we have not achieved the optimum solution for VLSI routing.It is exactly done in two steps:
-\begin{enumerate}
-    \item Global routing.
-    \item Detailed routing.
-\end{enumerate}
-We first run a global routing which is the responsible for making an approximate routing for the whole circuit in order to be used as a guide for detailed routing, then we run a detailed routing to make the exact routing for the system.
+Routing is critical step in physical design process.
+Until now the optimum solution for VLSI routing has not been achieved yet, so it is considered as a very interesting challenging feild.
+It is exactly done in two steps, global routing and detailed routing.
+At first global routing is run which is the responsible for making an approximate routing for the whole circuit in order to be used as a guide for detailed routing, then the detailed routing is run to make the exact routing for the system.
 That means if global or detailed routing is improved the whole routing process is improved, but there are many problems we have to overcome to make a correct routing process.
-First of all we have to take into consideration the scale, as millions of wires are exist in a small chip area which means that many kilometers of wires are placed in a very small area, so we have to minimize total wire length as much as we can, also we know that as the wire length increases the resistance increases as well which means more delay in the chip.
-We can find another problem as circuits are done in nano-scale which means that its geometric will be complex.
+First of all we have to take into consideration the scale, as millions of wires exist in a small chip area which means that many kilometers of wires are placed in a very small area, so we have to minimize total wire length as much as we can, also we know that as the wire length increases the resistance increases as well which means more delay in the chip.
+We can find another problem as circuits are made in nano-scale which means that its geometric will be complex.
 Another problem that routing algorithm have to be applicable for more than one layer with different costs.
-We also have to take into consideration the direction of wires in every layer (vertical | horizontal) and no diagonal pathes, then to go from source 'S' to target 'T'
+We also have to take into consideration the direction of wires in every layer (vertical | horizontal) and no diagonal pathes, then to go from source 'S' to target 'T' the path taken should be in (vertical | horizontal) directions thet specified by the layer (at each layer wires are placed in one direction only), then there is another problem as when a wire goes from layer to another to continue on the perpendicular direction it have to go through via which have a high resistance.
+DFM (design for manufacturer) rules also has to be achieved.
+All of these constraints must be taken into consideration with the global routing to achieve hundred percent of the circuit connections, that means global routing will take a lot of time to achieve all these constraints, and here is the challenge to achieve all the routing specifications with minimum time taken.
 
@@
     }
-
+    \node [box,fill=green] at (0,0.5){A};  
     \node[box,fill=green] at (3,3){A};  
@@
 }
+\caption{Steps to get the best global routing}
+\label{fig:GlobalRoutingProcess}
+\end{figure}
 
-\end{figure}
+In Figure~\ref{fig:GlobalRoutingProcess}
 
@@
 Hence, it is essential to choose a proper method to compute the time quantum value to minimize response time and maximize overall performance.
-In \cite{b2}, an algorithm is introduced for minimizing the response time.
+In , an algorithm is introduced for minimizing the response time.
 In this algorithm, a Recurrent Neural Network (RNN) is used to determine both the number of queues and the optimized time quantum value for each queue.
@@
 Their proposed intelligent version of the MLFQ offers good results, however, it suffers from a few drawbacks, the first being the direct proportionality of its network learning time and the amount of input data, and the second is the possibility of experiencing initial overhead at the first iterations of the algorithm.
-Our approach proposes an improved version of MLFQ that utilizes an altered version of RR named shortest remaining burst round-robin (SRBRR) introduced in \cite{b3} which avoids the cost of learning time and overhead time in \cite{b2}.
+Our approach proposes an improved version of MLFQ that utilizes an altered version of RR named shortest remaining burst round-robin (SRBRR) introduced in  which avoids the cost of learning time and overhead time in .
 Regarding the various approaches to improve the MLFQ algorithm, those attempts dealt with starvation by assigning different quantum values to the ready queues depending on their priority.
@@
 In our proposed algorithm, there are 5 queues sorted in ascending order in line with their priority number, 1 being the highest priority and 5 being the lowest.
-Each queue uses a modified version of the round-robin scheduling algorithm stated in \cite{b3}.
-In \cite{b3}, processes are sorted in ascending order according to their burst time and are assigned a time quantum that equals the median burst time of those processes.
+Each queue uses a modified version of the round-robin scheduling algorithm stated in {b3}.
+In {b3}, processes are sorted in ascending order according to their burst time and are assigned a time quantum that equals the median burst time of those processes.
 This algorithm provides better turnaround time and waiting time than the standard static quantum RR algorithm whose quantum, if set too short, leads to many context switches and, if set too long, morphs the algorithm into an FCFS algorithm.
-The proposed alteration on the stated algorithm in \cite{b3} is that each queue quantum time equals the median burst time multiplied by a factor matching the queue number.
+The proposed alteration on the stated algorithm in {b3} is that each queue quantum time equals the median burst time multiplied by a factor matching the queue number.
 Hence, the gradual increase of quantum time as priority decreases.
@@
 
-In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in \cite{b4}.
+In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in {b4}.
 The first uses a static version of the RR algorithm for scheduling each queue, while the second variant uses a dynamic version of the RR algorithm for doing so.
@@
 
-In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in \cite{b4}.
+In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in {b4}.
 The first uses a static version of the SJFRR algorithm for scheduling each queue, while the second variant uses a dynamic version of the SJFRR algorithm for doing so.
@@
 
-In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in \cite{b5}.
+In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in {b5}.
 The first uses a static version of the SJFRR algorithm for scheduling each queue, while the second variant uses a dynamic version of the SJFRR algorithm for doing so.
@@
 
-In this experiment, the proposed algorithm is compared against multiple variants of the MLFQ algorithm that are stated in \cite{b6}: standard MLFQ algorithm, a priority-based MLFQ algorithm and a vague logic-based MLFQ algorithm.
+In this experiment, the proposed algorithm is compared against multiple variants of the MLFQ algorithm that are stated in {b6}: standard MLFQ algorithm, a priority-based MLFQ algorithm and a vague logic-based MLFQ algorithm.
 
@@
 
-In this experiment, the proposed algorithm is compared against two variants of the RR algorithm stated in \cite{b3}.
+In this experiment, the proposed algorithm is compared against two variants of the RR algorithm stated in {b3}.
 The first is a static version of the RR algorithm with a constant quantum value of $25$ for scheduling each queue while the second uses a dynamic version of the RR algorithm called SRBRR for doing so.
@@
 This experiment is the same as the previous one, but with a different input test case.
-Note that for this test case, a process queue number is irrelevant to both the RR algorithm and the SRBRR algorithm mentioned in \cite{b3}.
+Note that for this test case, a process queue number is irrelevant to both the RR algorithm and the SRBRR algorithm mentioned in {b3}.
 
@@
     \legend{Proposed Algorithm,Dynamic RR MLFQ, Static RR MLFQ, Dyn.
-SJFRR MLFQ of \cite{b4},  Stat.
-SJFRR MLFQ of \cite{b4}, Dyn.
-SJFRR MLFQ of \cite{b5}, Stat.
-SJFRR MLFQ of \cite{b5}, VMLFQ, MLFQ, PMLFQ, Dynamic SRBRR, Static RR}
+SJFRR MLFQ of {b4},  Stat.
+SJFRR MLFQ of {b4}, Dyn.
+SJFRR MLFQ of {b5}, Stat.
+SJFRR MLFQ of {b5}, VMLFQ, MLFQ, PMLFQ, Dynamic SRBRR, Static RR}
     \end{axis}

### 2020-05-28 paper.tex
Introduction

@@
 \centering  
-\subfigure[First iteration] {
+\subfigure[Before routing] {
     \begin{tikzpicture}
@@
     \node [box,fill=green] at (0,0.5){A};
-    \node[box,fill=green] at (3,3){A};  
-    \node[box,fill=red  ] at (2,2){};  
-    \node[box,fill=blue ] at (1,1){};  
+    \node[box,fill=green  ] at (2,2){A};  
+    \node[box,fill=red  ] at (1.5,2.5){B}; 
+    \node [box,fill=red] at (2.5,0.5){B}; 
     \end{tikzpicture}
 }
-\subfigure[Second iteration] {
+\subfigure[Iteration number x] {
     \begin{tikzpicture}
@@
 
-    \node[box,fill=green] at (3,3){A};  
-    \node[box,fill=red  ] at (2,2){};  
-    \node[box,fill=blue ] at (1,1){};  
+    \node [box,fill=green] at (0,0.5){A};
+    \node[box,fill=green  ] at (2,2){A};  
+    \node[box,fill=green  ] at (0.5,0.5){};  
+    \node[box,fill=green  ] at (0.5,1){};  
+    \node[box,fill=green  ] at (0.5,1.5){};  
+    \node[box,fill=green  ] at (1,1.5){};  
+    \node[box,fill=red  ] at (1.5,2.5){B}; 
+    \node [box,fill=red] at (2.5,0.5){B};
+    \node [box,fill=red] at (2,0.5){};
+    \node [box,fill=red] at (1.5,0.5){};
+    \node [box,fill=red] at (1.5,1){};
+    \node [box,fill=red] at (1.5,1.5){};
+    \node [box,fill=red] at (1.5,2){};
     \end{tikzpicture}
 }
-\subfigure[Third iteration] {
+\subfigure[Iteration number y] {
     \begin{tikzpicture}
@@
 
-    \node[box,fill=green] at (3,3){A};  
-    \node[box,fill=red  ] at (2,2){};  
-    \node[box,fill=blue ] at (1,1){};  
+    \node [box,fill=green] at (0,0.5){A};
+    \node[box,fill=green  ] at (2,2){A};  
+    \node[box,fill=green  ] at (0,1){};  
+    \node[box,fill=green  ] at (0,1.5){};  
+    \node[box,fill=green  ] at (0,2){};  
+    \node[box,fill=green  ] at (0.5,2){};  
+    \node[box,fill=green  ] at (1,2){};  
+    \node[box,fill=green  ] at (1,1.5){};  
+    \node[box,fill=green  ] at (1,1){};  
+    \node[box,fill=green  ] at (1,0.5){};  
+    \node[box,fill=green  ] at (1.5,0){};  
+    \node[box,fill=green  ] at (1,0){};  
+    \node[box,fill=green  ] at (2,0){};  
+    \node[box,fill=green  ] at (2,0.5){};  
+    \node[box,fill=green  ] at (2,1){};  
+    \node[box,fill=green  ] at (2,1.5){};  
+    \node[box,fill=red  ] at (1.5,2.5){B}; 
+    \node [box,fill=red] at (2.5,0.5){B};  
+    \node [box,fill=red] at (2.5,1){};
+    \node [box,fill=red] at (2.5,1.5){};
+    \node [box,fill=red] at (2.5,2){};
+    \node [box,fill=red] at (2.5,2.5){};
+    \node [box,fill=red] at (2,2.5){};
     \end{tikzpicture}
@@
 
-    \node[box,fill=green] at (3,3){A};  
-    \node[box,fill=red  ] at (2,2){};  
-    \node[box,fill=blue ] at (1,1){};  
+    \node [box,fill=green] at (0,0.5){A};
+    \node[box,fill=green  ] at (2,2){A};  
+    \node[box,fill=green  ] at (0,1){};  
+    \node[box,fill=green  ] at (0,1.5){};  
+    \node[box,fill=green  ] at (0,2){};  
+    \node[box,fill=green  ] at (0.5,2){};  
+    \node[box,fill=green  ] at (1,2){};  
+    \node[box,fill=green  ] at (1.5,2){};  
+    \node[box,fill=red  ] at (1.5,2.5){B}; 
+    \node [box,fill=red] at (2.5,0.5){B}; 
+    \node [box,fill=red] at (2.5,1){};
+    \node [box,fill=red] at (2.5,1.5){};
+    \node [box,fill=red] at (2.5,2){};
+    \node [box,fill=red] at (2.5,2.5){};
+    \node [box,fill=red] at (2,2.5){};
     \end{tikzpicture}
 }
-\caption{Steps to get the best global routing}
+\caption{Global routing to get the best pathes}
 \label{fig:GlobalRoutingProcess}
@@
 
-In Figure~\ref{fig:GlobalRoutingProcess}
+Figure~\ref{fig:GlobalRoutingProcess} shows a very simple approach of how the global router works.
+At (a) the source and target of both (A,B) need to be connected ignoring obstacles, nevertheless we can observe that the global router have to iterate to get the best routing pathes, at (b) (B,B) connected but there is no way to connect (A,A) as when (B,B) connected together they blocked the way for (A,A) to be connected, after some iterations we can find the figure at (c) in which (A,A) and (B,B) connected correctly, but there is a problem, the (A,A) connection is not the optimal path as there are pathes which achieve less wire length, so the global router have to iterate until reaching the optimal path.
+These iterations are done for only two connections in one layer without obstacles, then how about millions of wires in VLSI?
+this shows how much the global routing algorithm has to be very fast in order to connect this huge number of wires as fast as possible.
 

### 2020-05-29 code/cu-gr/build.sh
Add A* to cu-gr

@@ -1,0 +1,1 @@
+scripts/build.py -o release;

### 2020-05-29 code/cu-gr/sample_run.sh

@@ -1,0 +1,3 @@
+cd run/;
+./iccad19gr -lef ../toys/iccad2019c/ispd18_sample/ispd18_sample.input.lef -def ../toys/iccad2019c/ispd18_sample/ispd18_sample.input.def -output ispd18_test1.solution.guide -threads 20;
+cd ..;

### 2020-05-29 code/cu-gr/src/single_net/MazeRoute.cpp

@@ -1,0 +1,223 @@
+#include "MazeRoute.h"
+
+ostream &operator<<(ostream &os, const Solution &sol) {
+    // modified
+    os << "cost=" << sol.g_cost << ", vertex=" << sol.vertex << ", prev=" << (sol.prev ? sol.prev->vertex : -1);
+    return os;
+}
+
+void MazeRoute::constructGridGraph(const vector<gr::GrBoxOnLayer> &guides) {
+    GuideGridGraphBuilder graphBuilder(grNet, graph, guides);
+    mergedPinAccessBoxes = grNet.getMergedPinAccessBoxes(
+        [](const gr::GrPoint &point) { return gr::PointOnLayer(point.layerIdx, point[X], point[Y]); });
+    graphBuilder.run(mergedPinAccessBoxes);
+}
+
+void MazeRoute::constructGridGraph(const CongestionMap &congMap) {
+    CoarseGridGraphBuilder graphBuilder(grNet, graph, congMap);
+    mergedPinAccessBoxes =
+        grNet.getMergedPinAccessBoxes([&](const gr::GrPoint &point) { return graphBuilder.grPointToPoint(point); });
+    graphBuilder.run(mergedPinAccessBoxes);
+}
+
+db::RouteStatus MazeRoute::run() {
+    vertexCosts.assign(graph.getNodeNum(),
+                       {std::numeric_limits<db::CostT>::max(), std::numeric_limits<db::CostT>::max()});
+    pinSols.assign(mergedPinAccessBoxes.size(), nullptr);
+    const int startPin = 0;
+
+    auto status = route(startPin);
+    if (!db::isSucc(status)) {
+        return status;
+    }
+
+    getResult();
+
+    return status;
+}
+
+db::RouteStatus MazeRoute::route(int startPin) {
+    // define std::priority_queue
+    auto solComp = [](const std::shared_ptr<Solution> &lhs, const std::shared_ptr<Solution> &rhs) {
+        return rhs->f_cost < lhs->f_cost;
+    };
+    std::priority_queue<std::shared_ptr<Solution>, vector<std::shared_ptr<Solution>>, decltype(solComp)> solQueue(
+        solComp);
+
+    auto updateSol = [&](const std::shared_ptr<Solution> &sol) {
+        solQueue.push(sol);
[…]

### 2020-05-29 code/cu-gr/src/single_net/MazeRoute.h

@@ -1,0 +1,42 @@
+#pragma once
+
+#include "GridGraph.h"
+#include "multi_net/CongestionMap.h"
+
+class Solution {
+public:
+    db::CostT g_cost;
+    db::CostT f_cost;  // g_cost + h_cost
+    db::CostT h_cost;
+    int vertex;
+    std::shared_ptr<Solution> prev;
+
+    Solution(db::CostT gc, int v, const std::shared_ptr<Solution> &p)
+        : g_cost(gc), f_cost(FLT_MAX), vertex(v), prev(p) {}
+
+    Solution(db::CostT gc, db::CostT hc, db::CostT fc, int v, const std::shared_ptr<Solution> &p)
+        : g_cost(gc), h_cost(hc), f_cost(fc), vertex(v), prev(p) {}
+
+    friend ostream &operator<<(ostream &os, const Solution &sol);
+};
+
+class MazeRoute {
+public:
+    MazeRoute(gr::GrNet &grNetData) : grNet(grNetData) {}
+
+    void constructGridGraph(const vector<gr::GrBoxOnLayer> &guides);
+    void constructGridGraph(const CongestionMap &congMap);
+    db::RouteStatus run();
+
+private:
+    gr::GrNet &grNet;
+    GridGraph graph;
+
+    // h_cost first // f_cost second // min cost upper bound for each vertex
+    vector<std::pair<db::CostT, db::CostT>> vertexCosts;
+    vector<std::shared_ptr<Solution>> pinSols;  // best solution for each pin
+    vector<vector<gr::PointOnLayer>> mergedPinAccessBoxes;
+
+    db::RouteStatus route(int startPin);
+    void getResult();
+};

### 2020-05-29 code/cu-gr/test1_run.sh

@@ -1,0 +1,3 @@
+cd run/;
+./iccad19gr -lef ../toys/iccad2019c/ispd18_sample/ispd18_test1.input.lef -def ../toys/iccad2019c/ispd18_sample/ispd18_test1.input.def -output ispd18_test1.solution.guide -threads 20;
+cd ..;

### 2020-05-29 code/cu-gr/test7_run.sh

@@ -1,0 +1,3 @@
+cd run/;
+./iccad19gr -lef ../toys/iccad2019c/ispd18_sample/ispd18_test7.input.lef -def ../toys/iccad2019c/ispd18_sample/ispd18_test7.input.def -output ispd18_test7.solution.guide -threads 20;
+cd ..;

### 2020-05-30 code/cu-gr/src/single_net/MazeRoute.cpp
new heuristic function with parameters

@@ -21,8 +21,7 @@ void MazeRoute::constructGridGraph(const CongestionMap &congMap) {
 }
 
 db::RouteStatus MazeRoute::run() {
-    vertexCosts.assign(graph.getNodeNum(),
-                       {std::numeric_limits<db::CostT>::max(), std::numeric_limits<db::CostT>::max()});
+    vertexCosts.assign(graph.getNodeNum(), Costs(FLT_MAX, FLT_MAX, FLT_MAX));
     pinSols.assign(mergedPinAccessBoxes.size(), nullptr);
     const int startPin = 0;
 
@@ -46,11 +45,16 @@ db::RouteStatus MazeRoute::route(int startPin) {
 
     auto updateSol = [&](const std::shared_ptr<Solution> &sol) {
         solQueue.push(sol);
-        if (sol->f_cost < vertexCosts[sol->vertex].second) vertexCosts[sol->vertex] = {sol->h_cost, sol->f_cost};
+        if (sol->f_cost < vertexCosts[sol->vertex].f_cost)
+            vertexCosts[sol->vertex] = Costs(sol->g_cost, sol->h_cost, sol->f_cost);
     };
-
-    auto heuristic = [](const gr::PointOnLayer &p1, const gr::PointOnLayer &p2) {
-        return std::sqrt(std::pow(p1.x - p2.x, 2) + std::pow(p1.y - p2.y, 2));
+    const double HEURISTIC_CONST1 = 1;
+    const double HEURISTIC_CONST2 = 0.3;
+    auto heuristic = [&HEURISTIC_CONST1, &HEURISTIC_CONST2](
+                         const gr::PointOnLayer &p1, const int &layer1, const gr::PointOnLayer &p2, const int &layer2) {
+        // return std::sqrt(std::pow(p1.x - p2.x, 2) + std::pow(p1.y - p2.y, 2));
+        return (std::abs(p1.x - p2.x) + std::abs(p1.y - p2.y)) * HEURISTIC_CONST1 +
+               std::abs(layer1 - layer2) * HEURISTIC_CONST2;
     };
 
     // init from startPin
@@ -58,11 +62,7 @@ db::RouteStatus MazeRoute::route(int startPin) {
         gr::PointOnLayer s = graph.getPoint(startPin);
         updateSol(std::make_shared<Solution>(0, vertex, nullptr));
     }
-    /*
-    A star
-        //   source.g_cost = 0;
-        //   source.f_cost = source.h_cost;
-    */
[…]

### 2020-05-30 code/cu-gr/src/single_net/MazeRoute.h

@@ -20,6 +20,13 @@ public:
     friend ostream &operator<<(ostream &os, const Solution &sol);
 };
 
+class Costs {
+public:
+    db::CostT g_cost;
+    db::CostT f_cost;  // g_cost + h_cost
+    db::CostT h_cost;
+    Costs(db::CostT gc, db::CostT hc, db::CostT fc) : g_cost(gc), h_cost(hc), f_cost(fc) {}
+};
 class MazeRoute {
 public:
     MazeRoute(gr::GrNet &grNetData) : grNet(grNetData) {}
@@ -33,7 +40,7 @@ private:
     GridGraph graph;
 
     // h_cost first // f_cost second // min cost upper bound for each vertex
-    vector<std::pair<db::CostT, db::CostT>> vertexCosts;
+    vector<Costs> vertexCosts;
     vector<std::shared_ptr<Solution>> pinSols;  // best solution for each pin
     vector<vector<gr::PointOnLayer>> mergedPinAccessBoxes;
 

### 2020-05-30 code/cu-gr/test1_run.sh

@@ -1,3 +1,3 @@
 cd run/;
-./iccad19gr -lef ../toys/iccad2019c/ispd18_sample/ispd18_test1.input.lef -def ../toys/iccad2019c/ispd18_sample/ispd18_test1.input.def -output ispd18_test1.solution.guide -threads 20;
+./iccad19gr -lef ../toys/iccad2019c/ispd18_sample/ispd18_test1.input.lef -def ../toys/iccad2019c/ispd18_sample/ispd18_test1.input.def -output ispd18_test1.solution.guide -threads 1;
 cd ..;

### 2020-05-30 code/cu-gr/test2_run.sh

@@ -1,0 +1,3 @@
+cd run/;
+./iccad19gr -lef ../toys/iccad2019c/ispd18_sample/ispd18_test2.input.lef -def ../toys/iccad2019c/ispd18_sample/ispd18_test2.input.def -output ispd18_test2.solution.guide -threads 1;
+cd ..;

### 2020-05-30 code/cu-gr/test3_run.sh

@@ -1,0 +1,3 @@
+cd run/;
+./iccad19gr -lef ../toys/iccad2019c/ispd18_sample/ispd18_test3.input.lef -def ../toys/iccad2019c/ispd18_sample/ispd18_test3.input.def -output ispd18_test3.solution.guide -threads 1;
+cd ..;

### 2020-05-30 code/cu-gr/test4_run.sh

@@ -1,0 +1,3 @@
+cd run/;
+./iccad19gr -lef ../toys/iccad2019c/ispd18_sample/ispd18_test4.input.lef -def ../toys/iccad2019c/ispd18_sample/ispd18_test4.input.def -output ispd18_test4.solution.guide -threads 1;
+cd ..;

### 2020-05-30 code/cu-gr/test7_run.sh

@@ -1,3 +1,0 @@
-cd run/;
-./iccad19gr -lef ../toys/iccad2019c/ispd18_sample/ispd18_test7.input.lef -def ../toys/iccad2019c/ispd18_sample/ispd18_test7.input.def -output ispd18_test7.solution.guide -threads 20;
-cd ..;

### 2020-05-31 paper.tex
Edit Introduction & Abstract

@@
 
-\title{Improved Global Routing Using A-Star Algorithm\\}
+\title{Improved Global Routing By Using A Star Algorithm\\}
 
@@
 
-\author{\IEEEauthorblockN{AbdElrahman Elshafei\IEEEauthorrefmark{1}, Hossam Ahmed\IEEEauthorrefmark{2}, Mahmoud Mohamed\IEEEauthorrefmark{3} and Muhanad Atef\IEEEauthorrefmark{4}}
+\author{\IEEEauthorblockN{Abdulrahman Khalid\IEEEauthorrefmark{1}, Hossam Ahmed\IEEEauthorrefmark{2}, Mahmoud Mohamed\IEEEauthorrefmark{3} and Muhanad Atef\IEEEauthorrefmark{4}}
 \IEEEauthorblockA{Computer Engineering Dept.,
@@
 Cairo, Egypt\\
-\IEEEauthorrefmark{1}abdelrahman.elshafei98@gmail.com,
+\IEEEauthorrefmark{1}abdulrahman.elshafei98@gmail.com,
 \IEEEauthorrefmark{2}hossamahmed201515@gmail.com,
@@
 \begin{abstract}
-    In this paper we want to improve routing by improving global routing, this can be done by using A-Star algorithm, which will reduce time taken in this process and achieve the minimum wire length, many comparisons are taken in this paper with different algorithms to find the optimum algorithm to be used to achieve both minimum wire length and minimum time taken.
-From the comparisons of the paper we can find that using any algorithm is a trade off as when we decrease time taken, the wire length is increased and vice versa, so we cannot find an algorithm which is better from the other algorithms in general but we can say that using A-Star algorithm is a good approach to be used in global routing as it decreases the routing time however it is not the the best achieveable time but it is better than many other algorithms, and it is the best algorithm to achieve the minimum wire length with this complexity.
+    In this paper VLSI routing is improved by improving global routing, this can be done by using A-Star with heuristic cost function that has parameters which affect the time taken by the router on changing instead of Dijkstra's algorithm in finding path, which will reduce time taken in this process and achieve the minimum wirelength, many comparisons are taken in this paper with different algorithms to find the optimum algorithm to be used to achieve both minimum wirelength and minimum time taken.
+From the comparisons of the paper we can find that using any algorithm is a trade off as when time taken is decreased, the wirelength is increased and vice versa, so there is no algorithm which is better from the other algorithms in general but using A-Star algorithm with the heuristic function in finding path is a good approach to be used in global routing as it decreases the routing time and achieve the minimum wirelength.
 \end{abstract}
@@
 Routing is critical step in physical design process.
-Until now the optimum solution for VLSI routing has not been achieved yet, so it is considered as a very interesting challenging feild.
+Until now the optimum solution for VLSI routing has not been achieved yet, so it is considered as a very interesting challenging field.
 It is exactly done in two steps, global routing and detailed routing.
 At first global routing is run which is the responsible for making an approximate routing for the whole circuit in order to be used as a guide for detailed routing, then the detailed routing is run to make the exact routing for the system.
-That means if global or detailed routing is improved the whole routing process is improved, but there are many problems we have to overcome to make a correct routing process.
-First of all we have to take into consideration the scale, as millions of wires exist in a small chip area which means that many kilometers of wires are placed in a very small area, so we have to minimize total wire length as much as we can, also we know that as the wire length increases the resistance increases as well which means more delay in the chip.
-We can find another problem as circuits are made in nano-scale which means that its geometric will be complex.
-Another problem that routing algorithm have to be applicable for more than one layer with different costs.
-We also have to take into consideration the direction of wires in every layer (vertical | horizontal) and no diagonal pathes, then to go from source 'S' to target 'T' the path taken should be in (vertical | horizontal) directions thet specified by the layer (at each layer wires are placed in one direction only), then there is another problem as when a wire goes from layer to another to continue on the perpendicular direction it have to go through via which have a high resistance.
+That means if global or detailed routing is improved the whole routing process is improved, but there are many problems that have to be overcame to make a correct routing process.
+First of all the scale has to be taken into consideration, as millions of wires exist in a small chip area which means that many kilometers of wires are placed in a very small area, so wetotal wirelength has to be minimized as much as possible, also it is known that as the wirelength increases the resistance increases as well which means more delay in the chip.
+There is another problem as circuits are made in nano-scale which means that its geometric will be complex.
+Another problem is that routing algorithm have to be applicable for more than one layer with different costs.
+The direction of wires also have to taken into consideration as the direction of wires in every layer can be either vertical or horizontal and no diagonal paths, then to go from source 'S' to target 'T' the path taken should be in (vertical | horizontal) directions that specified by the layer (at each layer wires are placed in one direction only), then there is another problem as when a wire goes from layer to another to continue on the perpendicular direction it have to go through via which have a high resistance.
 DFM (design for manufacturer) rules also has to be achieved.
@@
 }
-\caption{Global routing to get the best pathes}
+\caption{Finding path in global routing}
 \label{fig:GlobalRoutingProcess}
@@
 Figure~\ref{fig:GlobalRoutingProcess} shows a very simple approach of how the global router works.
-At (a) the source and target of both (A,B) need to be connected ignoring obstacles, nevertheless we can observe that the global router have to iterate to get the best routing pathes, at (b) (B,B) connected but there is no way to connect (A,A) as when (B,B) connected together they blocked the way for (A,A) to be connected, after some iterations we can find the figure at (c) in which (A,A) and (B,B) connected correctly, but there is a problem, the (A,A) connection is not the optimal path as there are pathes which achieve less wire length, so the global router have to iterate until reaching the optimal path.
+At (a) the source and target of both (A,B) need to be connected ignoring obstacles, nevertheless we can observe that the global router have to iterate to get the best routing paths, at (b) (B,B) connected but there is no way to connect (A,A) as when (B,B) connected together they blocked the way for (A,A) to be connected, after some iterations we can find the figure at (c) in which (A,A) and (B,B) connected correctly, but there is a problem, the (A,A) connection is not the optimal path as there are paths which achieve less wirelength, so the global router have to iterate until reaching the optimal path.
 These iterations are done for only two connections in one layer without obstacles, then how about millions of wires in VLSI?
@@
 
-Several papers proposed various types of approaches to improve the overall efficiency of the multilevel feedback queue scheduling algorithm.
-The chosen quantum time for each queue plays a major role.
-Hence, it is essential to choose a proper method to compute the time quantum value to minimize response time and maximize overall performance.
-In , an algorithm is introduced for minimizing the response time.
-In this algorithm, a Recurrent Neural Network (RNN) is used to determine both the number of queues and the optimized time quantum value for each queue.
-The RNN generates an effective model to compute the time quantum value.
-Their proposed intelligent version of the MLFQ offers good results, however, it suffers from a few drawbacks, the first being the direct proportionality of its network learning time and the amount of input data, and the second is the possibility of experiencing initial overhead at the first iterations of the algorithm.
-Our approach proposes an improved version of MLFQ that utilizes an altered version of RR named shortest remaining burst round-robin (SRBRR) introduced in  which avoids the cost of learning time and overhead time in .
-Regarding the various approaches to improve the MLFQ algorithm, those attempts dealt with starvation by assigning different quantum values to the ready queues depending on their priority.
-Our approach also deals with starvation by boosting processes from lower priority queues to higher ones according to certain criteria.
+Several papers proposed various types of approaches to improve the routing process, each of them tried to improve the overall routing by improving one or more parameters, some paperes tried to decrease number of vias, other papers tried to decrease the time taken and so on.
+In \cite{b2} they used two bounded length maze algorithms as finding path algorithms in order to make the router faster, the first one is optimal-BLMR which is used to get the minimum cost paths to be used as a routing paths, this can be done in three steps, first BLC (bounded length constraint) is defined as grater than Manhattan distance then to go from source to target the neighbour points are tested if it can be a part of path or not, each point that violates the BLC constraint is discarded, second
 
@@
 
+\bibitem{b2} Liu, Wen-Hao, et al.
+"NCTU-GR 2.0: Multithreaded collision-aware global routing with bounded-length maze routing." \textit{IEEE Transactions on computer-aided design of integrated circuits and systems} 32.5 (2013): 709-722.
+
 \end{thebibliography}

### 2020-05-31 paper.tex

@@
 Several papers proposed various types of approaches to improve the routing process, each of them tried to improve the overall routing by improving one or more parameters, some paperes tried to decrease number of vias, other papers tried to decrease the time taken and so on.
-In \cite{b2} they used two bounded length maze algorithms as finding path algorithms in order to make the router faster, the first one is optimal-BLMR which is used to get the minimum cost paths to be used as a routing paths, this can be done in three steps, first BLC (bounded length constraint) is defined as grater than Manhattan distance then to go from source to target the neighbour points are tested if it can be a part of path or not, each point that violates the BLC constraint is discarded, second
+In \cite{b2} they used a sequential global routing and they provided two bounded length maze algorithms as finding path algorithms in order to make the router faster and to avoid congestions thus avoiding overflow, the first one is optimal-BLMR and the second one is heuristic-BLMR.
+optimal-BLMR is used to get the minimum cost paths to be used as a routing paths, this can be done in three steps.
+First BLC (bounded length constraint) is defined as a grater number than Manhattan distance then to go from source to target the neighbour points are tested if it can be a part of path or not, each point that violates the BLC constraint is discarded.
+Second if the route started from point \textit{v} and ended at point \textit{u} and there was many paths between these two points, the normal maze algorithm wwill take the path with minimum cost which may cause the route get into congestions, bun in optimal-BLMR they keep track of all paths between these two points in order to choose the path that will not cause overflow, it iterates on the minimum cost path everytime and if it found a suitable path it reserves that path otherwise it discard that path.
+Third step the optimal-BLMR iterates on the reserved paths and choose the one to be used for routing.
+In heuristic-BLMR they tried to speed the router up by reserving only one path between the two points, but they also wanted to keep the advantage of optimal-BLMR (avoidng congestions) and this can be achieved by choosing the selected path only if the wirelength is enough to detour around congested regions.
+The advantages of this paper are using sequential global routing which is based on multithreaded global routing which speedup the router, avoiding collision by using optimal-BLMR, and making a fast and nearly avoiding collision algorithm (heuristic-BLMR).
+But there are some disadvanatges too, as optimal-BLMR is very slow to be used, although heuristic-BLMR is faster than optimal-BLMR its results are not accurate as the wirelength is not the best compared with other papers.
 

### 2020-05-31 paper.tex
change format

@@
+%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
+%% Do not edit unless you really know what you are doing.
 \documentclass[conference]{IEEEtran}
+\usepackage[latin9]{inputenc}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{amsmath}
+\usepackage{amssymb}
+
+\makeatletter
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+%% Because html converters don't know tabularnewline
+\providecommand{\tabularnewline}{\\}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
 \IEEEoverridecommandlockouts
@@
 \usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithm}
+\usepackage{amsfonts}\usepackage{algorithm}
 \usepackage{algpseudocode}
@@
 
-\makeatletter
-\newcommand\fs@norules{\def\@fs@cfont{\bfseries}\let\@fs@capt\floatc@ruled
+\newcommand{\fs@norules}{\def\@fs@cfont{\bfseries}\let\@fs@capt\floatc@ruled
     \def\@fs@pre{}%
@@
     \let\@fs@iftopcapt\iftrue}
-\makeatother
 
@@
 
-\newcommand\T{\rule{0pt}{2.6ex}}       % Top strut
-\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut
+\newcommand{\T}{\rule{0pt}{2.6ex}}       % Top strut
+\newcommand{\B}{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut
+
+\makeatother
 
 \begin{document}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\title{Improved Global Routing By Using A Star Algorithm\\}
+\title{Improved Global Routing By Using A Star Algorithm}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AUTHORS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\author{\IEEEauthorblockN{Abdulrahman Khalid\IEEEauthorrefmark{1}, Hossam Ahmed\IEEEauthorrefmark{2}, Mahmoud Mohamed\IEEEauthorrefmark{3} and Muhanad Atef\IEEEauthorrefmark{4}}
-\IEEEauthorblockA{Computer Engineering Dept.,
-Faculty of Engineering, Cairo University\\
+\author{\IEEEauthorblockN{Abdulrahman Khalid\IEEEauthorrefmark{1}, Hossam Ahmed\IEEEauthorrefmark{2},
+Mahmoud Mohamed\IEEEauthorrefmark{3} and Muhanad Atef\IEEEauthorrefmark{4}} \IEEEauthorblockA{Computer Engineering Dept., Faculty of Engineering, Cairo University\\
  Cairo, Egypt\\
-\IEEEauthorrefmark{1}abdulrahman.elshafei98@gmail.com,
-\IEEEauthorrefmark{2}hossamahmed201515@gmail.com,
-\IEEEauthorrefmark{3}mmmacmp@gmail.com,
-\IEEEauthorrefmark{4}muhanad.atef23@gmail.com}}
+ \IEEEauthorrefmark{1}abdulrahman.elshafei98@gmail.com, \IEEEauthorrefmark{2}hossamahmed201515@gmail.com,
+\IEEEauthorrefmark{3}mmmacmp@gmail.com, \IEEEauthorrefmark{4}muhanad.atef23@gmail.com}}
 
 \maketitle
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{abstract}
-    In this paper VLSI routing is improved by improving global routing, this can be done by using A-Star with heuristic cost function that has parameters which affect the time taken by the router on changing instead of Dijkstra's algorithm in finding path, which will reduce time taken in this process and achieve the minimum wirelength, many comparisons are taken in this paper with different algorithms to find the optimum algorithm to be used to achieve both minimum wirelength and minimum time taken.
-From the comparisons of the paper we can find that using any algorithm is a trade off as when time taken is decreased, the wirelength is increased and vice versa, so there is no algorithm which is better from the other algorithms in general but using A-Star algorithm with the heuristic function in finding path is a good approach to be used in global routing as it decreases the routing time and achieve the minimum wirelength.
+In this paper VLSI routing is improved by improving global routing,
+this can be done by using A-Star with heuristic cost function that
+has parameters which affect the time taken by the router on changing
+instead of Dijkstra's algorithm in finding path, which will reduce
+time taken in this process and achieve the minimum wirelength, many
+comparisons are taken in this paper with different algorithms to find
+the optimum algorithm to be used to achieve both minimum wirelength
+and minimum time taken. From the comparisons of the paper we can find
+that using any algorithm is a trade off as when time taken is decreased,
+the wirelength is increased and vice versa, so there is no algorithm
+which is better from the other algorithms in general but using A-Star
+algorithm with the heuristic function in finding path is a good approach
+to be used in global routing as it decreases the routing time and
+achieve the minimum wirelength. 
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{IEEEkeywords}
-VLSI Routing, Global Routing, Routing Algorithms, Fast Global Routing, Fast Routing Algorithms, Routing Algoritms Comparisons.
+VLSI Routing, Global Routing, Routing Algorithms, Fast Global Routing,
+Fast Routing Algorithms, Routing Algoritms Comparisons. 
 \end{IEEEkeywords}
@@
 
-Routing is critical step in physical design process.
-Until now the optimum solution for VLSI routing has not been achieved yet, so it is considered as a very interesting challenging field.
-It is exactly done in two steps, global routing and detailed routing.
-At first global routing is run which is the responsible for making an approximate routing for the whole circuit in order to be used as a guide for detailed routing, then the detailed routing is run to make the exact routing for the system.
-That means if global or detailed routing is improved the whole routing process is improved, but there are many problems that have to be overcame to make a correct routing process.
-First of all the scale has to be taken into consideration, as millions of wires exist in a small chip area which means that many kilometers of wires are placed in a very small area, so wetotal wirelength has to be minimized as much as possible, also it is known that as the wirelength increases the resistance increases as well which means more delay in the chip.
-There is another problem as circuits are made in nano-scale which means that its geometric will be complex.
-Another problem is that routing algorithm have to be applicable for more than one layer with different costs.
-The direction of wires also have to taken into consideration as the direction of wires in every layer can be either vertical or horizontal and no diagonal paths, then to go from source 'S' to target 'T' the path taken should be in (vertical | horizontal) directions that specified by the layer (at each layer wires are placed in one direction only), then there is another problem as when a wire goes from layer to another to continue on the perpendicular direction it have to go through via which have a high resistance.
-DFM (design for manufacturer) rules also has to be achieved.
-All of these constraints must be taken into consideration with the global routing to achieve hundred percent of the circuit connections, that means global routing will take a lot of time to achieve all these constraints, and here is the challenge to achieve all the routing specifications with minimum time taken.
+Routing is critical step in physical design process. Until now the
+optimum solution for VLSI routing has not been achieved yet, so it
+is considered as a very interesting challenging field. It is exactly
+done in two steps, global routing and detailed routing. At first global
+routing is run which is the responsible for making an approximate
+routing for the whole circuit in order to be used as a guide for detailed
+routing, then the detailed routing is run to make the exact routing
+for the system. That means if global or detailed routing is improved
+the whole routing process is improved, but there are many problems
+that have to be overcame to make a correct routing process. First
+of all the scale has to be taken into consideration, as millions of
+wires exist in a small chip area which means that many kilometers
+of wires are placed in a very small area, so wetotal wirelength has
+to be minimized as much as possible, also it is known that as the
+wirelength increases the resistance increases as well which means
+more delay in the chip. There is another problem as circuits are made
+in nano-scale which means that its geometric will be complex. Another
+problem is that routing algorithm have to be applicable for more than
+one layer with different costs. The direction of wires also have to
+taken into consideration as the direction of wires in every layer
+can be either vertical or horizontal and no diagonal paths, then to
+go from source 'S' to target 'T' the path taken should be in (vertical
+\textbar{} horizontal) directions that specified by the layer (at
+each layer wires are placed in one direction only), then there is
+another problem as when a wire goes from layer to another to continue
+on the perpendicular direction it have to go through via which have
+a high resistance. DFM (design for manufacturer) rules also has to
+be achieved. All of these constraints must be taken into consideration
+with the global routing to achieve hundred percent of the circuit
+connections, that means global routing will take a lot of time to
+achieve all these constraints, and here is the challenge to achieve
+all the routing specifications with minimum time taken.
 
 \begin{figure}
-\centering  
-\subfigure[Before routing] {
-    \begin{tikzpicture}
-        [
+\centering \subfigure[Before routing]{ \begin{tikzpicture}[
             box/.style={rectangle,draw=black,thick, minimum size=0.5cm},
@@
     \node [box,fill=red] at (2.5,0.5){B}; 
-    \end{tikzpicture}
-}
-\subfigure[Iteration number x] {
-    \begin{tikzpicture}
-        [
+    \end{tikzpicture} } \subfigure[Iteration number x]{ \begin{tikzpicture}[
             box/.style={rectangle,draw=black,thick, minimum size=0.5cm},
@@
     \node [box,fill=red] at (1.5,2){};
-    \end{tikzpicture}
-}
-\subfigure[Iteration number y] {
-    \begin{tikzpicture}
-        [
+    \end{tikzpicture} } \subfigure[Iteration number y]{ \begin{tikzpicture}[
             box/.style={rectangle,draw=black,thick, minimum size=0.5cm},
@@
     \node [box,fill=red] at (2,2.5){};
-    \end{tikzpicture}
-}
-\subfigure[After N iteration] {
-    \begin{tikzpicture}
-        [
+    \end{tikzpicture} } \subfigure[After N iteration]{ \begin{tikzpicture}[
             box/.style={rectangle,draw=black,thick, minimum size=0.5cm},
@@
     \node [box,fill=red] at (2,2.5){};
-    \end{tikzpicture}
-}
-\caption{Finding path in global routing}
+    \end{tikzpicture} } \caption{Finding path in global routing}
 \label{fig:GlobalRoutingProcess} 
@@
 
-Figure~\ref{fig:GlobalRoutingProcess} shows a very simple approach of how the global router works.
-At (a) the source and target of both (A,B) need to be connected ignoring obstacles, nevertheless we can observe that the global router have to iterate to get the best routing paths, at (b) (B,B) connected but there is no way to connect (A,A) as when (B,B) connected together they blocked the way for (A,A) to be connected, after some iterations we can find the figure at (c) in which (A,A) and (B,B) connected correctly, but there is a problem, the (A,A) connection is not the optimal path as there are paths which achieve less wirelength, so the global router have to iterate until reaching the optimal path.
-These iterations are done for only two connections in one layer without obstacles, then how about millions of wires in VLSI?
-this shows how much the global routing algorithm has to be very fast in order to connect this huge number of wires as fast as possible.
+Figure~\ref{fig:GlobalRoutingProcess} shows a very simple approach
+of how the global router works. At (a) the source and target of both
+(A,B) need to be connected ignoring obstacles, nevertheless we can
+observe that the global router have to iterate to get the best routing
+paths, at (b) (B,B) connected but there is no way to connect (A,A)
+as when (B,B) connected together they blocked the way for (A,A) to
+be connected, after some iterations we can find the figure at (c)
+in which (A,A) and (B,B) connected correctly, but there is a problem,
+the (A,A) connection is not the optimal path as there are paths which
+achieve less wirelength, so the global router have to iterate until
+reaching the optimal path. These iterations are done for only two
+connections in one layer without obstacles, then how about millions
+of wires in VLSI? this shows how much the global routing algorithm
+has to be very fast in order to connect this huge number of wires
+as fast as possible.
 
@@
 
-Several papers proposed various types of approaches to improve the routing process, each of them tried to improve the overall routing by improving one or more parameters, some paperes tried to decrease number of vias, other papers tried to decrease the time taken and so on.
-In \cite{b2} they used a sequential global routing and they provided two bounded length maze algorithms as finding path algorithms in order to make the router faster and to avoid congestions thus avoiding overflow, the first one is optimal-BLMR and the second one is heuristic-BLMR.
-optimal-BLMR is used to get the minimum cost paths to be used as a routing paths, this can be done in three steps.
-First BLC (bounded length constraint) is defined as a grater number than Manhattan distance then to go from source to target the neighbour points are tested if it can be a part of path or not, each point that violates the BLC constraint is discarded.
-Second if the route started from point \textit{v} and ended at point \textit{u} and there was many paths between these two points, the normal maze algorithm wwill take the path with minimum cost which may cause the route get into congestions, bun in optimal-BLMR they keep track of all paths between these two points in order to choose the path that will not cause overflow, it iterates on the minimum cost path everytime and if it found a suitable path it reserves that path otherwise it discard that path.
-Third step the optimal-BLMR iterates on the reserved paths and choose the one to be used for routing.
-In heuristic-BLMR they tried to speed the router up by reserving only one path between the two points, but they also wanted to keep the advantage of optimal-BLMR (avoidng congestions) and this can be achieved by choosing the selected path only if the wirelength is enough to detour around congested regions.
-The advantages of this paper are using sequential global routing which is based on multithreaded global routing which speedup the router, avoiding collision by using optimal-BLMR, and making a fast and nearly avoiding collision algorithm (heuristic-BLMR).
-But there are some disadvanatges too, as optimal-BLMR is very slow to be used, although heuristic-BLMR is faster than optimal-BLMR its results are not accurate as the wirelength is not the best compared with other papers.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROPOSED APPROACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Proposed Approach}
-
-For a multilevel feedback queue scheduling algorithm, three parameters are considered.
-The first is the chosen scheduling algorithm for each queue, especially the last queue as its scheduling algorithm is expected to treat starvation.
-The second is the criteria according to which a process is promoted, this technique is also known as Aging.
-The third is the criteria according to which a process is demoted.
-In our proposed algorithm, there are 5 queues sorted in ascending order in line with their priority number, 1 being the highest priority and 5 being the lowest.
-Each queue uses a modified version of the round-robin scheduling algorithm stated in {b3}.
-In {b3}, processes are sorted in ascending order according to their burst time and are assigned a time quantum that equals the median burst time of those processes.
-This algorithm provides better turnaround time and waiting time than the standard static quantum RR algorithm whose quantum, if set too short, leads to many context switches and, if set too long, morphs the algorithm into an FCFS algorithm.
-The proposed alteration on the stated algorithm in {b3} is that each queue quantum time equals the median burst time multiplied by a factor matching the queue number.
-Hence, the gradual increase of quantum time as priority decreases.
-For clarification, a queue with priority equal $2$ has the following processes denoted by their burst time: $100$, $300$, $550$, $600$, $620$, $700$, $720$, $900$ and $1200$, the median value is $620$, since we are in a queue whose priority equals $2$, therefore the quantum slice value according to the proposed approach equals $1240$ as in $620 * 2$.
-If processes of a certain queue didn't terminate after assigning the quantum time value, they are shifted to the next lower priority queue.
-After introducing new processes into a queue, the quantum time slice is recalculated.
-Processes age whenever they are in a queue whose priority is one less than that currently getting scheduled and satisfies the following inequality:
-\begin{equation}
-\frac{waiting \; time \; of \; P}{burst \; time \; of \; P} >= 1\label{eq1}
-\end{equation}
-
-Those procedures are repeated for all the generated queues until all processes reach the lowest priority queue where they are rescheduled until their completion.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FLOWCHART %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Pseudocode Flowchart of the Proposed Approach}
-\begin{tikzpicture}[node distance=2.2cm]
-
-    \node (start) [startstop] {Start};
-    \node (in1) [io, below of=start, text width = 2cm] {Read Processes Data};
-    \node (dec1) [decision, below of=in1, text width = 2cm, yshift=-1cm] {All processes are finished};
-    \node (pro1) [process, below of=dec1, text width= 3cm, yshift = -1cm] {Iterate on queues $Q$};
-    \node (pro2) [process, below of=pro1, text width = 3cm] {Assign eligable processes to the current queue};
-    \node (out1) [io, left of=dec1, text width = 2cm, xshift= -2cm] {Print avg. waiting time, avg. turnaround time, throughput};
-    \node (end) [startstop, below of=out1, yshift=-1cm] {End};
-    \node (dec2) [decision, below of=pro2, text width = 2cm, yshift=-2cm] {A process $P$ in the subsequent queue is boostable};
-
-    \node (pro3) [process, left of=dec2, text width= 3cm, xshift= -2.5cm] {Promote $P$ to current queue};
-    \node (pro4) [process, below of=dec2, text width= 3cm, yshift=-2.2cm] {Calculate the quantum time value $\phi$};
-    \node (pro5) [process, below of=pro4, text width= 3cm] {Schedule processes in current queue};
-
-    \draw [arrow] (start) -- (in1);
-    \draw [arrow] (in1) -- (dec1);
-    % \draw [arrow] (pro1) -- (dec1);
-    \draw [arrow] (dec1) -- node[anchor=west, above] {Yes} (out1);
-    \draw [arrow] (out1) -- (end);
-    \draw [arrow] (dec1) -- node[anchor=south, left] {No} (pro1);
-    \draw [arrow] (pro1) -- (pro2);
-    \draw [arrow] (pro2) -- (dec2);
-    \draw [arrow] (dec2) -- node[anchor=west,above] {Yes} (pro3);
-    \draw [arrow] (pro3.north) -- ++ (0,3.7) -- ++ (3.1,0);
-    \draw [arrow] (dec2) -- node[anchor=south, left] {No} (pro4);
-    \draw [arrow] (pro4) -- (pro5);
-    \draw [arrow] (pro5.east) -- ++ (1.2,0) -- ++(0,16.2) -- ++(-1.3,0);
-    \end{tikzpicture}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALGORITHM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Proposed Algorithm}
-% \floatstyle{norules}
-\restylefloat{algorithm}
-\begin{algorithm}[H]
-    \caption{Developed Multilevel Feedback Queue Scheduling Algorithm}
-    \hspace*{\algorithmicindent} \textbf{Input:} Number of processes $n$, processes priority $\alpha$\\
-    \hspace*{\algorithmicindent} burst time values $\beta$, arrival time values $\sigma$, \\
-    \hspace*{\algorithmicindent} context switching cost $\epsilon$\\
-    \hspace*{\algorithmicindent} \textbf{Output:} Average turnaround time, average waiting time,\\
-    \hspace*{\algorithmicindent} throughput
-    \begin{algorithmic}[1]
-    \Procedure {DMLFQ}{}
-    % Return  Average waiting time, throughput
-    \Statex Declaration and Initialisation:
-    \State Queue $Q_{i}$ where $i \in \{1, 2, 3, 4, 5\}$
-    \State Turnaround time values $\tau$
-    \State Finish time values $\lambda$
-    \State Waiting time values $\theta$
-    \State Remaining time values $\mu = \beta$
-    \State Quantum time value $\phi$
-    \State Number of context switches $\delta$
-        \State$time = 0$
-        \While{$\exists P \in Q$}
-            \For{$i = 1$ to $5$}
-                \For{$j = 1$ to $n$}
-                    \If{$\sigma_{j} <= time$ and $\alpha_{j}$ equals $i$}
-                        \State \textit{\textbf{Assign}} $P_{j}$ to $Q_{i}$
-                    \EndIf
-                    \State $waitingTime = time - \sigma_{j}$
-                    \If{$i < 5$ and $waitingTime/\mu_{j} >= 1$ and $\alpha_{j}$ equals $i + 1$ and  $\sigma_{j} <= time$}
-                        \State \textit{\textbf{Assign}} $P_{j}$ to $Q_{i}$
-                    \EndIf
-                \EndFor
-                \State Sort $Q_{i}$ in ascending order according to remaining time values
-                \State $\phi = median\; value\; of\; Q_{i} * i$
-                \algrenewcommand\algorithmicfor{\textbf{foreach}}
-                \For{$P_{j} \in Q_{i}$}
-                    \If{$\mu_{j} <= \phi$}
-                        \State $time = time + \mu_{j}$
-                        \State $\lambda_{j} = time$
-                        \State \textit{\textbf{Remove}} $P_{j}$ from $Q_{i}$
-                    \Else
-                        \State $time = time + \phi$
-                        \State $\mu_{j} = \mu_{j} - \phi$
-                        \If{$i < 5$}
-                            \State $\alpha_{j} = \alpha_{j} + 1$
-                        \EndIf
-                    \EndIf
-                    \If{Previous process $\neq P_{j}$}
-                        \State $time = time + \epsilon$
-                        \State $\delta = \delta + 1$
-                    \EndIf
-                \EndFor
-                \algrenewcommand\algorithmicfor{\textbf{for}}
-            \EndFor
-        \EndWhile
-        \For{$i = 1$ to $n$}
-            $\tau_{j} = \lambda_{j} - \sigma_{j}$, $\theta_{j} = \tau_{j} - \beta_{j}$
-        \EndFor
-        \State \textbf{return} average of $\theta$, average of $\tau$, $n/time$
-        \EndProcedure
-    \end{algorithmic}
-\end{algorithm}
+Several papers proposed various types of approaches to improve the
+routing process, each of them tried to improve the overall routing
+by improving one or more parameters, some paperes tried to decrease
+number of vias, other papers tried to decrease the time taken and
+so on. In \cite{b2} they used a sequential global routing and they
+provided two bounded length maze algorithms as finding path algorithms
+in order to make the router faster and to avoid congestions thus avoiding
+overflow, the first one is optimal-BLMR and the second one is heuristic-BLMR.
+optimal-BLMR is used to get the minimum cost paths to be used as a
+routing paths, this can be done in three steps. First BLC (bounded
+length constraint) is defined as a grater number than Manhattan distance
+then to go from source to target the neighbour points are tested if
+it can be a part of path or not, each point that violates the BLC
+constraint is discarded. Second if the route started from point \textit{v}
+and ended at point \textit{u} and there was many paths between these
+two points, the normal maze algorithm wwill take the path with minimum
+cost which may cause the route get into congestions, bun in optimal-BLMR
+they keep track of all paths between these two points in order to
+choose the path that will not cause overflow, it iterates on the minimum
+cost path everytime and if it found a suitable path it reserves that
+path otherwise it discard that path. Third step the optimal-BLMR iterates
+on the reserved paths and choose the one to be used for routing. In
+heuristic-BLMR they tried to speed the router up by reserving only
+one path between the two points, but they also wanted to keep the
+advantage of optimal-BLMR (avoidng congestions) and this can be achieved
+by choosing the selected path only if the wirelength is enough to
+detour around congested regions. The advantages of this paper are
+using sequential global routing which is based on multithreaded global
+routing which speedup the router, avoiding collision by using optimal-BLMR,
+and making a fast and nearly avoiding collision algorithm (heuristic-BLMR).
+But there are some disadvanatges too, as optimal-BLMR is very slow
+to be used, although heuristic-BLMR is faster than optimal-BLMR its
+results are not accurate as the wirelength is not the best compared
+with other papers.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ASSUMPTIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+we implement global routing with A\_Star router algorithm in c++ language
+with Rsyn to parse input test cases files with format LEF/DEF. All
+experiments are perfromed on a Machine with 2 GHZ intel Processor
+and 8 GB RAM. our algorithm is focus on three important factors :total
+wire-lenght, channel congestion ,number of vias. Our target is to
+minimize a convex combination of the total wire-lenght and the number
+of vias that represent the bends in the tree that result in solving
+the net of pins to be connected.our test cases input are all from
+ICCAD'19 contest for global routing.we test our code with different
+heurestic function -that affect the run time of A{*}- to check its
+effect on CPU time.our concern is on wire-lengh and number of vias
+result from routing.
 
-\subsection{Assumptions}
+\subsubsection{Experiment1}
 
-The proposed scheduling algorithm is software simulated using a Python script which simulates scheduling independent CPU-bound processes on a single processor environment which guarantees that no more than a single process is getting scheduled at any arbitrary moment.
-Each process is assumed to have its own predetermined burst time, arrival time and the queue to which each one belongs.
-The proposed approach is non-preemptive.
-For the sake of giving an example, if a process was lately introduced to a queue denoted by $Q_{i}$ prior to the current queue getting scheduled, it won't get scheduled until the current queue, its subsequent queues and the queues prior to $Q_{i}$ get scheduled.
+in this experiment we compare run time of router with dijkstra Router
+and out A{*} router with heurestic function with differents constants
+of heurestic functions that affect the run time of the router:
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% I/O %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\scriptsize{}$Heurestic-Fucntion1=(|p_{1}.x-p_{2}.x|+|p_{1}.y-p_{2}.y|*const1)+(|p_{1}.layer-p_{2}.layer|)*const2)$}{\scriptsize\par}
 
-\subsection{Experimental Scheme}
+{\scriptsize{}$Heurestic-Fucntion2=(ln(|p_{1}.x-p_{2}.x|+|p_{1}.y-p_{2}.y|)*const1)+(|p_{1}.layer-p_{2}.layer|)*const2)$}{\scriptsize\par}
 
-On one hand, the input arguments to the proposed algorithm implementation are the number of processes to be scheduled, their burst time, their arrival time and the queue where each one belongs.
-On the other hand, output parameters are the average waiting time, average turnaround time and throughput.
-The following equations are used to calculate the previously mentioned output parameters:
+{\scriptsize{}$Heurestic-Fucntion3=(|p_{1}.x-p_{2}.x|+|p_{1}.y-p_{2}.y|*const1)+(ln(|p_{1}.layer-p_{2}.layer|)*const2)$}{\scriptsize\par}
 
-\begin{equation}
-    Average\; Waiting\; Time =  \frac{Total \; Waiting \; Time}{Number \; of \; Processes} \label{eq2}
-\end{equation}
+{\tiny{}}
+\begin{table}
+{\tiny{}\caption{Compare run time of Dijkstra router and A{*} router with different
+heuristic function}
+}{\tiny\par}
 
-\begin{equation}
-    Average\; Turnaround\; Time =  \frac{Total \; Turnaround \; Time}{Number \; of \; Processes} \label{eq3}
-\end{equation}
-
-\begin{equation}
-    Throughput =  \frac{Number \; of \; Executed \; Processes}{Total \; Execution \; Time} \label{eq4}
-\end{equation}
-
-% \vspace{4mm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PERFORMANCE METRICS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Performance Metrics}
-
-As a means to have a concrete, viable evaluation of either the proposed algorithm or any other scheduling algorithm, the output parameters are taken into consideration for analysis.
-Since the average waiting time indicates the average time that a  process had to starve for, therefore the lower the average waiting time is the better.
-The same principle applies to the average turnaround time and the number of context switches, as the former implies the average time spent by the process since its arrival time to its completion and the latter costs time as the CPU is assigned back and forth between different processes.
-Contrarily to the prior metrics, the larger the throughput is the better as it indicates the number of processes that are completely executed per unit time.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SIMULATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Simulation}
-
-For the sake of showcasing the proposed algorithm, a number of processes, their predetermined burst time values and their arrival time values are taken as input to the Python simulation script.
-Suppose that the input to the script is according to the following table:
-
-\begin{table}[H]
-    \caption{}
-    \centering
-     \begin{tabular}{||c c c c||} 
+{\tiny{}}%
+\begin{tabular}{|c|c|c|c|c||c|c|c|c|}
 \hline 
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
+\multirow{3}{*}{{\tiny{}Design}} & \multicolumn{8}{c|}{{\tiny{}A{*} Router}}\tabularnewline
+\cline{2-9} 
+ & \multicolumn{4}{c||}{{\tiny{}F1}} & \multicolumn{4}{c|}{{\tiny{}F2}}\tabularnewline
+\cline{2-9} 
+ & {\tiny{}(0.1,0.1)} & {\tiny{}(0.2,0.1)} & {\tiny{}(0.3,0.3)} & {\tiny{}(0.5,0.5)} & {\tiny{}(0.1,0.1)} & {\tiny{}(0.2,0.1)} & {\tiny{}(0.3,0.3)} & {\tiny{}(0.5,0.5)}\tabularnewline
 \hline 
 \hline 
-     1 & 0 & 60 & 1 \T \B \\ 
+{\tiny{}19test2} & {\tiny{}87.150469} & {\tiny{}75.843764} & {\tiny{}87.797614} & {\tiny{}87.086193} & {\tiny{}90.440165} & {\tiny{}93.288501} & {\tiny{}89.414646} & {\tiny{}96.377979}\tabularnewline
 \hline 
-     2 & 0 & 50 & 1 \T \B \\
+{\tiny{}19test3} & {\tiny{}2.489458} & {\tiny{}2.511599} & {\tiny{}2.606054} & {\tiny{}2.874605} & {\tiny{}2.461400} & {\tiny{}2.469304} & {\tiny{}2.480592} & {\tiny{}2.497377}\tabularnewline
 \hline 
-     3 & 0 & 40 & 2 \T \B \\
+{\tiny{}19test5} & {\tiny{}13.785204} & {\tiny{}12.381436} & {\tiny{}14.959666} & {\tiny{}14.859677} & {\tiny{}12.264829} & {\tiny{}13.449206} & {\tiny{}12.039944} & {\tiny{}14.766495}\tabularnewline
 \hline 
-     4 & 0 & 30 & 2 \T \B \\
+{\tiny{}sample} & {\tiny{}0.221261} & {\tiny{}0.075472} & {\tiny{}0.073069} & {\tiny{}0.073769} & {\tiny{}0.071577} & {\tiny{}0.157244} & {\tiny{}0.078624} & {\tiny{}0.072691}\tabularnewline
 \hline 
-     5 & 0 & 10 & 3 \T \B \\ 
+{\tiny{}sample2} & {\tiny{}0.096618} & {\tiny{}0.073988} & {\tiny{}0.072911} & {\tiny{}0.074165} & {\tiny{}0.078316} & {\tiny{}0.090906} & {\tiny{}0.071333} & {\tiny{}0.072767}\tabularnewline
 \hline 
-     6 & 0 & 210 & 3 \T \B \\ 
+{\tiny{}sample3} & {\tiny{}7.002814} & {\tiny{}6.948016} & {\tiny{}6.266789} & {\tiny{}5.198969} & {\tiny{}6.893310} & {\tiny{}6.400888} & {\tiny{}6.974920} & {\tiny{}6.906992}\tabularnewline
 \hline 
-     7 & 0 & 200 & 3 \T \B \\ 
+\end{tabular}{\tiny\par}
+\end{table}
+{\tiny\par}
+
+\begin{table}
+
+{\tiny{}\caption{Continue compare run time of Dijkstra router and A{*} router with
+different heuristic function}
+}{\tiny\par}
+
+{\tiny{}}%
+\begin{tabular}{|c|c|c|c|c|c|}
 \hline 
-     \end{tabular}
-     \label{table1}
+\multirow{3}{*}{{\tiny{}Design}} & \multicolumn{4}{c|}{{\tiny{}A{*} Router}} & \multirow{3}{*}{{\tiny{}Dijkstra}}\tabularnewline
+\cline{2-5} 
+ & \multicolumn{4}{c|}{{\tiny{}F3}} & \tabularnewline
+\cline{2-5} 
+ & {\tiny{}(0.1,0.1)} & {\tiny{}(0.2,0.1)} & {\tiny{}(0.3,0.3)} & {\tiny{}(0.5,0.5)} & \tabularnewline
+\hline 
+\hline 
+{\tiny{}19test2} & {\tiny{}86.598509} & {\tiny{}83.204272} & {\tiny{}103.166426} & {\tiny{}102.378304} & {\tiny{}91.348007}\tabularnewline
+\hline 
+{\tiny{}19test3} & {\tiny{}2.481847} & {\tiny{}2.486656} & {\tiny{}3.622759} & {\tiny{}2.556863} & {\tiny{}3.435606}\tabularnewline
+\hline 
+{\tiny{}19test5} & {\tiny{}12.655603} & {\tiny{}15.447421} & {\tiny{}15.629251} & {\tiny{}20.004493} & {\tiny{}11.824573}\tabularnewline
+\hline 
+{\tiny{}sample} & {\tiny{}0.073731} & {\tiny{}0.070911} & {\tiny{}0.073468} & {\tiny{}0.103421} & {\tiny{}0.071829}\tabularnewline
+\hline 
+{\tiny{}sample2} & {\tiny{}0.078171} & {\tiny{}0.079362} & {\tiny{}0.088107} & {\tiny{}0.099699} & {\tiny{}0.071945}\tabularnewline
+\hline 
+{\tiny{}sample3} & {\tiny{}6.470339} & {\tiny{}7.195767} & {\tiny{}8.455288} & {\tiny{}7.637577} & {\tiny{}7.038505}\tabularnewline
+\hline 
+\end{tabular}{\tiny\par}
+
 \end{table}
 
-According to the proposed algorithm, the time quanta calculated are as follows:
+we notice from Table 1,Table 2 that heurestric function affect run
+time of router ,decreases it to be lower than dijkstra router's run
+time in many test cases. run time changes with the change of heuristic
+function constants. we notice that higher constants increase the run
+time and sometimes be greater than dijkstra router's runtime. Heurestic
+function 2 has ovarall results which is good than others herestics
+function, with other Heurestic functions run time may improve mostly.
 
-\begin{table}[H]
-    \caption{}
-    \centering
-     \begin{tabular}{||c c||} 
+\subsection{Performance Comparsions}
+
+we compare results of our algorithm which focus on factors - total
+wire-lenght,number of vias in the routing results - with TripleZ and
+NTUidRoute algorithms in ICCAD'19 Table 3 .threads number used in
+all cases is 8 threads. score used as unit to compare ,score of wire
+length is a function of metal pitch and wire length and weight:
+
+$WLScore=\frac{wire-length*weight}{metal-pitch}$
+
+score of vias is function of number of vias :
+
+$ViasScore=\#vias*2$
+
+{\tiny{}}
+\begin{table}
+{\tiny{}\caption{compared Wire Lengh,vias with TripleZ and NTUidRoute Algorithms in
+ICCAD'19 Global routing Contest }
+}{\tiny\par}
+
+{\tiny{}}%
+\begin{tabular}{|c|c|c|c|c|c|c|}
 \hline 
-     \textit{\textbf{Queue}} & \textit{\textbf{Quantum Value}} \T \B \\ 
+\multirow{2}{*}{{\tiny{}Design}} & \multicolumn{3}{c|}{{\tiny{}wire-length scores}} & \multicolumn{3}{c|}{{\tiny{}vias score}}\tabularnewline
+\cline{2-7} 
+ & {\tiny{}TripleZ} & {\tiny{}NTUidRoute} & {\tiny{}ours} & {\tiny{}TripleZ} & {\tiny{}NTUidRoute} & {\tiny{}ours}\tabularnewline
 \hline 
+{\tiny{}19test2} & {\tiny{}12485549.76} & {\tiny{}12992510.61} & {\tiny{}12150100} & {\tiny{}3261476.00} & {\tiny{}4017448.00} & {\tiny{}2803560}\tabularnewline
 \hline 
-     1 & 55 \T \B \\ 
+{\tiny{}19test3} & {\tiny{}569622.01} & {\tiny{}466809.64} & {\tiny{}389460} & {\tiny{}251728.00} & {\tiny{}318404.00} & {\tiny{}176728}\tabularnewline
 \hline 
-     2 & 40 \T \B \\
+{\tiny{}19test4} & {\tiny{}17800019.36} & {\tiny{}15935101.91} & {\tiny{}14663400} & {\tiny{}4265744.00} & {\tiny{}4789488.00} & {\tiny{}2666120}\tabularnewline
 \hline 
-     3 & 615 \T \B \\
+{\tiny{}19test5} & {\tiny{}2859212.04} & {\tiny{}2495661.79} & {\tiny{}2851900} & {\tiny{}695348.00} & {\tiny{}771328.00} & {\tiny{}446024}\tabularnewline
 \hline 
-     4 & 0 \T \B \\
+{\tiny{}19test7} & {\tiny{}74264784.88} & {\tiny{}65028116.52} & {\tiny{}70041500} & {\tiny{}19689760.00} & {\tiny{}23183264.00} & {\tiny{}12532800}\tabularnewline
 \hline 
-     5 & 0 \T \B \\ 
+{\tiny{}Avg} & {\tiny{}21595837.61} & {\tiny{}19383640} & {\tiny{}20019272} & {\tiny{}5632811.2} & {\tiny{}6615986.4} & {\tiny{}3725046.4}\tabularnewline
 \hline 
-     \end{tabular}
+\end{tabular}{\tiny\par}
 \end{table}
-
-All processes are sorted in ascending order according to their remaining time and are scheduled by assigning the time quantum calculated for their respective queue.
-The time spent scheduling a particular queue is the waiting time for its subsequent queues.
-
-The scheduling process goes as follows:
-
-\begin{figure}[H]
-        \begin{center}
-        \begin{tabular}{|c|c|}
-         \hline
-            $P_{2}$ & $P_{1}$\T\B\\ 
-         \hline
-        \end{tabular}
-        \end{center}
-        \begin{center}
-            \begin{tabular}{c c c}
-                   0 & 50 & 105\\ 
-            \end{tabular}
-        \end{center}
-    \caption{$Q_{1}$ Gantt Chart}
-\end{figure}
-
-Considering that each process in $Q_{1}$ is assigned a quantum value of $50$, as we reach the last process in $Q_{1}$, the total time elapsed equals $105$, which happens to be the time that all the other processes in the subsequent queues had to wait for, hence the addition of their waiting time by a value of $105$ units of time.
-
-\begin{figure}[H]
-    \begin{center}
-    \begin{tabular}{|c|c|c|c|}
-     \hline
-        $P_{1}$ & $P_{5}$ & $P_{4}$ & $P_{3}$\T\B\\ 
-     \hline
-    \end{tabular}
-    \end{center}
-    \begin{center}
-        \begin{tabular}{c c c c c}
-               105 & 110 & 120 & 150 & 190\\ 
-        \end{tabular}
-    \end{center}
-\caption{$Q_{2}$ Gantt Chart}
-\end{figure}
-
-Even though $P_{5}$ is initially assigned to $Q_{3}$ as in Table \ref{table1}, it was promoted to $Q_{2}$ due to satisfying inequality (\ref{eq1}).
-
-\begin{figure}[H]
-    \begin{center}
-    \begin{tabular}{|c|c|}
-     \hline
-        P7 & P6\T\B\\ 
-     \hline
-    \end{tabular}
-    \end{center}
-    \begin{center}
-        \begin{tabular}{c c c}
-               190 & 390 & 600\\ 
-        \end{tabular}
-    \end{center}
-\caption{$Q_{3}$ Gantt Chart}
-\end{figure}
-
-Whenever processes reach the lowest queue precompletion, they are scheduled using the RR scheduling algorithm with a relatively large quantum time value which is in most cases similar to using the FCFS algorithm because, as the time quantum value of an RR algorithm tends to infinity which could practically be a very large number relative to the available processes remaining time values, the algorithm tends to morph into the FCFS algorithm.
-This procedure is iterated until all the processes are finished.
-Simulation results are shown in the table below:
-
-\begin{table}[H]
-    \caption{}
-    \centering
-     \begin{tabular}{||c c c||} 
-     \hline
-     \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}} & \textit{\textbf{Throughput}}\T \B \\ 
-     \hline
-     \hline
-     230 & 144.3 & 0.011667 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% COMPARISONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Performance Comparisons}
-
-To assess the performance of the proposed algorithm implementation, multiple test cases are addressed and analyzed in seven different experiments.
-In each experiment, the output of the proposed algorithm implementation is compared to the output of another scheduling algorithm implementation addressed in a different paper, such as standard MLFQ algorithm with static quantum RR and other variants of MLFQ algorithms and RR algorithms.
-
-\subsubsection{Experiment 1}
-
-In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in {b4}.
-The first uses a static version of the RR algorithm for scheduling each queue, while the second variant uses a dynamic version of the RR algorithm for doing so.
-
-\begin{table}[H]
-    \caption{Experiment 1 Input}
-    \centering
-     \begin{tabular}{||c c c c||} 
-     \hline
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
-     \hline
-     \hline
-     1 & 1 & 25 & 1 \T \B \\ 
-     \hline
-     2 & 5 & 70 & 1 \T \B \\
-     \hline
-     3 & 6 & 84 & 1 \T \B \\
-     \hline
-     4 & 7 & 17 & 1 \T \B \\
-     \hline
-     5 & 8 & 35 & 1 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-\begin{table}[H]
-    \caption{Experiment 1 Results}
-    \centering
-    \begin{tabular}{||c c c||}
-        \hline
-        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
-    \hline
-    \hline
-    \textbf{Proposed Algorithm} & 115 & 68.8 \T \B\\ \hline
-    \textbf{Dynamic RR MLFQ} & 150.8 & 107.6\T \B\\ \hline
-    \textbf{Static RR MLFQ} & 161.4 & 116.2 \T \B\\ \hline
-     \end{tabular}
-\end{table}
-
-\subsubsection{Experiment 2}
-
-In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in {b4}.
-The first uses a static version of the SJFRR algorithm for scheduling each queue, while the second variant uses a dynamic version of the SJFRR algorithm for doing so.
-
-\begin{table}[H]
-    \caption{Experiment 2 Input}
-    \centering
-     \begin{tabular}{||c c c c||} 
-     \hline
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
-     \hline
-     \hline
-     1 & 1 & 25 & 1 \T \B \\ 
-     \hline
-     2 & 5 & 70 & 1 \T \B \\
-     \hline
-     3 & 6 & 84 & 1 \T \B \\
-     \hline
-     4 & 7 & 17 & 1 \T \B \\
-     \hline
-     5 & 8 & 35 & 1 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-\begin{table}[H]
-    \caption{Experiment 2 Results}
-    \centering
-    \begin{tabular}{||c c c||}
-        \hline
-        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
-    \hline
-    \hline
-    \textbf{Proposed Algorithm} & 115 & 68.8 \T \B\\ \hline
-    \textbf{Dyn. SJFRR MLFQ} & 134 & 91.8\T \B\\ \hline
-    \textbf{Stat. SJFRRMLFQ} & 143.4 & 98.2 \T \B\\ \hline
-     \end{tabular}
-\end{table}
-
-\subsubsection{Experiment 3}
-
-In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in {b5}.
-The first uses a static version of the SJFRR algorithm for scheduling each queue, while the second variant uses a dynamic version of the SJFRR algorithm for doing so.
-
-\begin{table}[H]
-    \caption{Experiment 3 Input}
-    \centering
-     \begin{tabular}{||c c c c||} 
-     \hline
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
-     \hline
-     \hline
-     1 & 0 & 8 & 1 \T \B \\ 
-     \hline
-     2 & 3 & 133 & 3 \T \B \\
-     \hline
-     3 & 2 & 21 & 2 \T \B \\
-     \hline
-     4 & 8 & 39 & 2 \T \B \\
-     \hline
-     5 & 19 & 67 & 2 \T \B \\ 
-     \hline
-     6 & 33 & 114 & 3 \T \B \\ 
-     \hline
-     7 & 33 & 54 & 2 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-\begin{table}[H]
-    \caption{Experiment 3 Results}
-    \centering
-    \begin{tabular}{||c c c||}
-        \hline
-        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
-    \hline
-    \hline
-    \textbf{Proposed Algorithm} & 151 & 88.7 \T \B\\ \hline
-    \textbf{Dyn. SJFRR MLFQ} & 252 & 119 \T \B\\ \hline
-    \textbf{Stat. SJFRR MLFQ} & 351 & 228 \T \B\\ \hline
-     \end{tabular}
-\end{table}
-
-\subsubsection{Experiment 4}
-
-In this experiment, the proposed algorithm is compared against multiple variants of the MLFQ algorithm that are stated in {b6}: standard MLFQ algorithm, a priority-based MLFQ algorithm and a vague logic-based MLFQ algorithm.
-
-\begin{table}[H]
-    \caption{Experiment 4 Input}
-    \centering
-     \begin{tabular}{||c c c c||} 
-     \hline
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
-     \hline
-     \hline
-     1 & 0 & 40 & 1 \T \B \\ 
-     \hline
-     2 & 0 & 30 & 1 \T \B \\
-     \hline
-     3 & 0 & 50 & 1 \T \B \\
-     \hline
-     4 & 2 & 70 & 1 \T \B \\
-     \hline
-     5 & 4 & 25 & 1 \T \B \\ 
-     \hline
-     6 & 6 & 60 & 1 \T \B \\ 
-     \hline
-     7 & 7 & 45 & 1 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-\begin{table}[H]
-    \caption{Experiment 4 Results}
-    \centering
-    \begin{tabular}{||c c c||}
-        \hline
-        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
-    \hline
-    \hline
-    \textbf{Proposed Algorithm} & 185.85 & 140.14 \T \B\\ \hline
-    \textbf{VMLFQ} & 190 & 170 \T \B\\ \hline
-    \textbf{MLFQ} & 232.14 & 175 \T \B\\ \hline
-    \textbf{PMLFQ} & 240 & 180 \T \B\\ \hline
-     \end{tabular}
-\end{table}
-
-\subsubsection{Experiment 5}
-
-This experiment is the same as the previous one, but with a different input test case.
-
-\begin{table}[H]
-    \caption{Experiment 5 Input}
-    \centering
-     \begin{tabular}{||c c c c||} 
-     \hline
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
-     \hline
-     \hline
-     1 & 0 & 90 & 1 \T \B \\ 
-     \hline
-     2 & 0 & 30 & 1 \T \B \\
-     \hline
-     3 & 0 & 28 & 1 \T \B \\
-     \hline
-     4 & 0 & 57 & 1 \T \B \\
-     \hline
-     5 & 0 & 73 & 1 \T \B \\ 
-     \hline
-     6 & 0 & 19 & 1 \T \B \\ 
-     \hline
-     7 & 0 & 42 & 1 \T \B \\ 
-     \hline
-     8 & 0 & 67 & 1 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-\begin{table}[H]
-    \caption{Experiment 5 Results}
-    \centering
-    \begin{tabular}{||c c c||}
-        \hline
-        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
-    \hline
-    \hline
-    \textbf{Proposed Algorithm} & 212.5 & 161.75 \T \B\\ \hline
-    \textbf{VMLFQ} & 260 & 225 \T \B\\ \hline
-    \textbf{MLFQ} & 290 & 240 \T \B\\ \hline
-    \textbf{PMLFQ} & 300 & 245 \T \B\\ \hline
-     \end{tabular}
-\end{table}
-
-\subsubsection{Experiment 6}
-
-In this experiment, the proposed algorithm is compared against two variants of the RR algorithm stated in {b3}.
-The first is a static version of the RR algorithm with a constant quantum value of $25$ for scheduling each queue while the second uses a dynamic version of the RR algorithm called SRBRR for doing so.
-
-\begin{table}[H]
-    \caption{Experiment 6 Input}
-    \centering
-     \begin{tabular}{||c c c c||} 
-     \hline
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
-     \hline
-     \hline
-     1 & 0 & 13 & 1 \T \B \\ 
-     \hline
-     2 & 0 & 35 & 1 \T \B \\
-     \hline
-     3 & 0 & 46 & 1 \T \B \\
-     \hline
-     4 & 0 & 63 & 1 \T \B \\
-     \hline
-     5 & 0 & 97 & 1 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-\begin{table}[H]
-    \caption{Experiment 6 Results}
-    \centering
-    \begin{tabular}{||c c c||}
-        \hline
-        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
-    \hline
-    \hline
-    \textbf{Proposed Algorithm} & 113.2 & 62.4 \T \B\\ \hline
-    \textbf{Dynamic SRBRR} & 122.4 & 71.6 \T \B\\ \hline
-    \textbf{Static RR} & 148.2 & 97.4 \T \B\\ \hline
-     \end{tabular}
-\end{table}
-
-\subsubsection{Experiment 7}
-
-This experiment is the same as the previous one, but with a different input test case.
-Note that for this test case, a process queue number is irrelevant to both the RR algorithm and the SRBRR algorithm mentioned in {b3}.
-
-\begin{table}[H]
-    \caption{Experiment 7 Input}
-    \centering
-     \begin{tabular}{||c c c c||} 
-     \hline
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
-     \hline
-     \hline
-     1 & 0 & 54 & 1 \T \B \\ 
-     \hline
-     2 & 0 & 99 & 3 \T \B \\
-     \hline
-     3 & 0 & 5 & 2 \T \B \\
-     \hline
-     4 & 0 & 27 & 2 \T \B \\
-     \hline
-     5 & 0 & 32 & 2 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-\begin{table}[H]
-    \caption{Experiment 7 Results}
-    \centering
-    \begin{tabular}{||c c c||}
-        \hline
-        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
-    \hline
-    \hline
-    \textbf{Dynamic SRBRR} & 93.6 & 50.2 \T \B\\ \hline
-    \textbf{Proposed Algorithm} & 106.8 & 63.4 \T \B\\ \hline
-    \textbf{Static RR} & 152.2 & 108.8 \T \B\\ \hline
-     \end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% OBSERVATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\tiny\par}
 
@@
 
-From the above simulations of different test cases and multiple performance comparisons that involved as many as 11 different scheduling algorithms not including this paper algorithm, it is clear that the average turnaround time and the average waiting time of the proposed algorithm is less than or – in few occasions  – nearly equal to those of the stated algorithms.
-With that said, the proposed algorithm is arguably advantageous over those algorithms, considering even the case in which it underperformed compared to the SRBRR algorithm, it is still favourable due to the capability to separate processes into categories based on their need for the processor and other advantages of the MLFQ algorithm.
-The performance of the proposed algorithm compared to other algorithms is further illustrated in the following graphs:
-
-\begin{figure}[H]
-    \begin{center}
-\begin{tikzpicture}
-    \begin{axis}[
-        width=0.475*\textwidth,
-        symbolic x coords={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
-        ylabel=Avg. Turnaround Time,
-        enlargelimits=0.15,
-        legend style={at={(0.5,-0.25)}, anchor=north,legend columns=1},
-        ybar,
-        xtick={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
-        x tick label style={rotate=45,anchor=east},
-        bar width=3pt,
-        cycle list name=color list
-    ]
-
-    \addplot[plot 0,bar group size={0}{3}, red]
-    coordinates {(Exp. 1,115) (Exp. 2,115) (Exp. 3,151) (Exp. 6,113.2) (Exp. 7,106.8)};
-    \addplot[plot 1,bar group size={1}{3}, green]
-    coordinates {(Exp. 1,150.8)};
-    \addplot[plot 2,bar group size={2}{3}, blue]
-    coordinates {(Exp. 1,161.4)};
-
-    \addplot[plot 1,bar group size={1}{3}, black]
-    coordinates {(Exp. 2,134)};
-    \addplot[plot 2,bar group size={2}{3}, brown]
-    coordinates {(Exp. 2,143.4)};
-
-    \addplot[plot 1,bar group size={1}{3}, teal]
-    coordinates {(Exp. 3,252)};
-    \addplot[plot 2,bar group size={2}{3}, violet]
-    coordinates {(Exp. 3,351)};
-
-    \addplot[plot 0,bar group size={0}{4}, red]
-    coordinates {(Exp. 4,185.85) (Exp. 5,212.5)};
-    \addplot[plot 1,bar group size={1}{4}, lime]
-    coordinates {(Exp. 4,190) (Exp. 5,260)};
-    \addplot[plot 2,bar group size={2}{4}, orange]
-    coordinates {(Exp. 4,232.14) (Exp. 5,290)};
-    \addplot[plot 3,bar group size={3}{4}, olive]
-    coordinates {(Exp. 4,240) (Exp. 5,300)};
-
-    \addplot[plot 1,bar group size={1}{3}, cyan]
-    coordinates {(Exp. 6,122.4) (Exp. 7,93.6)};
-    \addplot[plot 2,bar group size={2}{3}, magenta]
-    coordinates {(Exp. 6,148.2) (Exp. 7,152.2)};
-
-    \legend{Proposed Algorithm,Dynamic RR MLFQ, Static RR MLFQ, Dyn.
-SJFRR MLFQ of {b4},  Stat.
-SJFRR MLFQ of {b4}, Dyn.
-SJFRR MLFQ of {b5}, Stat.
-SJFRR MLFQ of {b5}, VMLFQ, MLFQ, PMLFQ, Dynamic SRBRR, Static RR}
-    \end{axis}
-\end{tikzpicture}
-\end{center}
-\caption{Comparison graph for average turnaround time}
-\vspace{45mm}
-\end{figure}
-
-\begin{figure}[H]
-    \begin{center}
-\begin{tikzpicture}
-    \begin{axis}[
-        width=0.475*\textwidth,
-        symbolic x coords={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
-        ylabel=Avg. Waiting Time,
-        enlargelimits=0.15,
-        legend style={at={(0.5,-0.25)}, anchor=north,legend columns=1},
-        ybar,
-        xtick={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
-        x tick label style={rotate=45,anchor=east},
-        bar width=3pt,
-        cycle list name=color list
-    ]
-
-    \addplot[plot 0,bar group size={0}{3}, red]
-    coordinates {(Exp. 1,68.8) (Exp. 2,68.8) (Exp. 3,88.7) (Exp. 6,62.4) (Exp. 7,63.4)};
-    \addplot[plot 1,bar group size={1}{3}, green]
-    coordinates {(Exp. 1,107.6)};
-    \addplot[plot 2,bar group size={2}{3}, blue]
-    coordinates {(Exp. 1,116.2)};
-
-    \addplot[plot 1,bar group size={1}{3}, black]
-    coordinates {(Exp. 2,91.8)};
-    \addplot[plot 2,bar group size={2}{3}, brown]
-    coordinates {(Exp. 2,98.2)};
-
-    \addplot[plot 1,bar group size={1}{3}, teal]
-    coordinates {(Exp. 3,119)};
-    \addplot[plot 2,bar group size={2}{3}, violet]
-    coordinates {(Exp. 3,228)};
-
-    \addplot[plot 0,bar group size={0}{4}, red]
-    coordinates {(Exp. 4,140.14) (Exp. 5,161.75)};
-    \addplot[plot 1,bar group size={1}{4}, lime]
-    coordinates {(Exp. 4,170) (Exp. 5,225)};
-    \addplot[plot 2,bar group size={2}{4}, orange]
-    coordinates {(Exp. 4,175) (Exp. 5,240)};
-    \addplot[plot 3,bar group size={3}{4}, olive]
-    coordinates {(Exp. 4,180) (Exp. 5,245)};
-
-    \addplot[plot 1,bar group size={1}{3}, cyan]
-    coordinates {(Exp. 6,71.6) (Exp. 7,50.2)};
-    \addplot[plot 2,bar group size={2}{3}, magenta]
-    coordinates {(Exp. 6,97.2) (Exp. 7,108.8)};
-
-    \legend{Proposed Algorithm,Dynamic RR MLFQ, Static RR MLFQ, Dyn.
-SJFRR MLFQ of {b4},  Stat.
-SJFRR MLFQ of {b4}, Dyn.
-SJFRR MLFQ of {b5}, Stat.
-SJFRR MLFQ of {b5}, VMLFQ, MLFQ, PMLFQ, Dynamic SRBRR, Static RR}
-    \end{axis}
-\end{tikzpicture}
-\end{center}
-\caption{Comparison graph for average waiting time}
-\end{figure}
+our algorithm has wire-length score less than TripleZ with 7.3\% and
+greater than NTUidRoute with 3.28\% but it affect the vias number
+greatly that our vias score is less than NTUidRoute's vias score by
+43\%
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CONCLUSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Conclusion and Future Work %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The goal of this paper is to tackle different shortcomings associated with the standard MLFQ scheduling algorithm as well as its variants discussed in several papers.
-To resolve these deficiencies, we introduced different adjustable policies and techniques.
-It is evidently clear that those methods yield better CPU performance and optimize utilization by reducing the average waiting time as well as the average turnaround time.
-Despite experimenting numerous combinations of the parameters and scheduling policies by which the proposed MLFQ algorithm operates, we can say that there is yet a large room for experiment and improvement through finding better methods and policies which would make the algorithm more adaptable to the nature of the submitted processes and overall more enhanced.
-For instance, adjusting the criteria by which the schedular decides whether to promote a process might further lessen starvation.
-Making the proposed algorithm preemptive might also aid mitigating starvation and render overall better performance.
-The possibilities are limitless.
+The goal of this paper is to develop A-star-based global Router with
+minimum wirelength and number of vias as the more vias number the
+more heat generated from the chip with minimum run time.to overcome
+the time problem we use heurestic function that decrease the run time
+of router and test it with different constants to define its affect
+on run time ,for future work we aim to define effective heurestic
+function to improve run time and using more effecient versions of
+A\_star algorithm such as bi-directional A-star ,deep A-star,iterative
+deeping A-star .for instance bi-directional A-star that process edges
+in both directions that improve run time.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{thebibliography}{1}
+\bibitem{b1} Muhammet Mustafa Ozdal and M. D. F. Wong, \char`\"{}Archer:
+a history-driven global routing algorithm,\char`\"{} \textit{2007
+IEEE/ACM International Conference on Computer-Aided Design}, San Jose,
+CA, 2007, pp. 488-495, doi: 10.1109/ICCAD.2007.4397312.
 
-\begin{thebibliography}{00}
-
-\bibitem{b1} Muhammet Mustafa Ozdal and M.
-D.
-F.
-Wong, "Archer: a history-driven global routing algorithm," \textit{2007 IEEE/ACM International Conference on Computer-Aided Design}, San Jose, CA, 2007, pp.
-488-495, doi: 10.1109/ICCAD.2007.4397312.
-
-\bibitem{b2} Liu, Wen-Hao, et al.
-"NCTU-GR 2.0: Multithreaded collision-aware global routing with bounded-length maze routing." \textit{IEEE Transactions on computer-aided design of integrated circuits and systems} 32.5 (2013): 709-722.
-
+\bibitem{b2} Liu, Wen-Hao, et al. \char`\"{}NCTU-GR 2.0: Multithreaded
+collision-aware global routing with bounded-length maze routing.\char`\"{}
+\textit{IEEE Transactions on computer-aided design of integrated circuits
+and systems} 32.5 (2013): 709-722.
 \end{thebibliography}

### 2020-05-31 paper.tex
Error In Build

--- 2020-05-31 paper.tex
@@
 \begin{abstract}
-    In this paper VLSI routing is improved by improving global routing, this can be done by using A-Star with heuristic cost function that has parameters which affect the time taken by the router on changing instead of Dijkstra's algorithm in finding path, which will reduce time taken in this process and achieve the minimum wirelength, many comparisons are taken in this paper with different algorithms to find the optimum algorithm to be used to achieve both minimum wirelength and minimum time taken.
-From the comparisons of the paper we can find that using any algorithm is a trade off as when time taken is decreased, the wirelength is increased and vice versa, so there is no algorithm which is better from the other algorithms in general but using A-Star algorithm with the heuristic function in finding path is a good approach to be used in global routing as it decreases the routing time and achieve the minimum wirelength.
+    In this paper VLSI routing is improved by improving global routing, this can be done by using A-Star with a heuristic cost function that has parameters which affect the time taken by the router on changing instead of Dijkstra's algorithm in finding path, which will reduce the time taken in this process and achieve the minimum wirelength, many comparisons are taken in this paper with different algorithms to find the optimum algorithm to be used to achieve both minimum wirelength and minimum time taken.
+From the comparisons of the paper, we can find that using any algorithm is a trade-off as when the taken time is decreased, the wirelength is increased and vice versa, so there is no algorithm which is better from the other algorithms in general but using A-Star algorithm with the heuristic function in finding the path is a good approach to be used in global routing as it decreases the routing time and achieves the minimum wirelength.
 \end{abstract}
@@
 
-Routing is critical step in physical design process.
-Until now the optimum solution for VLSI routing has not been achieved yet, so it is considered as a very interesting challenging field.
-It is exactly done in two steps, global routing and detailed routing.
-At first global routing is run which is the responsible for making an approximate routing for the whole circuit in order to be used as a guide for detailed routing, then the detailed routing is run to make the exact routing for the system.
-That means if global or detailed routing is improved the whole routing process is improved, but there are many problems that have to be overcame to make a correct routing process.
-First of all the scale has to be taken into consideration, as millions of wires exist in a small chip area which means that many kilometers of wires are placed in a very small area, so wetotal wirelength has to be minimized as much as possible, also it is known that as the wirelength increases the resistance increases as well which means more delay in the chip.
+Routing is a critical step in the physical design process.
+Until now the optimum solution for VLSI routing has not been achieved yet, so it is considered a very interesting challenging field.
+It is exactly done in two steps, global routing, and detailed routing, in global routing, A-technique for 3D global routing is to compress a \textit{3D} grid into a \textit{2D} grid and handle \textit{2D} global routing.
+The obtained solution is then projected back to \textit{3D} by assignment of layers.
+as introduced in most of modern designs as in \cite{b1}, \cite{b2}, \cite{b3}, \cite{b4}, \cite{b5}, \cite{b6}, \cite{b7}, and \cite{b8}.
+At first global routing is run which is responsible for making an approximate routing for the whole circuit in order to be used as a guide for detailed routing, then the detailed routing is run to make the exact routing for the system.
+That means if global or detailed routing is improved the whole routing process is improved, but there are many problems that have to be overcome to make a correct routing process.
+First of all, the scale has to be taken into consideration, as millions of wires exist in a small chip area which means that many kilometers of wires are placed in a very small area, so total wirelength has to be minimized as much as possible, also it is known that as the wirelength increases the resistance increases as well which means more delay in the chip.
 There is another problem as circuits are made in nano-scale which means that its geometric will be complex.
-Another problem is that routing algorithm have to be applicable for more than one layer with different costs.
-The direction of wires also have to taken into consideration as the direction of wires in every layer can be either vertical or horizontal and no diagonal paths, then to go from source 'S' to target 'T' the path taken should be in (vertical | horizontal) directions that specified by the layer (at each layer wires are placed in one direction only), then there is another problem as when a wire goes from layer to another to continue on the perpendicular direction it have to go through via which have a high resistance.
-DFM (design for manufacturer) rules also has to be achieved.
-All of these constraints must be taken into consideration with the global routing to achieve hundred percent of the circuit connections, that means global routing will take a lot of time to achieve all these constraints, and here is the challenge to achieve all the routing specifications with minimum time taken.
+Another problem is that the routing algorithm has to be applicable for more than one layer with different costs.
+The direction of wires also has to be taken into consideration as the direction of wires in every layer can be either vertical or horizontal and no diagonal paths, then to go from source 'S' to target 'T' the path taken should be in (vertical | horizontal) directions that specified by the layer (at each layer wires are placed in one direction only), then there is another problem as when a wire goes from layer to another to continue on the perpendicular direction it has to go through via which has a high resistance.
+DFM (design for manufacturer) rules also have to be achieved.
+All of these constraints must be taken into consideration with the global routing to achieve a hundred percent of the circuit connections, which means global routing will take a lot of time to achieve all these constraints, and here is the challenge to achieve all the routing specifications with the minimum time taken.
 
@@
 
-Several papers proposed various types of approaches to improve the routing process, each of them tried to improve the overall routing by improving one or more parameters, some paperes tried to decrease number of vias, other papers tried to decrease the time taken and so on.
-In \cite{b2} they used two bounded length maze algorithms as finding path algorithms in order to make the router faster, the first one is optimal-BLMR which is used to get the minimum cost paths to be used as a routing paths, this can be done in three steps, first BLC (bounded length constraint) is defined as grater than Manhattan distance then to go from source to target the neighbour points are tested if it can be a part of path or not, each point that violates the BLC constraint is discarded, second
+Several papers proposed various types of approaches to improve the routing process, each of them tried to improve the overall routing by improving one or more parameters, some papers tried to decrease the number of vias, other papers tried to decrease the time taken and so on.
+\par
+In \cite{b1} a sequential global routing is used and two bounded length maze algorithms as finding path algorithms are provided in order to make the router faster and to avoid congestions thus avoiding overflow, the first one is optimal-BLMR and the second one is heuristic-BLMR.
+optimal-BLMR is used to get the minimum cost paths to be used as routing paths, this can be done in three steps.
+First BLC (bounded length constraint) is defined as a greater number than Manhattan distance then to go from source to target the neighbor points are tested if it can be a part of a path or not, each point that violates the BLC constraint is discarded.
+Second, if the route started from point \textit{v}, ended at point \textit{u} and there were many paths between these two points, the normal maze algorithm will take the path with the minimum cost which may cause the route to pass through congestions, but in optimal-BLMR, it keeps track of all paths between these two points in order to choose the path that will not cause overflow, it iterates on the minimum cost path every time and if it found a suitable path it reserves that path, otherwise, it discards that path.
+Third step the optimal-BLMR iterates on the reserved paths and choose the one to be used for routing.
+Heuristic-BLMR is used to speed the router up by reserving only one path between the two points, but it has to keep the advantage of optimal-BLMR (avoiding congestions), this can be achieved by reserving the selected path only if the wirelength is enough to detour around congested regions.
+The advantages of this paper are using sequential global routing which is based on multithreaded global routing which speedup the router between $2.71$ and $3.12$ in overflow free cases, avoiding collision by using optimal-BLMR, and making a fast and nearly avoiding collision algorithm (heuristic-BLMR).
+But there are some disadvantages too, as optimal-BLMR is very slow to be used, although heuristic-BLMR is faster than optimal-BLMR its results are not accurate as the wirelength is not the best compared with other papers, and it is done on \textit{2D} grid then it is projected to the \textit{3D} one however, this approach gives a good result but it is not accurate like routers that apply routing in the \textit{3D} grid directly as in \cite{b9}.
+\par
+In \cite{b4}
 
@@
 
-\bibitem{b1} Muhammet Mustafa Ozdal and M.
-D.
-F.
-Wong, "Archer: a history-driven global routing algorithm," \textit{2007 IEEE/ACM International Conference on Computer-Aided Design}, San Jose, CA, 2007, pp.
-488-495, doi: 10.1109/ICCAD.2007.4397312.
-
-\bibitem{b2} Liu, Wen-Hao, et al.
-"NCTU-GR 2.0: Multithreaded collision-aware global routing with bounded-length maze routing." \textit{IEEE Transactions on computer-aided design of integrated circuits and systems} 32.5 (2013): 709-722.
+    \bibitem{b1} Muhammet Mustafa Ozdal and M. D. F. Wong, \char`\"{}Archer: a history-driven global routi algorithm,\char`\"{} \textit{2007
+    IEEE/ACM International Conference on Computer-Aided Design}, San Jose,
+    CA, 2007, pp. 488-495, doi: 10.1109/ICCAD.2007.4397312.
+
+    \bibitem{b2} Chang, Yen-Jung, Yu-Ting Lee, and Ting-Chi Wang.
+"NTHU-Route 2.0: a fast and stable global router." \textit{2008 IEEE/ACM International Conference on Computer-Aided Design.
+IEEE}, 2008.
+
+    \bibitem{b3} H.-Y.
+Chen, C.-H.
+Hsu, and Y.-W.
+Chang, “High-performance global routing with fast overflow reduction,” \textit{in 2009 Asia and South Pacific Design Automation Conference}, pp.
+582–587, IEEE, 2009.
+
+    \bibitem{b4} Xu, Yue, Yanheng Zhang, and Chris Chu. "FastRoute 4.0: global router with efficient via minimization." \textit{2009 Asia and South Pacific Design Automation Conference. IEEE}, 2009.
+
+    \bibitem{b5} Cho, Minsik, et al.
+"BoxRouter 2.0: Architecture and implementation of a hybrid and robust global router." \textit{2007 IEEE/ACM International Conference on Computer-Aided Design.
+IEEE}, 2007.
+
+    \bibitem{b6} Ozdal, Muhammet Mustafa, and Martin DF Wong. "Archer: a history-driven global routing algorithm." \textit{2007 IEEE/ACM International Conference on Computer-Aided Design. IEEE}, 2007.
+
+    \bibitem{b7} Gao, Jhih-Rong, Pei-Ci Wu, and Ting-Chi Wang. "A new global router for modern designs." \textit{2008 Asia and South Pacific Design Automation Conference.} IEEE, 2008.
+
+    \bibitem{b8} Moffitt, Michael D.
+"MaizeRouter: Engineering an effective global router." \textit{IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems} 27.11 (2008): 2017-2026.
+
+    \bibitem{b9} Roy, Jarrod A., and Igor L.
+Markov.
+"High-performance routing at the nanometer scale." \textit{IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems} 27.6 (2008): 1066-1077.
 

### 2020-06-01 paper.tex
Second Related Work Paper

@@
 \par
-In \cite{b4}
+In \cite{b4}, both of via count and runtime are reduced, this done by integrating \cite{b10}, \cite{b11}, and \cite{b12} with via aware Steiner tree generation, 3-bend routing, and layer assignment with careful edge and net ordering to create \cite{b4}.
+Via aware Steiner tree is used to at the beginning of the global routing, it generates a suitable topology, by changing tree topology the via count greatly changed, which means that using a suitable topology for Steiner tree will greatly reduce the via count.
+The 3-bend routing is used instead of L, U, Z, maze, and monotonic routing, as L, U, Z routing can not avoid congestions but they generate a little number of vias, maze and monotonic can avoid congestions but they generate a lot of vias and their runtime is very high, so the 3-bend routing was used as it is fast, its completely \textit{O(nm)}, and it generates vias less than maze and monotonic routing as it consists of two L routing.
+Layer assignment with careful ordering algorithm is used as a solution of \textit{3D}, it is like all the modern techniques projects the \textit{3D} grid into \textit{2D} one to be easier and faster in routing, this algorithm guarantees the wirelength and overflow unchanged on assigning to layers, dynamic programming is used in layer assignment to make it faster.
+From the previous explanation the advantages of this paper are decreasing number of vias, which means less power consumption and circuit delay, and decreasing runtime of global routing thus decreasing runtime of whole the routing process.
+But it has disadvantages too, one of them is the wirelength is not optimal, as using 3-bend routing increases the wirelength to avoid congestions, another one is caused by layer assignment, as if the \textit{2D} was not congestion-free the results will not be accurate.
 
@@
 
+    \bibitem{b10} Zhang, Yanheng, Yue Xu, and Chris Chu.
+"FastRoute3.
+0: a fast and high quality global router based on virtual capacity." \textit{2008 IEEE/ACM International Conference on Computer-Aided Design.} IEEE, 2008.
+
+    \bibitem{b11} Pan, Min, and Chris Chu.
+"FastRoute: A step to integrate global routing into placement." \textit{Proceedings of the 2006 IEEE/ACM international conference on Computer-aided design.} 2006.
+
+    \bibitem{b12} Pan, Min, and Chris Chu. "FastRoute 2.0: A high-quality and efficient global router." \textit{2007 Asia and south pacific design automation conference.} IEEE, 2007.
+
 \end{thebibliography}

### 2020-06-01 paper.tex
Proposed Approach

@@
 \begin{abstract}
-    In this paper VLSI routing is improved by improving global routing, this can be done by using A-Star with a heuristic cost function that has parameters which affect the time taken by the router on changing instead of Dijkstra's algorithm in finding path, which will reduce the time taken in this process and achieve the minimum wirelength, many comparisons are taken in this paper with different algorithms to find the optimum algorithm to be used to achieve both minimum wirelength and minimum time taken.
-From the comparisons of the paper, we can find that using any algorithm is a trade-off as when the taken time is decreased, the wirelength is increased and vice versa, so there is no algorithm which is better from the other algorithms in general but using A-Star algorithm with the heuristic function in finding the path is a good approach to be used in global routing as it decreases the routing time and achieves the minimum wirelength.
+    In this paper VLSI routing is improved by improving global routing, this can be done by using A-Star with a heuristic cost function that has parameters which affect the time taken by the router on changing instead of Dijkstra's algorithm in finding path, which will reduce the time taken in this process and achieve the minimum wire length, many comparisons are taken in this paper with different algorithms to find the optimum algorithm to be used to achieve both minimum wire length and minimum time taken.
+From the comparisons of the paper, we can find that using any algorithm is a trade-off as when the taken time is decreased, the wire length is increased and vice versa, so there is no algorithm which is better from the other algorithms in general but using A-Star algorithm with the heuristic function in finding the path is a good approach to be used in global routing as it decreases the routing time and achieves the minimum wire length.
 \end{abstract}
@@
 That means if global or detailed routing is improved the whole routing process is improved, but there are many problems that have to be overcome to make a correct routing process.
-First of all, the scale has to be taken into consideration, as millions of wires exist in a small chip area which means that many kilometers of wires are placed in a very small area, so total wirelength has to be minimized as much as possible, also it is known that as the wirelength increases the resistance increases as well which means more delay in the chip.
+First of all, the scale has to be taken into consideration, as millions of wires exist in a small chip area which means that many kilometers of wires are placed in a very small area, so total wire length has to be minimized as much as possible, also it is known that as the wire length increases the resistance increases as well which means more delay in the chip.
 There is another problem as circuits are made in nano-scale which means that its geometric will be complex.
@@
 Figure~\ref{fig:GlobalRoutingProcess} shows a very simple approach of how the global router works.
-At (a) the source and target of both (A,B) need to be connected ignoring obstacles, nevertheless we can observe that the global router have to iterate to get the best routing paths, at (b) (B,B) connected but there is no way to connect (A,A) as when (B,B) connected together they blocked the way for (A,A) to be connected, after some iterations we can find the figure at (c) in which (A,A) and (B,B) connected correctly, but there is a problem, the (A,A) connection is not the optimal path as there are paths which achieve less wirelength, so the global router have to iterate until reaching the optimal path.
+At (a) the source and target of both (A,B) need to be connected ignoring obstacles, nevertheless we can observe that the global router have to iterate to get the best routing paths, at (b) (B,B) connected but there is no way to connect (A,A) as when (B,B) connected together they blocked the way for (A,A) to be connected, after some iterations we can find the figure at (c) in which (A,A) and (B,B) connected correctly, but there is a problem, the (A,A) connection is not the optimal path as there are paths which achieve less wire length, so the global router have to iterate until reaching the optimal path.
 These iterations are done for only two connections in one layer without obstacles, then how about millions of wires in VLSI?
@@
 Third step the optimal-BLMR iterates on the reserved paths and choose the one to be used for routing.
-Heuristic-BLMR is used to speed the router up by reserving only one path between the two points, but it has to keep the advantage of optimal-BLMR (avoiding congestions), this can be achieved by reserving the selected path only if the wirelength is enough to detour around congested regions.
+Heuristic-BLMR is used to speed the router up by reserving only one path between the two points, but it has to keep the advantage of optimal-BLMR (avoiding congestions), this can be achieved by reserving the selected path only if the wire length is enough to detour around congested regions.
 The advantages of this paper are using sequential global routing which is based on multithreaded global routing which speedup the router between $2.71$ and $3.12$ in overflow free cases, avoiding collision by using optimal-BLMR, and making a fast and nearly avoiding collision algorithm (heuristic-BLMR).
-But there are some disadvantages too, as optimal-BLMR is very slow to be used, although heuristic-BLMR is faster than optimal-BLMR its results are not accurate as the wirelength is not the best compared with other papers, and it is done on \textit{2D} grid then it is projected to the \textit{3D} one however, this approach gives a good result but it is not accurate like routers that apply routing in the \textit{3D} grid directly as in \cite{b9}.
+But there are some disadvantages too, as optimal-BLMR is very slow to be used, although heuristic-BLMR is faster than optimal-BLMR its results are not accurate as the wire length is not the best compared with other papers, and it is done on \textit{2D} grid then it is projected to the \textit{3D} one however, this approach gives a good result but it is not accurate like routers that apply routing in the \textit{3D} grid directly as in \cite{b9}.
 \par
@@
 The 3-bend routing is used instead of L, U, Z, maze, and monotonic routing, as L, U, Z routing can not avoid congestions but they generate a little number of vias, maze and monotonic can avoid congestions but they generate a lot of vias and their runtime is very high, so the 3-bend routing was used as it is fast, its completely \textit{O(nm)}, and it generates vias less than maze and monotonic routing as it consists of two L routing.
-Layer assignment with careful ordering algorithm is used as a solution of \textit{3D}, it is like all the modern techniques projects the \textit{3D} grid into \textit{2D} one to be easier and faster in routing, this algorithm guarantees the wirelength and overflow unchanged on assigning to layers, dynamic programming is used in layer assignment to make it faster.
-From the previous explanation the advantages of this paper are decreasing number of vias, which means less power consumption and circuit delay, and decreasing runtime of global routing thus decreasing runtime of whole the routing process.
-But it has disadvantages too, one of them is the wirelength is not optimal, as using 3-bend routing increases the wirelength to avoid congestions, another one is caused by layer assignment, as if the \textit{2D} was not congestion-free the results will not be accurate.
+Layer assignment with careful ordering algorithm is used as a solution of \textit{3D}, it is like all the modern techniques project the \textit{3D} grid into \textit{2D} one to be easier and faster in routing, this algorithm guarantees the wire length and overflow unchanged on assigning to layers, dynamic programming is used in layer assignment to make it faster.
+From the previous explanation, the advantages of this paper are decreasing the number of vias, which means less power consumption and circuit delay, and decreasing runtime of global routing thus decreasing runtime of whole the routing process.
+But it has disadvantages too, one of them is the wire length is not optimal, as using 3-bend routing increases the wire length to avoid congestions, another one is caused by layer assignment as if the \textit{2D} was not congestion-free the results will not be accurate.
 
@@
 \section{Proposed Approach}
-
-For a multilevel feedback queue scheduling algorithm, three parameters are considered.
-The first is the chosen scheduling algorithm for each queue, especially the last queue as its scheduling algorithm is expected to treat starvation.
-The second is the criteria according to which a process is promoted, this technique is also known as Aging.
-The third is the criteria according to which a process is demoted.
-In our proposed algorithm, there are 5 queues sorted in ascending order in line with their priority number, 1 being the highest priority and 5 being the lowest.
-Each queue uses a modified version of the round-robin scheduling algorithm stated in {b3}.
-In {b3}, processes are sorted in ascending order according to their burst time and are assigned a time quantum that equals the median burst time of those processes.
-This algorithm provides better turnaround time and waiting time than the standard static quantum RR algorithm whose quantum, if set too short, leads to many context switches and, if set too long, morphs the algorithm into an FCFS algorithm.
-The proposed alteration on the stated algorithm in {b3} is that each queue quantum time equals the median burst time multiplied by a factor matching the queue number.
-Hence, the gradual increase of quantum time as priority decreases.
-For clarification, a queue with priority equal $2$ has the following processes denoted by their burst time: $100$, $300$, $550$, $600$, $620$, $700$, $720$, $900$ and $1200$, the median value is $620$, since we are in a queue whose priority equals $2$, therefore the quantum slice value according to the proposed approach equals $1240$ as in $620 * 2$.
-If processes of a certain queue didn't terminate after assigning the quantum time value, they are shifted to the next lower priority queue.
-After introducing new processes into a queue, the quantum time slice is recalculated.
-Processes age whenever they are in a queue whose priority is one less than that currently getting scheduled and satisfies the following inequality:
-\begin{equation}
-\frac{waiting \; time \; of \; P}{burst \; time \; of \; P} >= 1\label{eq1}
-\end{equation}
-
-Those procedures are repeated for all the generated queues until all processes reach the lowest priority queue where they are rescheduled until their completion.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FLOWCHART %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Pseudocode Flowchart of the Proposed Approach}
-\begin{tikzpicture}[node distance=2.2cm]
-
-    \node (start) [startstop] {Start};
-    \node (in1) [io, below of=start, text width = 2cm] {Read Processes Data};
-    \node (dec1) [decision, below of=in1, text width = 2cm, yshift=-1cm] {All processes are finished};
-    \node (pro1) [process, below of=dec1, text width= 3cm, yshift = -1cm] {Iterate on queues $Q$};
-    \node (pro2) [process, below of=pro1, text width = 3cm] {Assign eligable processes to the current queue};
-    \node (out1) [io, left of=dec1, text width = 2cm, xshift= -2cm] {Print avg. waiting time, avg. turnaround time, throughput};
-    \node (end) [startstop, below of=out1, yshift=-1cm] {End};
-    \node (dec2) [decision, below of=pro2, text width = 2cm, yshift=-2cm] {A process $P$ in the subsequent queue is boostable};
-
-    \node (pro3) [process, left of=dec2, text width= 3cm, xshift= -2.5cm] {Promote $P$ to current queue};
-    \node (pro4) [process, below of=dec2, text width= 3cm, yshift=-2.2cm] {Calculate the quantum time value $\phi$};
-    \node (pro5) [process, below of=pro4, text width= 3cm] {Schedule processes in current queue};
-
-    \draw [arrow] (start) -- (in1);
-    \draw [arrow] (in1) -- (dec1);
-    % \draw [arrow] (pro1) -- (dec1);
-    \draw [arrow] (dec1) -- node[anchor=west, above] {Yes} (out1);
-    \draw [arrow] (out1) -- (end);
-    \draw [arrow] (dec1) -- node[anchor=south, left] {No} (pro1);
-    \draw [arrow] (pro1) -- (pro2);
-    \draw [arrow] (pro2) -- (dec2);
-    \draw [arrow] (dec2) -- node[anchor=west,above] {Yes} (pro3);
-    \draw [arrow] (pro3.north) -- ++ (0,3.7) -- ++ (3.1,0);
-    \draw [arrow] (dec2) -- node[anchor=south, left] {No} (pro4);
-    \draw [arrow] (pro4) -- (pro5);
-    \draw [arrow] (pro5.east) -- ++ (1.2,0) -- ++(0,16.2) -- ++(-1.3,0);
+For global routing, three parameters are considered.
+The first is the total wire length, the second is the total overflow.
+The third is the running time.
+In our proposed solution, we are focused on the time parameter without affecting much the total wire length and total overflow.
+So according to minimize the time we have decided to apply A* algorithm as the pathfinder algorithm with a proposed heuristic function, A* is basically a guided variation of Dijkstra.
+This algorithm can be turned into a better or worse pathfinding algorithm by experimenting with the heuristics it uses and how it evaluates each node a* expands on a node only if it seems promising.
+Its only focus is to reach the goal node as quickly as possible from the current node, not to try and reach every other node.
+Illustrative example:
+\begin{figure} [hbt!]
+    \centering  
+    \subfigure[Maze] {
+    \begin{tikzpicture}
+        [
+            box/.style={rectangle,draw=black,thick, minimum size=0.5cm},
+        ]
+
+    \foreach \x in {0,0.5,...,3.5}{
+        \foreach \y in {0,0.5,...,2}
+            \node[box] at (\x,\y){};
+    }
+    \node [box,fill=green] at (0.5,1){S};
+    \node[box,fill=green  ] at (3,1){D};  
+    \node[box,fill=black  ] at (2,1){ };  
     \end{tikzpicture}
+}
+
+\subfigure[Applying Dijkstra] {
+    \begin{tikzpicture}
+        [
+            box/.style={rectangle,draw=black,thick, minimum size=0.5cm},
+        ]
+
+    \foreach \x in {0,0.5,...,3.5}{
+        \foreach \y in {0,0.5,...,2}
+            \node[box] at (\x,\y){};
+    }
+
+    \node [box,fill=blue] at (0,0){};
+    \node [box,fill=blue] at (0.5,0){};
+    \node [box,fill=blue] at (1,0){};
+    \node [box,fill=blue] at (1.5,0){};
+    \node [box,fill=blue] at (2,0){};
+    \node [box,fill=blue] at (2.5,0){};
+    \node [box,fill=blue] at (3,0){};
+    \node [box,fill=blue] at (0,0.5){};
+    \node [box,fill=blue] at (0.5,0.5){};
+    \node [box,fill=blue] at (1,0.5){};
+    \node [box,fill=blue] at (1.5,0.5){};
+    \node [box,fill=blue] at (2,0.5){};
+    \node [box,fill=blue] at (2.5,0.5){};
+    \node [box,fill=blue] at (3,0.5){};
+    \node [box,fill=blue] at (3.5,.5){};
+    \node [box,fill=blue] at (2.5,1){};
+    \node [box,fill=blue] at (0,1){};
+    \node [box,fill=blue] at (2.5,0.5){};
+    \node [box,fill=blue] at (0,2){};
+    \node [box,fill=blue] at (0.5,2){};
+    \node [box,fill=blue] at (1,2){};
+    \node [box,fill=blue] at (1.5,2){};
+    \node [box,fill=blue] at (2,2){};
+    \node [box,fill=blue] at (2.5,2){};
+    \node [box,fill=blue] at (3,2){};
+    \node [box,fill=blue] at (3.5,2){};
+    \node [box,fill=blue] at (3.5,1.5){};
+    \node [box,fill=blue] at (0,1.5){};
+    \node [box,fill=blue] at (0.5,1.5){};
+    \node [box,fill=blue] at (1,1.5){};
+    \node [box,fill=yellow] at (0.5,1){S};
+    \node [box,fill=yellow] at (1,1){};
+    \node [box,fill=yellow] at (1.5,1){};
+    \node [box,fill=yellow] at (1.5,1.5){};
+    \node [box,fill=yellow] at (2,1.5){};
+    \node [box,fill=yellow] at (2.5,1.5){};
+    \node [box,fill=yellow] at (3,1.5){};
+    \node[box,fill=yellow  ] at (3,1){D};  
+    \node[box,fill=black  ] at (2,1){ };  
+    \end{tikzpicture}
+}
+\subfigure[Applying A*] {
+    \begin{tikzpicture}
+        [
+            box/.style={rectangle,draw=black,thick, minimum size=0.5cm},
+        ]
+
+    \foreach \x in {0,0.5,...,3.5}{
+        \foreach \y in {0,0.5,...,2}
+            \node[box] at (\x,\y){};
+    }
+    \node [box,fill=yellow] at (0.5,1){S};
+    \node[box,fill=yellow  ] at (3,1){D};
+    \node [box,fill=yellow] at (0.5,1.5){};  
+    \node [box,fill=yellow] at (1,1.5){};  
+    \node [box,fill=yellow] at (1.5,1.5){};
+    \node [box,fill=yellow] at (2,1.5){};
+    \node [box,fill=yellow] at (2.5,1.5){};
+    \node [box,fill=yellow] at (3,1.5){};
+    \node [box,fill=blue] at (0,1){};
+    \node [box,fill=blue] at (1,1){};
+    \node [box,fill=blue] at (1.5,1){};
+    \node[box,fill=black  ] at (2,1){ };  
+    \end{tikzpicture}
+}
+\caption{Comparison between Dijkstra \& A* }
+\label{fig:GlobalRoutingProcess}
+\end{figure}
+
+In the illustrative example the visited nodes are marked in blue color and the path is in yellow color.
+Both have path of six cells which in our case they have optimal wire length but totally different running time as Dijkstra visits much more nodes than A*
+, in the case of many target nodes, Dijkstra might be better in total wire length but much slower than A*, with an appropriate heuristic function we can minimize the time and try to reach optimal wire length.
+The heuristic function is a way of informing the search about the path to a target that provides an intelligent way of guessing which neighbor of the node is going to lead to the target faster.
+Hence, our heuristic function composed of Manhattan distance, layer index, and some constants.
+
+\begin{multline*}
+    h = \ln ((\mid p1 \cdot x-p2 \cdot x\mid+\mid p1 \cdot y-p2 \cdot y\mid)*const1) \\ 
+     +(\mid p1 \cdot layerid-p2 \cdot layerid\mid)*const2 \\
+\end{multline*}
+The global router is implemented using C++ with the boost library, and a parser for LEF/DEF formats.
+We conducted our experiment with the same configuration and tried to test the global router behavior using A* algorithm instead of Dijkstra's.
 
@@
 \begin{algorithm}[H]
-    \caption{Developed Multilevel Feedback Queue Scheduling Algorithm}
-    \hspace*{\algorithmicindent} \textbf{Input:} Number of processes $n$, processes priority $\alpha$\\
-    \hspace*{\algorithmicindent} burst time values $\beta$, arrival time values $\sigma$, \\
-    \hspace*{\algorithmicindent} context switching cost $\epsilon$\\
-    \hspace*{\algorithmicindent} \textbf{Output:} Average turnaround time, average waiting time,\\
-    \hspace*{\algorithmicindent} throughput
+    \caption{A* Algorithm}
+    \hspace*{\algorithmicindent} \textbf{Input:} Grid values $g$, Source $s$, Destination $d$\\
+    \hspace*{\algorithmicindent} \textbf{Output:} Path\\
     \begin{algorithmic}[1]
-    \Procedure {DMLFQ}{}
+    \Procedure {A*}{}
     % Return  Average waiting time, throughput
     \Statex Declaration and Initialisation:
-    \State Queue $Q_{i}$ where $i \in \{1, 2, 3, 4, 5\}$
-    \State Turnaround time values $\tau$
-    \State Finish time values $\lambda$
-    \State Waiting time values $\theta$
-    \State Remaining time values $\mu = \beta$
-    \State Quantum time value $\phi$
-    \State Number of context switches $\delta$
-        \State$time = 0$
-        \While{$\exists P \in Q$}
-            \For{$i = 1$ to $5$}
-                \For{$j = 1$ to $n$}
-                    \If{$\sigma_{j} <= time$ and $\alpha_{j}$ equals $i$}
-                        \State \textit{\textbf{Assign}} $P_{j}$ to $Q_{i}$
+    \State Cells $\theta$ % The Cells in the grid.
+    \State Visited Nodes $\phi$ % Nodes already visited.
+    \State Openlist Nodes $\delta$ % Nodes still to be visited. pq
+    \State The cost from starting point to a given node $g$
+    \State The heuristic function $h$
+    \State (The cost of $g$ + The cost of $h$) is $f$
+    \If{$s$ or $d$ is invalid}
+        \Return
     \EndIf
-                    \State $waitingTime = time - \sigma_{j}$
-                    \If{$i < 5$ and $waitingTime/\mu_{j} >= 1$ and $\alpha_{j}$ equals $i + 1$ and  $\sigma_{j} <= time$}
-                        \State \textit{\textbf{Assign}} $P_{j}$ to $Q_{i}$
+    \If{$s$ or $d$ is blocked}
+        \Return
+    \EndIf
+    \If{$s$ = $d$}
+        \Return
+    \EndIf
+    \State Initialize $\delta$ 
+    \State Initialize $\phi$
+        \While{$\delta$ is not empty}
+            \State $currNode$  = node with least $f$ in $\delta$
+            \State $\delta$.Remove($currNode$)
+            \State Generate 4 neighbours of $currNode$
+            \For{$neighbour \in neighbours$}
+            \If{$neighbour$ = $d$}
+                \State Get path
+                \Return
+            \ElsIf{$neighbour \notin \phi$ and $neighbour$ is not blocked}
+                \State $gnew$ = $currNode$.$g$ + distance between neighbour and currNode
+                \State $hnew$ = distance from $d$ to $neighbour$
+                \State $fnew$ = $gnew$ + $hnew$
+                \If{$fnew < neighbour$.$f$}
+                \State $neighbour$.$g$ = $currNode$.$g$ + distance between neighbour and currNode
+                \State $neighbour$.$h$ = distance from $d$ to $neighbour$
+                \State $neighbour$.$f$ = $neighbour$.$g$ + $neighbour$.$h$
+                \State $\delta$.Add($neighbour$)
+                \EndIf
             \EndIf
             \EndFor
-                \State Sort $Q_{i}$ in ascending order according to remaining time values
-                \State $\phi = median\; value\; of\; Q_{i} * i$
-                \algrenewcommand\algorithmicfor{\textbf{foreach}}
-                \For{$P_{j} \in Q_{i}$}
-                    \If{$\mu_{j} <= \phi$}
-                        \State $time = time + \mu_{j}$
-                        \State $\lambda_{j} = time$
-                        \State \textit{\textbf{Remove}} $P_{j}$ from $Q_{i}$
-                    \Else
-                        \State $time = time + \phi$
-                        \State $\mu_{j} = \mu_{j} - \phi$
-                        \If{$i < 5$}
-                            \State $\alpha_{j} = \alpha_{j} + 1$
-                        \EndIf
-                    \EndIf
-                    \If{Previous process $\neq P_{j}$}
-                        \State $time = time + \epsilon$
-                        \State $\delta = \delta + 1$
-                    \EndIf
-                \EndFor
-                \algrenewcommand\algorithmicfor{\textbf{for}}
-            \EndFor
+        \State $\phi$.Add($currNode$)
         \EndWhile
-        \For{$i = 1$ to $n$}
-            $\tau_{j} = \lambda_{j} - \sigma_{j}$, $\theta_{j} = \tau_{j} - \beta_{j}$
-        \EndFor
-        \State \textbf{return} average of $\theta$, average of $\tau$, $n/time$
         \EndProcedure
@@
 
+    \bibitem{b13} Liu, Jinwei, et al. "CUGR: Detailed-Routability-Driven 3D Global Routing with Probabilistic Resource Model."
+
 \end{thebibliography}

### 2020-06-01 paper.tex
Indentation

@@
     bar group skip/.initial=2pt,
-    plot 0/.style={blue,fill=blue!30!white,mark=none},%
+    plot 0/.style={cyan,fill=cyan!30!white,mark=none},%
     plot 1/.style={red,fill=red!30!white,mark=none},%
@@
 \end{figure}
-
+\medskip
 Figure~\ref{fig:GlobalRoutingProcess} shows a very simple approach of how the global router works.
@@
 Several papers proposed various types of approaches to improve the routing process, each of them tried to improve the overall routing by improving one or more parameters, some papers tried to decrease the number of vias, other papers tried to decrease the time taken and so on.
+\medskip
 \par
@@
 But there are some disadvantages too, as optimal-BLMR is very slow to be used, although heuristic-BLMR is faster than optimal-BLMR its results are not accurate as the wire length is not the best compared with other papers, and it is done on \textit{2D} grid then it is projected to the \textit{3D} one however, this approach gives a good result but it is not accurate like routers that apply routing in the \textit{3D} grid directly as in \cite{b9}.
+\medskip
 \par
@@
 In our proposed solution, we are focused on the time parameter without affecting much the total wire length and total overflow.
-So according to minimize the time we have decided to apply A* algorithm as the pathfinder algorithm with a proposed heuristic function, A* is basically a guided variation of Dijkstra.
-This algorithm can be turned into a better or worse pathfinding algorithm by experimenting with the heuristics it uses and how it evaluates each node a* expands on a node only if it seems promising.
+So according to minimize the time we have decided to apply A-Star algorithm as the pathfinder algorithm with a proposed heuristic function, A-Star is basically a guided variation of Dijkstra.
+This algorithm can be turned into a better or worse pathfinding algorithm by experimenting with the heuristics it uses and how it evaluates each node A-Star expands on a node only if it seems promising.
 Its only focus is to reach the goal node as quickly as possible from the current node, not to try and reach every other node.
@@
     }
-    \node [box,fill=green] at (0.5,1){S};
-    \node[box,fill=green  ] at (3,1){D};  
+    \node [box,fill=orange] at (0.5,1){S};
+    \node[box,fill=orange  ] at (3,1){D};  
     \node[box,fill=black  ] at (2,1){ };  
@@
 
-    \node [box,fill=blue] at (0,0){};
-    \node [box,fill=blue] at (0.5,0){};
-    \node [box,fill=blue] at (1,0){};
-    \node [box,fill=blue] at (1.5,0){};
-    \node [box,fill=blue] at (2,0){};
-    \node [box,fill=blue] at (2.5,0){};
-    \node [box,fill=blue] at (3,0){};
-    \node [box,fill=blue] at (0,0.5){};
-    \node [box,fill=blue] at (0.5,0.5){};
-    \node [box,fill=blue] at (1,0.5){};
-    \node [box,fill=blue] at (1.5,0.5){};
-    \node [box,fill=blue] at (2,0.5){};
-    \node [box,fill=blue] at (2.5,0.5){};
-    \node [box,fill=blue] at (3,0.5){};
-    \node [box,fill=blue] at (3.5,.5){};
-    \node [box,fill=blue] at (2.5,1){};
-    \node [box,fill=blue] at (0,1){};
-    \node [box,fill=blue] at (2.5,0.5){};
-    \node [box,fill=blue] at (0,2){};
-    \node [box,fill=blue] at (0.5,2){};
-    \node [box,fill=blue] at (1,2){};
-    \node [box,fill=blue] at (1.5,2){};
-    \node [box,fill=blue] at (2,2){};
-    \node [box,fill=blue] at (2.5,2){};
-    \node [box,fill=blue] at (3,2){};
-    \node [box,fill=blue] at (3.5,2){};
-    \node [box,fill=blue] at (3.5,1.5){};
-    \node [box,fill=blue] at (0,1.5){};
-    \node [box,fill=blue] at (0.5,1.5){};
-    \node [box,fill=blue] at (1,1.5){};
-    \node [box,fill=yellow] at (0.5,1){S};
-    \node [box,fill=yellow] at (1,1){};
-    \node [box,fill=yellow] at (1.5,1){};
-    \node [box,fill=yellow] at (1.5,1.5){};
-    \node [box,fill=yellow] at (2,1.5){};
-    \node [box,fill=yellow] at (2.5,1.5){};
-    \node [box,fill=yellow] at (3,1.5){};
-    \node[box,fill=yellow  ] at (3,1){D};  
+    \node [box,fill=cyan] at (0,0){};
+    \node [box,fill=cyan] at (0.5,0){};
+    \node [box,fill=cyan] at (1,0){};
+    \node [box,fill=cyan] at (1.5,0){};
+    \node [box,fill=cyan] at (2,0){};
+    \node [box,fill=cyan] at (2.5,0){};
+    \node [box,fill=cyan] at (3,0){};
+    \node [box,fill=cyan] at (0,0.5){};
+    \node [box,fill=cyan] at (0.5,0.5){};
+    \node [box,fill=cyan] at (1,0.5){};
+    \node [box,fill=cyan] at (1.5,0.5){};
+    \node [box,fill=cyan] at (2,0.5){};
+    \node [box,fill=cyan] at (2.5,0.5){};
+    \node [box,fill=cyan] at (3,0.5){};
+    \node [box,fill=cyan] at (3.5,.5){};
+    \node [box,fill=cyan] at (2.5,1){};
+    \node [box,fill=cyan] at (0,1){};
+    \node [box,fill=cyan] at (2.5,0.5){};
+    \node [box,fill=cyan] at (0,2){};
+    \node [box,fill=cyan] at (0.5,2){};
+    \node [box,fill=cyan] at (1,2){};
+    \node [box,fill=cyan] at (1.5,2){};
+    \node [box,fill=cyan] at (2,2){};
+    \node [box,fill=cyan] at (2.5,2){};
+    \node [box,fill=cyan] at (3,2){};
+    \node [box,fill=cyan] at (3.5,2){};
+    \node [box,fill=cyan] at (3.5,1.5){};
+    \node [box,fill=cyan] at (0,1.5){};
+    \node [box,fill=cyan] at (0.5,1.5){};
+    \node [box,fill=cyan] at (1,1.5){};
+    \node [box,fill=orange] at (0.5,1){S};
+    \node [box,fill=orange] at (1,1){};
+    \node [box,fill=orange] at (1.5,1){};
+    \node [box,fill=orange] at (1.5,1.5){};
+    \node [box,fill=orange] at (2,1.5){};
+    \node [box,fill=orange] at (2.5,1.5){};
+    \node [box,fill=orange] at (3,1.5){};
+    \node[box,fill=orange  ] at (3,1){D};  
     \node[box,fill=black  ] at (2,1){ };  
@@
 }
-\subfigure[Applying A*] {
+\subfigure[Applying A-Star] {
     \begin{tikzpicture}
@@
     }
-    \node [box,fill=yellow] at (0.5,1){S};
-    \node[box,fill=yellow  ] at (3,1){D};
-    \node [box,fill=yellow] at (0.5,1.5){};  
-    \node [box,fill=yellow] at (1,1.5){};  
-    \node [box,fill=yellow] at (1.5,1.5){};
-    \node [box,fill=yellow] at (2,1.5){};
-    \node [box,fill=yellow] at (2.5,1.5){};
-    \node [box,fill=yellow] at (3,1.5){};
-    \node [box,fill=blue] at (0,1){};
-    \node [box,fill=blue] at (1,1){};
-    \node [box,fill=blue] at (1.5,1){};
+    \node [box,fill=orange] at (0.5,1){S};
+    \node[box,fill=orange  ] at (3,1){D};
+    \node [box,fill=orange] at (0.5,1.5){};  
+    \node [box,fill=orange] at (1,1.5){};  
+    \node [box,fill=orange] at (1.5,1.5){};
+    \node [box,fill=orange] at (2,1.5){};
+    \node [box,fill=orange] at (2.5,1.5){};
+    \node [box,fill=orange] at (3,1.5){};
+    \node [box,fill=cyan] at (0,1){};
+    \node [box,fill=cyan] at (1,1){};
+    \node [box,fill=cyan] at (1.5,1){};
     \node[box,fill=black  ] at (2,1){ };  
@@
 }
-\caption{Comparison between Dijkstra \& A* }
+\caption{Comparison between Dijkstra \& A-Star }
 \label{fig:GlobalRoutingProcess}
 \end{figure}
-
-In the illustrative example the visited nodes are marked in blue color and the path is in yellow color.
-Both have path of six cells which in our case they have optimal wire length but totally different running time as Dijkstra visits much more nodes than A*
-, in the case of many target nodes, Dijkstra might be better in total wire length but much slower than A*, with an appropriate heuristic function we can minimize the time and try to reach optimal wire length.
+\medskip
+In the illustrative example the visited nodes are marked in cyan color, the path is in orange color, and the blocked cells are black.
+Both have path of six cells which in our case they have optimal wire length but totally different running time as Dijkstra visits much more nodes than A-Star
+, in the case of many target nodes, Dijkstra might be better in total wire length but much slower than A-Star, with an appropriate heuristic function we can minimize the time and try to reach optimal wire length.
 The heuristic function is a way of informing the search about the path to a target that provides an intelligent way of guessing which neighbor of the node is going to lead to the target faster.
@@
 The global router is implemented using C++ with the boost library, and a parser for LEF/DEF formats.
-We conducted our experiment with the same configuration and tried to test the global router behavior using A* algorithm instead of Dijkstra's.
+We conducted our experiment with the same configuration and tried to test the global router behavior using A-Star algorithm instead of Dijkstra's.
 
@@
 \begin{algorithm}[H]
-    \caption{A* Algorithm}
+    \caption{A-Star Algorithm}
     \hspace*{\algorithmicindent} \textbf{Input:} Grid values $g$, Source $s$, Destination $d$\\
@@
     \begin{algorithmic}[1]
-    \Procedure {A*}{}
+    \Procedure {A-Star}{}
     % Return  Average waiting time, throughput
@@
     coordinates {(Exp. 1,150.8)};
-    \addplot[plot 2,bar group size={2}{3}, blue]
+    \addplot[plot 2,bar group size={2}{3}, cyan]
     coordinates {(Exp. 1,161.4)};
@@
     coordinates {(Exp. 1,107.6)};
-    \addplot[plot 2,bar group size={2}{3}, blue]
+    \addplot[plot 2,bar group size={2}{3}, cyan]
     coordinates {(Exp. 1,116.2)};

### 2020-06-01 paper.tex
Conclusion

@@
 
-\tikzstyle{startstop} = [ellipse,minimum width=2cm, minimum height=1cm, text centered, draw=black, fill=white]
+\tikzstyle{Startstop} = [ellipse,minimum width=2cm, minimum height=1cm, text centered, draw=black, fill=white]
 \tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=2cm, minimum height=1cm, text centered, draw=black, fill=white]
@@
 The obtained solution is then projected back to \textit{3D} by assignment of layers.
-as introduced in most of modern designs as in \cite{b1}, \cite{b2}, \cite{b3}, \cite{b4}, \cite{b5}, \cite{b6}, \cite{b7}, and \cite{b8}.
+as introduced in most of modern designs as in \cite{b1}, \cite{b10}, \cite{b3}, \cite{b4}, \cite{b5}, and \cite{b6}, another less common approach is to route on the \textit{3D} grid directly as in \cite{b9} which applies maze algorithm on the \textit{3D} space, also \cite{b14} uses linear programming to apply routing on the \textit{3D} space, although this approach makes good results, it takes a high runtime and solution space.
 At first global routing is run which is responsible for making an approximate routing for the whole circuit in order to be used as a guide for detailed routing, then the detailed routing is run to make the exact routing for the system.
@@
 First BLC (bounded length constraint) is defined as a greater number than Manhattan distance then to go from source to target the neighbor points are tested if it can be a part of a path or not, each point that violates the BLC constraint is discarded.
-Second, if the route started from point \textit{v}, ended at point \textit{u} and there were many paths between these two points, the normal maze algorithm will take the path with the minimum cost which may cause the route to pass through congestions, but in optimal-BLMR, it keeps track of all paths between these two points in order to choose the path that will not cause overflow, it iterates on the minimum cost path every time and if it found a suitable path it reserves that path, otherwise, it discards that path.
+Second, if the route Started from point \textit{v}, ended at point \textit{u} and there were many paths between these two points, the normal maze algorithm will take the path with the minimum cost which may cause the route to pass through congestions, but in optimal-BLMR, it keeps track of all paths between these two points in order to choose the path that will not cause overflow, it iterates on the minimum cost path every time and if it found a suitable path it reserves that path, otherwise, it discards that path.
 Third step the optimal-BLMR iterates on the reserved paths and choose the one to be used for routing.
@@
 \par
-In \cite{b4}, both of via count and runtime are reduced, this done by integrating \cite{b10}, \cite{b11}, and \cite{b12} with via aware Steiner tree generation, 3-bend routing, and layer assignment with careful edge and net ordering to create \cite{b4}.
+In \cite{b4}, both of via count and runtime are reduced, this done by integrating \cite{b2}, \cite{b11}, and \cite{b12} with via aware Steiner tree generation, 3-bend routing, and layer assignment with careful edge and net ordering to create \cite{b4}.
 Via aware Steiner tree is used to at the beginning of the global routing, it generates a suitable topology, by changing tree topology the via count greatly changed, which means that using a suitable topology for Steiner tree will greatly reduce the via count.
@@
     \State Openlist Nodes $\delta$ % Nodes still to be visited. pq
-    \State The cost from starting point to a given node $g$
+    \State The cost from Starting point to a given node $g$
     \State The heuristic function $h$
@@
 As a means to have a concrete, viable evaluation of either the proposed algorithm or any other scheduling algorithm, the output parameters are taken into consideration for analysis.
-Since the average waiting time indicates the average time that a  process had to starve for, therefore the lower the average waiting time is the better.
+Since the average waiting time indicates the average time that a  process had to Starve for, therefore the lower the average waiting time is the better.
 The same principle applies to the average turnaround time and the number of context switches, as the former implies the average time spent by the process since its arrival time to its completion and the latter costs time as the CPU is assigned back and forth between different processes.
@@
 \end{figure}
-
-Even though $P_{5}$ is initially assigned to $Q_{3}$ as in Table \ref{table1}, it was promoted to $Q_{2}$ due to satisfying inequality (\ref{eq1}).
 
@@
 
-The goal of this paper is to tackle different shortcomings associated with the standard MLFQ scheduling algorithm as well as its variants discussed in several papers.
-To resolve these deficiencies, we introduced different adjustable policies and techniques.
-It is evidently clear that those methods yield better CPU performance and optimize utilization by reducing the average waiting time as well as the average turnaround time.
-Despite experimenting numerous combinations of the parameters and scheduling policies by which the proposed MLFQ algorithm operates, we can say that there is yet a large room for experiment and improvement through finding better methods and policies which would make the algorithm more adaptable to the nature of the submitted processes and overall more enhanced.
-For instance, adjusting the criteria by which the schedular decides whether to promote a process might further lessen starvation.
-Making the proposed algorithm preemptive might also aid mitigating starvation and render overall better performance.
-The possibilities are limitless.
+In the process of physical design, routing is among the most critical steps and is usually a very challenging problem.
+Effective and powerful routing algorithms are important to deal with the challenges emerging from the increasingly growing scale of IC integration, Routers will continue to evolve with rapidly growing design challenges like signal integrity, nanometer effects, reliability, etc.
+The goal of this paper is to develop A-Star-based global Router with minimum wire length and the number of vias as the more vias number the more heat generated from the chip with minimum run time.
+In order to optimize the time parameter, we use a heuristic function that decreases the run time of router and test it with different constants to define its effect on run time, for future work we aim to define an effective heuristic function to improve the running time.
+And build upon A-Star algorithm using more efficient versions of A-Star algorithm such as bi-directional A-Star, iterative deepening A-Star.
+In bi-directional A-Star that processes edges in both directions that improve the running time as well as it saves the memory demand for path saving as we will deal with both directions of edge.
 
@@
 
-    \bibitem{b1} Muhammet Mustafa Ozdal and M. D. F. Wong, \char`\"{}Archer: a history-driven global routi algorithm,\char`\"{} \textit{2007
-    IEEE/ACM International Conference on Computer-Aided Design}, San Jose,
-    CA, 2007, pp. 488-495, doi: 10.1109/ICCAD.2007.4397312.
-
-    \bibitem{b2} Chang, Yen-Jung, Yu-Ting Lee, and Ting-Chi Wang.
-"NTHU-Route 2.0: a fast and stable global router." \textit{2008 IEEE/ACM International Conference on Computer-Aided Design.
-IEEE}, 2008.
+    \bibitem{b1} Liu, Wen-Hao, et al.
+"NCTU-GR 2.0: Multithreaded collision-aware global routing with bounded-length maze routing." \textit{IEEE Transactions on computer-aided design of integrated circuits and systems} 32.5 (2013): 709-722.
+
+    \bibitem{b2} Zhang, Yanheng, Yue Xu, and Chris Chu.
+"FastRoute3.
+0: a fast and high quality global router based on virtual capacity." \textit{2008 IEEE/ACM International Conference on Computer-Aided Design.} IEEE, 2008.
 
@@
 
-    \bibitem{b10} Zhang, Yanheng, Yue Xu, and Chris Chu.
-"FastRoute3.
-0: a fast and high quality global router based on virtual capacity." \textit{2008 IEEE/ACM International Conference on Computer-Aided Design.} IEEE, 2008.
+    \bibitem{b10} Chang, Yen-Jung, Yu-Ting Lee, and Ting-Chi Wang.
+"NTHU-Route 2.0: a fast and stable global router." \textit{2008 IEEE/ACM International Conference on Computer-Aided Design.
+IEEE}, 2008.
 
@@
 
+    \bibitem{b14} Xu, Yue, and Chris Chu. "MGR: Multi-level global router." \textit{2011 IEEE/ACM International Conference on Computer-Aided Design (ICCAD)}. IEEE, 2011.
+
 \end{thebibliography}

### 2020-06-01 paper.tex
Third Related Work Paper

@@
 \par
-In \cite{b1} a sequential global routing is used and two bounded length maze algorithms as finding path algorithms are provided in order to make the router faster and to avoid congestions thus avoiding overflow, the first one is optimal-BLMR and the second one is heuristic-BLMR.
+In \cite{b1}, a sequential global routing is used and two bounded length maze algorithms as finding path algorithms are provided in order to make the router faster and to avoid congestions thus avoiding overflow, the first one is optimal-BLMR and the second one is heuristic-BLMR.
 optimal-BLMR is used to get the minimum cost paths to be used as routing paths, this can be done in three steps.
@@
 But it has disadvantages too, one of them is the wire length is not optimal, as using 3-bend routing increases the wire length to avoid congestions, another one is caused by layer assignment as if the \textit{2D} was not congestion-free the results will not be accurate.
+\medskip
+\par
+In \cite{b15}, routing efficiency is increased compared to \textit{2D} routers, and runtime is decreased compared to \textit{3D} routers.
+As the \textit{3D} routers achieve efficient results, it will be used but with some modifications to achieve an acceptable runtime.
+At first, initialization is done by running a Steiner tree, pattern routing step, and dynamic programming is used in layer assignment as in \textit{2D} routers like \cite{b4}.
+The second step named coarsening stage, in which, the \textit{3D} grid is split into a hierarchy of levels, a \textit{3D} maze routing is done on each level, starting with the lower level to the higher one, each routed level is projected into the higher one and run the maze algorithm another time to the higher level, which guarantees fewer congestions and less via count as it is a \textit{3D} routing algorithm,
+and the divide and conquer technique they use reduces the time taken.
+So the advantages of this paper are creating more efficient routing than \textit{2D} and \textit{3D} projection that used in most modern papers and reducing the runtime compared to the ordinary \textit{3D} maze routing.
+But there are some disadvantages too, one of them that the results are not efficient enough compared to the \textit{3D} routing algorithms, another one is that the runtime still high compared to \textit{2D} routers.
 
@@
 
-    \bibitem{b14} Xu, Yue, and Chris Chu. "MGR: Multi-level global router." \textit{2011 IEEE/ACM International Conference on Computer-Aided Design (ICCAD)}. IEEE, 2011.
+    \bibitem{b14} Wu, Tai-Hsuan, Azadeh Davoodi, and Jeffrey T.
+Linderoth.
+"GRIP: scalable 3D global routing using integer programming." \textit{Proceedings of the 46th Annual Design Automation Conference}.
+2009.
+
+    \bibitem{b15} Xu, Yue, and Chris Chu. "MGR: Multi-level global router." \textit{2011 IEEE/ACM International Conference on Computer-Aided Design (ICCAD)}. IEEE, 2011.
 

### 2020-06-01 paper.tex
Final paper

--- 2020-06-01 paper.tex
@@
 \usepackage{subfigure}
+\usepackage{multirow}
+\usepackage{float}
+\usepackage{adjustbox}
 
@@
 
-\title{Improved Global Routing By Using A Star Algorithm\\}
+\title{Improved Global Routing By Using A-Star Algorithm\\}
 
@@
 But it has disadvantages too, one of them is the wire length is not optimal, as using 3-bend routing increases the wire length to avoid congestions, another one is caused by layer assignment as if the \textit{2D} was not congestion-free the results will not be accurate.
+
+\medskip
+\par
+In \cite{b13} they proposed an approach to not only perform pathfinding, but also the global routers are also required to generate a set of connected rectangle guides,  each of which contains an integral number of G-cells so that the detailed router can find a path within the guides to connect all pins of each net and reduce a given cost function to the minimum.
+\\
+The proposed 3D pattern routing generates 3D topologies directly, while the traditional 3D pattern routing only generates 2D topologies and uses an extra layer for the assignment level.
+They, therefore, proposed a combination of 2D pattern routing with layer assignment and used it to choose a path for each two-pin net, and, with the help of dynamic programming, they ensure that an optimal solution can be found if it exists.
+The overall flow of their proposed algorithm can be divided into 3 parts, summarized as follows:
+\begin{enumerate}
+	\item Initial routing:
+    \begin{enumerate}
+    	\item Pattern Routing Planning: \\
+        In order to carry out 3D pattern routing, each multi-pin net first will be broken into set of two pin nets in this step.        
+        \item 3D Pattern Routing with Layer Assignment: \\
+        After breaking down the nets into two-pin nets and decide their order,
+        pattern routing and layer assignment are performed simultaneously using a dynamic programming algorithm.
+        Rather than performing layer assignment after a net is a pattern routed,
+        our dynamic programming algorithm merges the two steps to minimize the overall cost
+        and Prevent loss of precision caused by compressing the 3D grid graph to 2D.
+    \end{enumerate}
+    \item Multi-level 3D Maze Routing: \\
+    After initial routing, the nets with violations will be destroyed and multiple iterations of rip-up and reroute (RRR) may be performed by maze routing.
+The multi-level 3D Maze Routing is repeated until there's no overflow.
+Because the maze routing on the entire 3d  graph would take too much time because of the wide search space, an algorithm that limits the search area to the bounding box of the net will make rerouting much faster, but it may reduce the routing quality.
+    Considering the above, the proposed algorithm Uses multi-level 3d maze routing to allow graph searching process while reaching reasonable trade off between time and routing quality.
+    The proposed routing technique has two levels, each serves a different purpose:
+    \begin{enumerate}
+    	\item  Maze Routing Planning (Bounding Box Generation): \\
+        In order to carry out 3D pattern routing, each multi-pin net will first be broken down into a set of two-pin nets in this step.        
+        \item 3D Maze Routing within Bounding Box (fine-grained maze routing within guides): \\
+        Performs another level of maze routing, it seeks to find a path with the minimum
+        actual cost within the search space.
+    \end{enumerate}
+	\item Route guide generation \& patching: \\
+    The output of the global router is connected rectangular route guides, the algorithm proposes a new technique called patching to add some stand-alone route guides or patches onto the routed path to further improve the detailed routing.
+\end{enumerate}
+
+They introduce a global 3D router that could enhance the routing well in efficiency and quality.
+The 3d routing technique combines 2d routing and assignment of layers and helps most nets to be routed quickly and optimally.
+A patching method that actually contributes to useful route guidance to improve detailed routing in some way.
+An innovative probability-based cost scheme which takes into account the risk of overflow, the total wire length, and it is also capable of reducing the number of via and the total wire length while avoiding overflow and preserving enough edge capacity which is the number of paths that can pass through the edge.
+A multi-level maze routing method which is used to shrink the search space and then performs a bounded maze routing to find a minimum cost path.in that method we decided to work on the time parameter by instead of using the Dijkstra algorithm we will use the A-Star algorithm with a proposed heuristic function that will improve the time.
 
@@
 Hence, our heuristic function composed of Manhattan distance, layer index, and some constants.
-
 \begin{multline*}
-    h = \ln ((\mid p1 \cdot x-p2 \cdot x\mid+\mid p1 \cdot y-p2 \cdot y\mid)*const1) \\ 
+    h = \ln (\mid p1 \cdot x-p2 \cdot x\mid+\mid p1 \cdot y-p2 \cdot y\mid)*const1 \\ 
      +(\mid p1 \cdot layerid-p2 \cdot layerid\mid)*const2 \\
@@
     \If{$s$ or $d$ is blocked}
-        \Return
+        \State \Return
     \EndIf
     \If{$s$ = $d$}
-        \Return
+        \State \Return
     \EndIf
@@
                 \State Get path
-                \Return
+                \State \Return
             \ElsIf{$neighbour \notin \phi$ and $neighbour$ is not blocked}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ASSUMPTIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+we implement global routing with A-Star router algorithm in c++ language
+with Rsyn to parse input test cases files with format LEF/DEF. All
+experiments are performed on a Machine with 2 GHZ Intel Processor
+and 8 GB RAM. our algorithm is focus on three important factors :total
+wire-length, channel congestion ,number of vias. Our target is to
+minimize a convex combination of the total wire-length and the number
+of vias that represent the bends in the tree that result in solving
+the net of pins to be connected.our test cases input are all from
+ICCAD'19 contest for global routing.we test our code with different
+heuristic functions -that affect the run time of A-Star- to check its
+effect on CPU run time.our concern is on wire-length and number of
+vias result from routing without increasing in-feasibility.we generate
+the trees of all nets in parallel to reduce running by using multi-threaded
+approach to generate the net results tree as this step has the most
+costly part of the router algorithm.our algorithm not only route each net to find a path that connect all pins of the net, but it also generate a set of connected rectangle for each net to be used in detailed routing and to minimize its cost.
 
-\subsection{Assumptions}
+\subsubsection{Experiment 1}
 
-The proposed scheduling algorithm is software simulated using a Python script which simulates scheduling independent CPU-bound processes on a single processor environment which guarantees that no more than a single process is getting scheduled at any arbitrary moment.
-Each process is assumed to have its own predetermined burst time, arrival time and the queue to which each one belongs.
-The proposed approach is non-preemptive.
-For the sake of giving an example, if a process was lately introduced to a queue denoted by $Q_{i}$ prior to the current queue getting scheduled, it won't get scheduled until the current queue, its subsequent queues and the queues prior to $Q_{i}$ get scheduled.
+In this experiment we compare run time of router with Dijkstra Router
+and out A-Star router with heuristic function with different constants
+of heuristic functions that affect the run time of the router.heuristic
+function help us to know how near the point to the target point so it help in decreasing the cost of routing:
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% I/O %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{multline*}
+h1=(\mid p1\cdot x-p2\cdot x\mid+\mid p1\cdot y-p2\cdot y\mid)*const1\\
++(\mid p1\cdot layerid-p2\cdot layerid\mid)*const2\\
+\end{multline*}
 
-\subsection{Experimental Scheme}
+\begin{multline*}
+h2=ln(\mid p1\cdot x-p2\cdot x\mid+\mid p1\cdot y-p2\cdot y\mid)*const1\\
++(\mid p1\cdot layerid-p2\cdot layerid\mid)*const2\\
+\end{multline*}
 
-On one hand, the input arguments to the proposed algorithm implementation are the number of processes to be scheduled, their burst time, their arrival time and the queue where each one belongs.
-On the other hand, output parameters are the average waiting time, average turnaround time and throughput.
-The following equations are used to calculate the previously mentioned output parameters:
+\begin{multline*}
+h3=(\mid p1\cdot x-p2\cdot x\mid+\mid p1\cdot y-p2\cdot y\mid)*const1\\
++ln(\mid p1\cdot layerid-p2\cdot layerid\mid)*const2\\
+\end{multline*}
 
-\begin{equation}
-    Average\; Waiting\; Time =  \frac{Total \; Waiting \; Time}{Number \; of \; Processes} \label{eq2}
-\end{equation}
-
-\begin{equation}
-    Average\; Turnaround\; Time =  \frac{Total \; Turnaround \; Time}{Number \; of \; Processes} \label{eq3}
-\end{equation}
-
-\begin{equation}
-    Throughput =  \frac{Number \; of \; Executed \; Processes}{Total \; Execution \; Time} \label{eq4}
-\end{equation}
-
-% \vspace{4mm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PERFORMANCE METRICS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Performance Metrics}
-
-As a means to have a concrete, viable evaluation of either the proposed algorithm or any other scheduling algorithm, the output parameters are taken into consideration for analysis.
-Since the average waiting time indicates the average time that a  process had to Starve for, therefore the lower the average waiting time is the better.
-The same principle applies to the average turnaround time and the number of context switches, as the former implies the average time spent by the process since its arrival time to its completion and the latter costs time as the CPU is assigned back and forth between different processes.
-Contrarily to the prior metrics, the larger the throughput is the better as it indicates the number of processes that are completely executed per unit time.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SIMULATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Simulation}
-
-For the sake of showcasing the proposed algorithm, a number of processes, their predetermined burst time values and their arrival time values are taken as input to the Python simulation script.
-Suppose that the input to the script is according to the following table:
-
-\begin{table}[H]
-    \caption{}
-    \centering
-     \begin{tabular}{||c c c c||} 
+{\tiny{}}
+\begin{table}[b]
+{\tiny{}\caption{\label{tab:Compare-run-time}Compare run time of Dijkstra router and
+A-Star router with Heuristic-Function 1}
+}{\tiny\par}
+\centering{}{\footnotesize{}}%
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|c|c|c|c|c|c|}
 \hline 
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
+\multirow{2}{*}{{\footnotesize{}Design}} & \multicolumn{4}{c|}{{\footnotesize{}A-Star}} & \multirow{2}{*}{{\footnotesize{}Dijkstra}}\tabularnewline
+\cline{2-5} \cline{3-5} \cline{4-5} \cline{5-5} 
+ & {\footnotesize{}(0.2,0.1)} & {\footnotesize{}(0.3,0.3)} & {\footnotesize{}(0.5,0.5)} & \multicolumn{1}{c||}{{\footnotesize{}(0.5,0.5)}} & \tabularnewline
 \hline 
 \hline 
-     1 & 0 & 60 & 1 \T \B \\ 
+{\footnotesize{}test1} & {\footnotesize{}75.843764} & {\footnotesize{}87.797614} & {\footnotesize{}87.086193} & {\footnotesize{}96.377979} & {\footnotesize{}91.348007}\tabularnewline
 \hline 
-     2 & 0 & 50 & 1 \T \B \\
+{\footnotesize{}test2} & {\footnotesize{}2.511599} & {\footnotesize{}2.606054} & {\footnotesize{}2.874605} & {\footnotesize{}2.497377} & {\footnotesize{}3.435606}\tabularnewline
 \hline 
-     3 & 0 & 40 & 2 \T \B \\
+{\footnotesize{}test3} & {\footnotesize{}12.381436} & {\footnotesize{}14.959666} & {\footnotesize{}14.859677} & {\footnotesize{}14.766495} & {\footnotesize{}11.824573}\tabularnewline
 \hline 
-     4 & 0 & 30 & 2 \T \B \\
+{\footnotesize{}test4} & {\footnotesize{}0.075472} & {\footnotesize{}0.073069} & {\footnotesize{}0.073769} & {\footnotesize{}0.072691} & {\footnotesize{}0.071829}\tabularnewline
 \hline 
-     5 & 0 & 10 & 3 \T \B \\ 
+{\footnotesize{}test5} & {\footnotesize{}0.073988} & {\footnotesize{}0.072911} & {\footnotesize{}0.074165} & {\footnotesize{}0.072767} & {\footnotesize{}0.071945}\tabularnewline
 \hline 
-     6 & 0 & 210 & 3 \T \B \\ 
+{\footnotesize{}test6} & {\footnotesize{}6.948016} & {\footnotesize{}6.266789} & {\footnotesize{}5.198969} & {\footnotesize{}6.906992} & {\footnotesize{}7.0385}\tabularnewline
 \hline 
-     7 & 0 & 200 & 3 \T \B \\ 
+\end{tabular}{\footnotesize\par}
+\end{adjustbox}
+\end{table}
+{\tiny\par}
+
+\begin{table}
+\caption{\label{tab:Compare-run-time-1}Compare run time of Dijkstra router
+and A-Star router with Heuristic-Function 2}
+
+\centering{}{\footnotesize{}}%
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|c|c|c|c|c|c|}
 \hline 
-     \end{tabular}
-     \label{table1}
+\multirow{2}{*}{{\footnotesize{}Design}} & \multicolumn{4}{c|}{{\footnotesize{}A-Star}} & \multirow{2}{*}{{\footnotesize{}Dijkstra}}\tabularnewline
+\cline{2-5} \cline{3-5} \cline{4-5} \cline{5-5} 
+ & {\footnotesize{}(0.1,0.1)} & {\footnotesize{}(0.2,0.1)} & {\footnotesize{}(0.3,0.3)} & {\footnotesize{}(0.5,0.5)} & \tabularnewline
+\hline 
+\hline 
+{\footnotesize{}test1} & {\footnotesize{}90.440165} & {\footnotesize{}93.288501} & {\footnotesize{}89.414646} & {\footnotesize{}96.377979} & {\footnotesize{}91.348007}\tabularnewline
+\hline 
+{\footnotesize{}test2} & {\footnotesize{}2.461400} & {\footnotesize{}2.469304} & {\footnotesize{}2.480592} & {\footnotesize{}2.497377} & {\footnotesize{}3.435606}\tabularnewline
+\hline 
+{\footnotesize{}test3} & {\footnotesize{}12.264829} & {\footnotesize{}13.449206} & {\footnotesize{}12.039944} & {\footnotesize{}14.766495} & {\footnotesize{}11.824573}\tabularnewline
+\hline 
+{\footnotesize{}test4} & {\footnotesize{}0.071577} & {\footnotesize{}0.157244} & {\footnotesize{}0.078624} & {\footnotesize{}0.072691} & {\footnotesize{}0.071829}\tabularnewline
+\hline 
+{\footnotesize{}test5} & {\footnotesize{}0.078316} & {\footnotesize{}0.090906} & {\footnotesize{}0.071333} & {\footnotesize{}0.072767} & {\footnotesize{}0.071945}\tabularnewline
+\hline 
+{\footnotesize{}test6} & {\footnotesize{}6.893310} & {\footnotesize{}6.400888} & {\footnotesize{}6.974920} & {\footnotesize{}6.906992} & {\footnotesize{}7.038505}\tabularnewline
+\hline 
+\end{tabular}{\footnotesize\par}
+\end{adjustbox}
 \end{table}
 
-According to the proposed algorithm, the time quanta calculated are as follows:
-
-\begin{table}[H]
-    \caption{}
-    \centering
-     \begin{tabular}{||c c||} 
+\begin{table}
+{\tiny{}\caption{\label{tab:Continue-compare-run} compare run time of Dijkstra router
+and A-Star router with Heuristic-Function 3}
+}{\tiny\par}
+\centering{}{\footnotesize{}}%
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|c|c|c|c|c|c|}
 \hline 
-     \textit{\textbf{Queue}} & \textit{\textbf{Quantum Value}} \T \B \\ 
+\multirow{2}{*}{{\footnotesize{}Design}} & \multicolumn{4}{c|}{{\footnotesize{}A-Star}} & \multirow{2}{*}{{\footnotesize{}Dijkstra}}\tabularnewline
+\cline{2-5} \cline{3-5} \cline{4-5} \cline{5-5} 
+ & {\footnotesize{}(0.1,0.1)} & {\footnotesize{}(0.2,0.1)} & {\footnotesize{}(0.3,0.3)} & {\footnotesize{}(0.5,0.5)} & \tabularnewline
 \hline 
 \hline 
-     1 & 55 \T \B \\ 
+{\footnotesize{}test1} & {\footnotesize{}86.598509} & {\footnotesize{}83.204272} & {\footnotesize{}103.166426} & {\footnotesize{}102.378304} & {\footnotesize{}91.348007}\tabularnewline
 \hline 
-     2 & 40 \T \B \\
+{\footnotesize{}test2} & {\footnotesize{}2.481847} & {\footnotesize{}2.486656} & {\footnotesize{}3.622759} & {\footnotesize{}2.556863} & {\footnotesize{}3.435606}\tabularnewline
 \hline 
-     3 & 615 \T \B \\
+{\footnotesize{}test3} & {\footnotesize{}12.655603} & {\footnotesize{}15.447421} & {\footnotesize{}15.629251} & {\footnotesize{}20.004493} & {\footnotesize{}11.824573}\tabularnewline
 \hline 
-     4 & 0 \T \B \\
+{\footnotesize{}test4} & {\footnotesize{}0.073731} & {\footnotesize{}0.070911} & {\footnotesize{}0.073468} & {\footnotesize{}0.103421} & {\footnotesize{}0.071829}\tabularnewline
 \hline 
-     5 & 0 \T \B \\ 
+{\footnotesize{}test5} & {\footnotesize{}0.078171} & {\footnotesize{}0.079362} & {\footnotesize{}0.088107} & {\footnotesize{}0.099699} & {\footnotesize{}0.071945}\tabularnewline
+\hline 
+{\footnotesize{}test6} & {\footnotesize{}6.470339} & {\footnotesize{}7.195767} & {\footnotesize{}8.455288} & {\footnotesize{}7.637577} & {\footnotesize{}7.038505}\tabularnewline
+\hline 
+\end{tabular}{\footnotesize\par}
+\end{adjustbox}
+\end{table}
+
+we notice from Table\ref{tab:Compare-run-time},Table\ref{tab:Continue-compare-run},Table\ref{tab:Compare-run-time-1}
+that heuristic function affect the running time of router ,decreases
+it to be lower than Dijkstra router's running time in many test cases.
+the running time changes with the change of heuristic function constants.
+we notice that higher constants increase the running time and sometimes
+be greater than Dijkstra router's run time. Heuristic function 2 has
+overall results which is better than others, with using more efficient
+heuristic functions,run time and wire-length and vias number combination
+may improve greatly.
+
+\subsection{Performance Comparisons}
+
+we used ISPD19 benchmarks to compare out results with another global
+routing algorithms such as TripleZ and NTUidRoute. we compare the
+results in terms of total wire length score and vias score. we compare
+results of our algorithm which focus on factors - total wire-length,number
+of vias in the routing results - with TripleZ and NTUidRoute algorithms
+in ICCAD'19 Table\ref{tab:compared-Wire-Lengh},Table \ref{tab:compared-Vias}
+.we use multi-threaded approach to generate net result trees in parallel
+so we have done our experiments using 8 threads in all test cases.
+score used as unit to compare ,score of wire length is a function
+of metal pitch and wire length and weight:
+
+\[
+WLScore=\frac{wire-length*weight}{metal-pitch}
+\]
+
+score of vias is function of number of vias :
+
+\[
+ViasScore=\#vias*2
+\]
+
+{\tiny{}}
+\begin{table}
+{\tiny{}\caption{\label{tab:compared-Wire-Lengh}compared Wire Length with TripleZ and
+NTUidRoute Algorithms in ICCAD'19 Global routing Contest }
+}{\tiny\par}
+\centering{}{\footnotesize{}}%
+\begin{tabular}{|c|c|c|c|}
+\hline 
+\multirow{2}{*}{{\footnotesize{}Design}} & \multicolumn{3}{c|}{{\footnotesize{}wire-length scores}}\tabularnewline
+\cline{2-4} \cline{3-4} \cline{4-4} 
+ & {\footnotesize{}TripleZ} & {\footnotesize{}NTUidRoute} & {\footnotesize{}ours}\tabularnewline
+\hline 
+{\footnotesize{}test1} & {\footnotesize{}12485549.76} & {\footnotesize{}12992510.61} & {\footnotesize{}12150100}\tabularnewline
+\hline 
+{\footnotesize{}test2} & {\footnotesize{}569622.01} & {\footnotesize{}466809.64} & {\footnotesize{}389460}\tabularnewline
+\hline 
+{\footnotesize{}test7} & {\footnotesize{}17800019.36} & {\footnotesize{}15935101.91} & {\footnotesize{}14663400}\tabularnewline
+\hline 
+{\footnotesize{}test3} & {\footnotesize{}2859212.04} & {\footnotesize{}2495661.79} & {\footnotesize{}2851900}\tabularnewline
+\hline 
+{\footnotesize{}test8} & {\footnotesize{}74264784.88} & {\footnotesize{}65028116.52} & {\footnotesize{}70041500}\tabularnewline
+\hline 
+{\footnotesize{}Avg} & {\footnotesize{}21595837.61} & {\footnotesize{}19383640} & {\footnotesize{}20019272}\tabularnewline
+\hline 
+\end{tabular}{\footnotesize\par}
+\end{table}
+{\tiny\par}
+
+\begin{table} [hbt!]
+\centering{}{\footnotesize{}\caption{\label{tab:compared-Vias}compared Vias TripleZ and NTUidRoute Algorithms
+in ICCAD'19 Global routing Contest}
+}%
+\begin{tabular}{|c|c|c|c|}
+\hline 
+\multirow{2}{*}{{\footnotesize{}Design}} & \multicolumn{3}{c|}{{\footnotesize{}vias score}}\tabularnewline
+\cline{2-4} \cline{3-4} \cline{4-4} 
+ & {\footnotesize{}TripleZ} & {\footnotesize{}NTUidRoute} & {\footnotesize{}ours}\tabularnewline
+\hline 
+\hline 
+{\footnotesize{}test1} & {\footnotesize{}3261476.00} & {\footnotesize{}4017448.00} & {\footnotesize{}2803560}\tabularnewline
+\hline 
+{\footnotesize{}test2} & {\footnotesize{}251728.00} & {\footnotesize{}318404.00} & {\footnotesize{}176728}\tabularnewline
+\hline 
+{\footnotesize{}test7} & {\footnotesize{}4265744.00} & {\footnotesize{}4789488.00} & {\footnotesize{}2666120}\tabularnewline
+\hline 
+{\footnotesize{}test3} & {\footnotesize{}695348.00} & {\footnotesize{}771328.00} & {\footnotesize{}446024}\tabularnewline
+\hline 
+{\footnotesize{}test8} & {\footnotesize{}19689760.00} & {\footnotesize{}23183264.00} & {\footnotesize{}12532800}\tabularnewline
+\hline 
+{\footnotesize{}Avg} & {\footnotesize{}5632811.2} & {\footnotesize{}6615986.4} & {\footnotesize{}3725046.4}\tabularnewline
 \hline 
@@
 
-All processes are sorted in ascending order according to their remaining time and are scheduled by assigning the time quantum calculated for their respective queue.
-The time spent scheduling a particular queue is the waiting time for its subsequent queues.
-
-The scheduling process goes as follows:
-
-\begin{figure}[H]
-        \begin{center}
-        \begin{tabular}{|c|c|}
-         \hline
-            $P_{2}$ & $P_{1}$\T\B\\ 
-         \hline
-        \end{tabular}
-        \end{center}
-        \begin{center}
-            \begin{tabular}{c c c}
-                   0 & 50 & 105\\ 
-            \end{tabular}
-        \end{center}
-    \caption{$Q_{1}$ Gantt Chart}
-\end{figure}
-
-Considering that each process in $Q_{1}$ is assigned a quantum value of $50$, as we reach the last process in $Q_{1}$, the total time elapsed equals $105$, which happens to be the time that all the other processes in the subsequent queues had to wait for, hence the addition of their waiting time by a value of $105$ units of time.
-
-\begin{figure}[H]
-    \begin{center}
-    \begin{tabular}{|c|c|c|c|}
-     \hline
-        $P_{1}$ & $P_{5}$ & $P_{4}$ & $P_{3}$\T\B\\ 
-     \hline
-    \end{tabular}
-    \end{center}
-    \begin{center}
-        \begin{tabular}{c c c c c}
-               105 & 110 & 120 & 150 & 190\\ 
-        \end{tabular}
-    \end{center}
-\caption{$Q_{2}$ Gantt Chart}
-\end{figure}
-
-\begin{figure}[H]
-    \begin{center}
-    \begin{tabular}{|c|c|}
-     \hline
-        P7 & P6\T\B\\ 
-     \hline
-    \end{tabular}
-    \end{center}
-    \begin{center}
-        \begin{tabular}{c c c}
-               190 & 390 & 600\\ 
-        \end{tabular}
-    \end{center}
-\caption{$Q_{3}$ Gantt Chart}
-\end{figure}
-
-Whenever processes reach the lowest queue precompletion, they are scheduled using the RR scheduling algorithm with a relatively large quantum time value which is in most cases similar to using the FCFS algorithm because, as the time quantum value of an RR algorithm tends to infinity which could practically be a very large number relative to the available processes remaining time values, the algorithm tends to morph into the FCFS algorithm.
-This procedure is iterated until all the processes are finished.
-Simulation results are shown in the table below:
-
-\begin{table}[H]
-    \caption{}
-    \centering
-     \begin{tabular}{||c c c||} 
-     \hline
-     \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}} & \textit{\textbf{Throughput}}\T \B \\ 
-     \hline
-     \hline
-     230 & 144.3 & 0.011667 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% COMPARISONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Performance Comparisons}
-
-To assess the performance of the proposed algorithm implementation, multiple test cases are addressed and analyzed in seven different experiments.
-In each experiment, the output of the proposed algorithm implementation is compared to the output of another scheduling algorithm implementation addressed in a different paper, such as standard MLFQ algorithm with static quantum RR and other variants of MLFQ algorithms and RR algorithms.
-
-\subsubsection{Experiment 1}
-
-In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in {b4}.
-The first uses a static version of the RR algorithm for scheduling each queue, while the second variant uses a dynamic version of the RR algorithm for doing so.
-
-\begin{table}[H]
-    \caption{Experiment 1 Input}
-    \centering
-     \begin{tabular}{||c c c c||} 
-     \hline
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
-     \hline
-     \hline
-     1 & 1 & 25 & 1 \T \B \\ 
-     \hline
-     2 & 5 & 70 & 1 \T \B \\
-     \hline
-     3 & 6 & 84 & 1 \T \B \\
-     \hline
-     4 & 7 & 17 & 1 \T \B \\
-     \hline
-     5 & 8 & 35 & 1 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-\begin{table}[H]
-    \caption{Experiment 1 Results}
-    \centering
-    \begin{tabular}{||c c c||}
-        \hline
-        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
-    \hline
-    \hline
-    \textbf{Proposed Algorithm} & 115 & 68.8 \T \B\\ \hline
-    \textbf{Dynamic RR MLFQ} & 150.8 & 107.6\T \B\\ \hline
-    \textbf{Static RR MLFQ} & 161.4 & 116.2 \T \B\\ \hline
-     \end{tabular}
-\end{table}
-
-\subsubsection{Experiment 2}
-
-In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in {b4}.
-The first uses a static version of the SJFRR algorithm for scheduling each queue, while the second variant uses a dynamic version of the SJFRR algorithm for doing so.
-
-\begin{table}[H]
-    \caption{Experiment 2 Input}
-    \centering
-     \begin{tabular}{||c c c c||} 
-     \hline
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
-     \hline
-     \hline
-     1 & 1 & 25 & 1 \T \B \\ 
-     \hline
-     2 & 5 & 70 & 1 \T \B \\
-     \hline
-     3 & 6 & 84 & 1 \T \B \\
-     \hline
-     4 & 7 & 17 & 1 \T \B \\
-     \hline
-     5 & 8 & 35 & 1 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-\begin{table}[H]
-    \caption{Experiment 2 Results}
-    \centering
-    \begin{tabular}{||c c c||}
-        \hline
-        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
-    \hline
-    \hline
-    \textbf{Proposed Algorithm} & 115 & 68.8 \T \B\\ \hline
-    \textbf{Dyn. SJFRR MLFQ} & 134 & 91.8\T \B\\ \hline
-    \textbf{Stat. SJFRRMLFQ} & 143.4 & 98.2 \T \B\\ \hline
-     \end{tabular}
-\end{table}
-
-\subsubsection{Experiment 3}
-
-In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in {b5}.
-The first uses a static version of the SJFRR algorithm for scheduling each queue, while the second variant uses a dynamic version of the SJFRR algorithm for doing so.
-
-\begin{table}[H]
-    \caption{Experiment 3 Input}
-    \centering
-     \begin{tabular}{||c c c c||} 
-     \hline
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
-     \hline
-     \hline
-     1 & 0 & 8 & 1 \T \B \\ 
-     \hline
-     2 & 3 & 133 & 3 \T \B \\
-     \hline
-     3 & 2 & 21 & 2 \T \B \\
-     \hline
-     4 & 8 & 39 & 2 \T \B \\
-     \hline
-     5 & 19 & 67 & 2 \T \B \\ 
-     \hline
-     6 & 33 & 114 & 3 \T \B \\ 
-     \hline
-     7 & 33 & 54 & 2 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-\begin{table}[H]
-    \caption{Experiment 3 Results}
-    \centering
-    \begin{tabular}{||c c c||}
-        \hline
-        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
-    \hline
-    \hline
-    \textbf{Proposed Algorithm} & 151 & 88.7 \T \B\\ \hline
-    \textbf{Dyn. SJFRR MLFQ} & 252 & 119 \T \B\\ \hline
-    \textbf{Stat. SJFRR MLFQ} & 351 & 228 \T \B\\ \hline
-     \end{tabular}
-\end{table}
-
-\subsubsection{Experiment 4}
-
-In this experiment, the proposed algorithm is compared against multiple variants of the MLFQ algorithm that are stated in {b6}: standard MLFQ algorithm, a priority-based MLFQ algorithm and a vague logic-based MLFQ algorithm.
-
-\begin{table}[H]
-    \caption{Experiment 4 Input}
-    \centering
-     \begin{tabular}{||c c c c||} 
-     \hline
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
-     \hline
-     \hline
-     1 & 0 & 40 & 1 \T \B \\ 
-     \hline
-     2 & 0 & 30 & 1 \T \B \\
-     \hline
-     3 & 0 & 50 & 1 \T \B \\
-     \hline
-     4 & 2 & 70 & 1 \T \B \\
-     \hline
-     5 & 4 & 25 & 1 \T \B \\ 
-     \hline
-     6 & 6 & 60 & 1 \T \B \\ 
-     \hline
-     7 & 7 & 45 & 1 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-\begin{table}[H]
-    \caption{Experiment 4 Results} 
-    \centering
-    \begin{tabular}{||c c c||}
-        \hline
-        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
-    \hline
-    \hline
-    \textbf{Proposed Algorithm} & 185.85 & 140.14 \T \B\\ \hline
-    \textbf{VMLFQ} & 190 & 170 \T \B\\ \hline
-    \textbf{MLFQ} & 232.14 & 175 \T \B\\ \hline
-    \textbf{PMLFQ} & 240 & 180 \T \B\\ \hline
-     \end{tabular}
-\end{table}
-
-\subsubsection{Experiment 5}
-
-This experiment is the same as the previous one, but with a different input test case.
-
-\begin{table}[H]
-    \caption{Experiment 5 Input}
-    \centering
-     \begin{tabular}{||c c c c||} 
-     \hline
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
-     \hline
-     \hline
-     1 & 0 & 90 & 1 \T \B \\ 
-     \hline
-     2 & 0 & 30 & 1 \T \B \\
-     \hline
-     3 & 0 & 28 & 1 \T \B \\
-     \hline
-     4 & 0 & 57 & 1 \T \B \\
-     \hline
-     5 & 0 & 73 & 1 \T \B \\ 
-     \hline
-     6 & 0 & 19 & 1 \T \B \\ 
-     \hline
-     7 & 0 & 42 & 1 \T \B \\ 
-     \hline
-     8 & 0 & 67 & 1 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-\begin{table}[H]
-    \caption{Experiment 5 Results}
-    \centering
-    \begin{tabular}{||c c c||}
-        \hline
-        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
-    \hline
-    \hline
-    \textbf{Proposed Algorithm} & 212.5 & 161.75 \T \B\\ \hline
-    \textbf{VMLFQ} & 260 & 225 \T \B\\ \hline
-    \textbf{MLFQ} & 290 & 240 \T \B\\ \hline
-    \textbf{PMLFQ} & 300 & 245 \T \B\\ \hline
-     \end{tabular}
-\end{table}
-
-\subsubsection{Experiment 6}
-
-In this experiment, the proposed algorithm is compared against two variants of the RR algorithm stated in {b3}.
-The first is a static version of the RR algorithm with a constant quantum value of $25$ for scheduling each queue while the second uses a dynamic version of the RR algorithm called SRBRR for doing so.
-
-\begin{table}[H]
-    \caption{Experiment 6 Input}
-    \centering
-     \begin{tabular}{||c c c c||} 
-     \hline
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
-     \hline
-     \hline
-     1 & 0 & 13 & 1 \T \B \\ 
-     \hline
-     2 & 0 & 35 & 1 \T \B \\
-     \hline
-     3 & 0 & 46 & 1 \T \B \\
-     \hline
-     4 & 0 & 63 & 1 \T \B \\
-     \hline
-     5 & 0 & 97 & 1 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-\begin{table}[H]
-    \caption{Experiment 6 Results}
-    \centering
-    \begin{tabular}{||c c c||}
-        \hline
-        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
-    \hline
-    \hline
-    \textbf{Proposed Algorithm} & 113.2 & 62.4 \T \B\\ \hline
-    \textbf{Dynamic SRBRR} & 122.4 & 71.6 \T \B\\ \hline
-    \textbf{Static RR} & 148.2 & 97.4 \T \B\\ \hline
-     \end{tabular}
-\end{table}
-
-\subsubsection{Experiment 7}
-
-This experiment is the same as the previous one, but with a different input test case.
-Note that for this test case, a process queue number is irrelevant to both the RR algorithm and the SRBRR algorithm mentioned in {b3}.
-
-\begin{table}[H]
-    \caption{Experiment 7 Input}
-    \centering
-     \begin{tabular}{||c c c c||} 
-     \hline
-     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
-     \hline
-     \hline
-     1 & 0 & 54 & 1 \T \B \\ 
-     \hline
-     2 & 0 & 99 & 3 \T \B \\
-     \hline
-     3 & 0 & 5 & 2 \T \B \\
-     \hline
-     4 & 0 & 27 & 2 \T \B \\
-     \hline
-     5 & 0 & 32 & 2 \T \B \\ 
-     \hline
-     \end{tabular}
-\end{table}
-
-\begin{table}[H]
-    \caption{Experiment 7 Results}
-    \centering
-    \begin{tabular}{||c c c||}
-        \hline
-        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
-    \hline
-    \hline
-    \textbf{Dynamic SRBRR} & 93.6 & 50.2 \T \B\\ \hline
-    \textbf{Proposed Algorithm} & 106.8 & 63.4 \T \B\\ \hline
-    \textbf{Static RR} & 152.2 & 108.8 \T \B\\ \hline
-     \end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% OBSERVATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Observation}
 
-From the above simulations of different test cases and multiple performance comparisons that involved as many as 11 different scheduling algorithms not including this paper algorithm, it is clear that the average turnaround time and the average waiting time of the proposed algorithm is less than or – in few occasions  – nearly equal to those of the stated algorithms.
-With that said, the proposed algorithm is arguably advantageous over those algorithms, considering even the case in which it underperformed compared to the SRBRR algorithm, it is still favourable due to the capability to separate processes into categories based on their need for the processor and other advantages of the MLFQ algorithm.
-The performance of the proposed algorithm compared to other algorithms is further illustrated in the following graphs:
-
-\begin{figure}[H]
-    \begin{center}
-\begin{tikzpicture}
-    \begin{axis}[
-        width=0.475*\textwidth,
-        symbolic x coords={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
-        ylabel=Avg. Turnaround Time,
-        enlargelimits=0.15,
-        legend style={at={(0.5,-0.25)}, anchor=north,legend columns=1},
-        ybar,
-        xtick={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
-        x tick label style={rotate=45,anchor=east},
-        bar width=3pt,
-        cycle list name=color list
-    ]
-
-    \addplot[plot 0,bar group size={0}{3}, red]
-    coordinates {(Exp. 1,115) (Exp. 2,115) (Exp. 3,151) (Exp. 6,113.2) (Exp. 7,106.8)};
-    \addplot[plot 1,bar group size={1}{3}, green]
-    coordinates {(Exp. 1,150.8)};
-    \addplot[plot 2,bar group size={2}{3}, cyan]
-    coordinates {(Exp. 1,161.4)};
-
-    \addplot[plot 1,bar group size={1}{3}, black]
-    coordinates {(Exp. 2,134)};
-    \addplot[plot 2,bar group size={2}{3}, brown]
-    coordinates {(Exp. 2,143.4)};
-
-    \addplot[plot 1,bar group size={1}{3}, teal]
-    coordinates {(Exp. 3,252)};
-    \addplot[plot 2,bar group size={2}{3}, violet]
-    coordinates {(Exp. 3,351)};
-
-    \addplot[plot 0,bar group size={0}{4}, red]
-    coordinates {(Exp. 4,185.85) (Exp. 5,212.5)};
-    \addplot[plot 1,bar group size={1}{4}, lime]
-    coordinates {(Exp. 4,190) (Exp. 5,260)};
-    \addplot[plot 2,bar group size={2}{4}, orange]
-    coordinates {(Exp. 4,232.14) (Exp. 5,290)};
-    \addplot[plot 3,bar group size={3}{4}, olive]
-    coordinates {(Exp. 4,240) (Exp. 5,300)};
-
-    \addplot[plot 1,bar group size={1}{3}, cyan]
-    coordinates {(Exp. 6,122.4) (Exp. 7,93.6)};
-    \addplot[plot 2,bar group size={2}{3}, magenta]
-    coordinates {(Exp. 6,148.2) (Exp. 7,152.2)};
-
-    \legend{Proposed Algorithm,Dynamic RR MLFQ, Static RR MLFQ, Dyn.
-SJFRR MLFQ of {b4},  Stat.
-SJFRR MLFQ of {b4}, Dyn.
-SJFRR MLFQ of {b5}, Stat.
-SJFRR MLFQ of {b5}, VMLFQ, MLFQ, PMLFQ, Dynamic SRBRR, Static RR}
-    \end{axis}
-\end{tikzpicture}
-\end{center}
-\caption{Comparison graph for average turnaround time}
-\vspace{45mm}
-\end{figure}
-
-\begin{figure}[H]
-    \begin{center}
-\begin{tikzpicture}
-    \begin{axis}[
-        width=0.475*\textwidth,
-        symbolic x coords={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
-        ylabel=Avg. Waiting Time,
-        enlargelimits=0.15,
-        legend style={at={(0.5,-0.25)}, anchor=north,legend columns=1},
-        ybar,
-        xtick={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
-        x tick label style={rotate=45,anchor=east},
-        bar width=3pt,
-        cycle list name=color list
-    ]
-
-    \addplot[plot 0,bar group size={0}{3}, red]
-    coordinates {(Exp. 1,68.8) (Exp. 2,68.8) (Exp. 3,88.7) (Exp. 6,62.4) (Exp. 7,63.4)};
-    \addplot[plot 1,bar group size={1}{3}, green]
-    coordinates {(Exp. 1,107.6)};
-    \addplot[plot 2,bar group size={2}{3}, cyan]
-    coordinates {(Exp. 1,116.2)};
-
-    \addplot[plot 1,bar group size={1}{3}, black]
-    coordinates {(Exp. 2,91.8)};
-    \addplot[plot 2,bar group size={2}{3}, brown]
-    coordinates {(Exp. 2,98.2)};
-
-    \addplot[plot 1,bar group size={1}{3}, teal]
-    coordinates {(Exp. 3,119)};
-    \addplot[plot 2,bar group size={2}{3}, violet]
-    coordinates {(Exp. 3,228)};
-
-    \addplot[plot 0,bar group size={0}{4}, red]
-    coordinates {(Exp. 4,140.14) (Exp. 5,161.75)};
-    \addplot[plot 1,bar group size={1}{4}, lime]
-    coordinates {(Exp. 4,170) (Exp. 5,225)};
-    \addplot[plot 2,bar group size={2}{4}, orange]
-    coordinates {(Exp. 4,175) (Exp. 5,240)};
-    \addplot[plot 3,bar group size={3}{4}, olive]
-    coordinates {(Exp. 4,180) (Exp. 5,245)};
-
-    \addplot[plot 1,bar group size={1}{3}, cyan]
-    coordinates {(Exp. 6,71.6) (Exp. 7,50.2)};
-    \addplot[plot 2,bar group size={2}{3}, magenta]
-    coordinates {(Exp. 6,97.2) (Exp. 7,108.8)};
-
-    \legend{Proposed Algorithm,Dynamic RR MLFQ, Static RR MLFQ, Dyn.
-SJFRR MLFQ of {b4},  Stat.
-SJFRR MLFQ of {b4}, Dyn.
-SJFRR MLFQ of {b5}, Stat.
-SJFRR MLFQ of {b5}, VMLFQ, MLFQ, PMLFQ, Dynamic SRBRR, Static RR}
-    \end{axis}
-\end{tikzpicture}
-\end{center}
-\caption{Comparison graph for average waiting time}
-\end{figure}
+for each benchmark we obtained wire length score and vias score for
+specific metal pitch and weight that used in score equation.we notice
+that our algorithm achieved wire-length score less than TripleZ with
+7.3\% and greater than NTUidRoute with 3.28\% in average.our vias
+score is less than TripleZ's score by 33.86\% so our total results
+is better than TripleZ's results in the two factors.wire length of
+our algorithm is greater than NTUidRoute due to that we attempted
+to minimize the total score combination of wire length and vias number
+so the total average score of our results is less than NTUidRoute's
+results.Decreasing wire length affect the vias number greatly so
+our vias score is less than NTUidRoute's vias score by 43\% due to that
+we try to decrease it as the vias is one of the sources of heat generation
+in the chip.
 

### 2020-06-01 paper.tex
Edit Abstract

@@
 \begin{abstract}
-    In this paper VLSI routing is improved by improving global routing, this can be done by using A-Star with a heuristic cost function that has parameters which affect the time taken by the router on changing instead of Dijkstra's algorithm in finding path, which will reduce the time taken in this process and achieve the minimum wire length, many comparisons are taken in this paper with different algorithms to find the optimum algorithm to be used to achieve both minimum wire length and minimum time taken.
-From the comparisons of the paper, we can find that using any algorithm is a trade-off as when the taken time is decreased, the wire length is increased and vice versa, so there is no algorithm which is better from the other algorithms in general but using A-Star algorithm with the heuristic function in finding the path is a good approach to be used in global routing as it decreases the routing time and achieves the minimum wire length.
+    In this paper VLSI routing is improved by improving global routing, this can be done by using A-Star with a heuristic cost function that has parameters which affect the time taken by the router instead of Dijkstra's algorithm in finding path, which will reduce the time taken in this process and achieve the minimum wire length, many comparisons are taken in this paper with different algorithms to find the optimum algorithm to be used to achieve both minimum wire length and minimum time taken.
+From the comparisons of the paper, we can find that global routing has a trade-off as when the taken time is decreased, the wire length, congestions, or vias count is increased and vice versa, so there is no algorithm which is better from the other algorithms in general but using A-Star algorithm with the heuristic function in finding the path is a good approach to be used in global routing as it decreases the routing time and achieves the minimum wire length.
 \end{abstract}

### 2020-06-01 Code/a_star/a_star.cpp
Final with paper

@@ -1,0 +1,186 @@
+#include <bits/stdc++.h>
+#include <thread>
+#include <pthread.h>
+using namespace std;
+
+int ROW, COL;
+typedef pair<int, int> ii;
+
+struct Grid
+{
+    ii parent = {-1, -1};
+    double f = FLT_MAX, g = FLT_MAX, h = FLT_MAX; // f = g + h
+};
+
+#define fi first
+#define se second
+#define mp make_pair
+typedef vector<vector<int>> VVI;
+typedef vector<vector<bool>> VVB;
+typedef vector<vector<Grid>> VVG;
+typedef pair<double, pair<int, int>> dii;
+
+auto is_valid = [](int r, int c) { return (r >= 0) && (r < ROW) && (c >= 0) && (c < COL); };
+auto not_blocked = [](VVI &grid, int r, int c) { return grid[r][c] != 0; };
+auto is_dst = [](int r, int c, ii dst) { return r == dst.fi && c == dst.se; };
+auto calc_h = [](int r, int c, ii dst) { return ((double)sqrt((r - dst.fi) * (r - dst.fi) + (c - dst.se) * (c - dst.se))); };
+
+vector<ii> pathVec;
+
+void get_path(const VVG &cells, ii dst)
+{
+    int r = dst.fi, c = dst.se;
+    stack<ii> path;
+    // partent (i, j)
+    while (!(cells[r][c].parent.fi == r && cells[r][c].parent.se == c))
+    {
+        path.push(mp(r, c));
+        int tmp_r = cells[r][c].parent.fi, tmp_c = cells[r][c].parent.se;
+        r = tmp_r, c = tmp_c;
+    }
+    path.push(mp(r, c)); // push source
+    while (!path.empty())
+    {
+        ii p = path.top();
+        path.pop();
+        pathVec.push_back({p.fi, p.se});
+    }
+}
+
+bool try_go_to(VVI &grid, int &i, int &j, int iNew, int jNew, VVG &cells, set<dii> &pq, VVB &visited, ii &dst)
+{
+    double fNew, hNew, gNew;
+    if (is_valid(iNew, jNew))
+    {
+        if (is_dst(iNew, jNew, dst))
+        {
+            cells[iNew][jNew].parent = {i, j};
+            get_path(cells, dst);
+            return true;
+        }
+        else if (!visited[iNew][jNew] && not_blocked(grid, iNew, jNew))
+        {
[…]

### 2020-06-01 Code/paper_code/src/gr_db/GrRouteGrid.cpp

@@ -1,0 +1,795 @@
+#include "GrRouteGrid.h"
+#include "db/Database.h"
+#include "GrDatabase.h"
+#include "db/Setting.h"
+
+namespace gr {
+void GrRouteGrid::init() {
+    int numLayers = database.getLayerNum();
+    routedWireMap.resize(numLayers);
+    fixedMetalMap.resize(numLayers);
+    histWireUsageMap.resize(numLayers);
+    routedViaMap.resize(numLayers);
+
+    GCellGrid::init();
+
+    for (int l = 0; l < numLayers; l++) {
+        auto dir = database.getLayerDir(l);
+        routedWireMap[l].resize(getNumGrPoint(dir), vector<UsageT>(getNumGrEdge(l)));
+        fixedMetalMap[l].resize(getNumGrPoint(dir), vector<std::pair<int, DBU>>(getNumGrEdge(l)));
+        histWireUsageMap[l].resize(getNumGrPoint(dir), vector<double>(getNumGrEdge(l), 0));
+        routedViaMap[l].resize(getNumGrPoint(X), vector<UsageT>(getNumGrPoint(Y)));
+    }
+
+    markFixedMetals();
+}
+
+void GrRouteGrid::clear() {
+    routedWireMap.clear();
+    fixedMetalMap.clear();
+    histWireUsageMap.clear();
+    routedViaMap.clear();
+}
+
+void GrRouteGrid::markFixed(int layerIdx, int gridline, int cp, int num_track, DBU avg_length) {
+    fixedMetalMap[layerIdx][gridline][cp] = std::make_pair(num_track, avg_length);
+}
+
+void GrRouteGrid::useWire(int layerIdx, int gridline, int cp, double usage) {
+    routedWireMap[layerIdx][gridline][cp] += usage;
+}
+
+void GrRouteGrid::useVia(int layerIdx, int x, int y, double usage) { routedViaMap[layerIdx][x][y] += usage; }
+
+void GrRouteGrid::useWire(const GrBoxOnLayer& box) {
+    int layerIdx = box.layerIdx;
+    auto dir = database.getLayerDir(layerIdx);
+    double usage = 1.0 / (box[dir].range() + 1);
+    for (int gridline = box[dir].low; gridline <= box[dir].high; gridline++)
+        for (int cp = box[1 - dir].low; cp < box[1 - dir].high; cp++) useWire(layerIdx, gridline, cp, usage);
+}
+
[…]

### 2020-06-01 Code/paper_code/src/single_net/MazeRoute.cpp

@@ -1,0 +1,202 @@
+#include "MazeRoute.h"
+
+ostream &operator<<(ostream &os, const Solution &sol) {
+    // modified
+    os << "cost=" << sol.g_cost << ", vertex=" << sol.vertex << ", prev=" << (sol.prev ? sol.prev->vertex : -1);
+    return os;
+}
+
+void MazeRoute::constructGridGraph(const vector<gr::GrBoxOnLayer> &guides) {
+    GuideGridGraphBuilder graphBuilder(grNet, graph, guides);
+    mergedPinAccessBoxes = grNet.getMergedPinAccessBoxes(
+        [](const gr::GrPoint &point) { return gr::PointOnLayer(point.layerIdx, point[X], point[Y]); });
+    graphBuilder.run(mergedPinAccessBoxes);
+}
+
+void MazeRoute::constructGridGraph(const CongestionMap &congMap) {
+    CoarseGridGraphBuilder graphBuilder(grNet, graph, congMap);
+    mergedPinAccessBoxes =
+        grNet.getMergedPinAccessBoxes([&](const gr::GrPoint &point) { return graphBuilder.grPointToPoint(point); });
+    graphBuilder.run(mergedPinAccessBoxes);
+}
+
+db::RouteStatus MazeRoute::run() {
+    vertexCosts.assign(graph.getNodeNum(), Costs(FLT_MAX, FLT_MAX, FLT_MAX));
+    pinSols.assign(mergedPinAccessBoxes.size(), nullptr);
+    const int startPin = 0;
+
+    auto status = route(startPin);
+    if (!db::isSucc(status)) {
+        return status;
+    }
+
+    getResult();
+
+    return status;
+}
+
+db::RouteStatus MazeRoute::route(int startPin) {
+    // define std::priority_queue
+    auto solComp = [](const std::shared_ptr<Solution> &lhs, const std::shared_ptr<Solution> &rhs) {
+        return rhs->f_cost < lhs->f_cost;
+    };
+    std::priority_queue<std::shared_ptr<Solution>, vector<std::shared_ptr<Solution>>, decltype(solComp)> solQueue(
+        solComp);
+
+    auto updateSol = [&](const std::shared_ptr<Solution> &sol) {
+        solQueue.push(sol);
+        if (sol->f_cost < vertexCosts[sol->vertex].f_cost)
[…]

### 2020-06-01 Code/paper_code/src/single_net/MazeRoute.h

@@ -1,0 +1,49 @@
+#pragma once
+
+#include "GridGraph.h"
+#include "multi_net/CongestionMap.h"
+
+class Solution {
+public:
+    db::CostT g_cost;
+    db::CostT f_cost;  // g_cost + h_cost
+    db::CostT h_cost;
+    int vertex;
+    std::shared_ptr<Solution> prev;
+
+    Solution(db::CostT gc, int v, const std::shared_ptr<Solution> &p)
+        : g_cost(gc), f_cost(FLT_MAX), vertex(v), prev(p) {}
+
+    Solution(db::CostT gc, db::CostT hc, db::CostT fc, int v, const std::shared_ptr<Solution> &p)
+        : g_cost(gc), h_cost(hc), f_cost(fc), vertex(v), prev(p) {}
+
+    friend ostream &operator<<(ostream &os, const Solution &sol);
+};
+
+class Costs {
+public:
+    db::CostT g_cost;
+    db::CostT f_cost;  // g_cost + h_cost
+    db::CostT h_cost;
+    Costs(db::CostT gc, db::CostT hc, db::CostT fc) : g_cost(gc), h_cost(hc), f_cost(fc) {}
+};
+class MazeRoute {
+public:
+    MazeRoute(gr::GrNet &grNetData) : grNet(grNetData) {}
+
+    void constructGridGraph(const vector<gr::GrBoxOnLayer> &guides);
+    void constructGridGraph(const CongestionMap &congMap);
+    db::RouteStatus run();
+
+private:
+    gr::GrNet &grNet;
+    GridGraph graph;
+
+    // h_cost first // f_cost second // min cost upper bound for each vertex
+    vector<Costs> vertexCosts;
+    vector<std::shared_ptr<Solution>> pinSols;  // best solution for each pin
+    vector<vector<gr::PointOnLayer>> mergedPinAccessBoxes;
+
+    db::RouteStatus route(int startPin);
+    void getResult();
+};

### 2020-06-01 Code/paper_code/test1_run.sh

@@ -1,0 +1,3 @@
+cd run/;
+./iccad19gr -lef ../toys/iccad2019c/ispd19_test1/ispd19_test1.input.lef -def ../toys/iccad2019c/ispd19_test1/ispd19_test1.input.def -output ispd18_test1.solution.guide -threads 8;
+cd ..;

### 2020-06-01 Code/paper_code/test2_run.sh

@@ -1,0 +1,3 @@
+cd run/;
+./iccad19gr -lef ../toys/iccad2019c/ispd19_test2/ispd19_test2.input.lef -def ../toys/iccad2019c/ispd19_test2/ispd19_test2.input.def -output ispd18_test2.solution.guide -threads 8;
+cd ..;

### 2020-06-01 Code/paper_code/test3_run.sh

@@ -1,0 +1,3 @@
+cd run/;
+./iccad19gr -lef ../toys/iccad2019c/ispd19_test3/ispd19_test3.input.lef -def ../toys/iccad2019c/ispd19_test3/ispd19_test3.input.def -output ispd18_test3.solution.guide -threads 8;
+cd ..;

### 2020-06-01 Code/paper_code/test4_run.sh

@@ -1,0 +1,3 @@
+cd run/;
+./iccad19gr -lef ../toys/iccad2019c/ispd19_test4/ispd19_test4.input.lef -def ../toys/iccad2019c/ispd19_test4/ispd19_test4.input.def -output ispd18_test4.solution.guide -threads 8;
+cd ..;

### 2020-06-01 Code/paper_code/test5_run.sh

@@ -1,0 +1,3 @@
+cd run/;
+./iccad19gr -lef ../toys/iccad2019c/ispd19_test5/ispd19_test5.input.lef -def ../toys/iccad2019c/ispd19_test5/ispd19_test5.input.def -output ispd18_test5.solution.guide -threads 8;
+cd ..;

### 2020-06-01 Code/paper_code/test6_run.sh

@@ -1,0 +1,3 @@
+cd run/;
+./iccad19gr -lef ../toys/iccad2019c/ispd19_test6/ispd19_test6.input.lef -def ../toys/iccad2019c/ispd19_test6/ispd19_test6.input.def -output ispd18_test6.solution.guide -threads 8;
+cd ..;

### 2020-06-01 Code/paper_code/test7_run.sh

@@ -1,0 +1,3 @@
+cd run/;
+./iccad19gr -lef ../toys/iccad2019c/ispd19_test7/ispd19_test7.input.lef -def ../toys/iccad2019c/ispd19_test7/ispd19_test7.input.def -output ispd18_test7.solution.guide -threads 8;
+cd ..;

### 2020-06-01 Code/paper_code/test8_run.sh

@@ -1,0 +1,3 @@
+cd run/;
+./iccad19gr -lef ../toys/iccad2019c/ispd19_test8/ispd19_test8.input.lef -def ../toys/iccad2019c/ispd19_test8/ispd19_test8.input.def -output ispd18_test8.solution.guide -threads 8;
+cd ..;

### 2020-06-01 code/A_Star_Algorithm/a_star.cpp

@@ -1,143 +1,0 @@
-#include <bits/stdc++.h>
-#include <thread>
-#include <pthread.h>
-using namespace std;
-
-int ROW, COL;
-typedef pair<int, int> ii;
-
-struct Grid
-{
-    ii parent = {-1, -1};
-    double f = FLT_MAX, g = FLT_MAX, h = FLT_MAX; // f = g + h
-};
-
-#define fi first
-#define se second
-#define mp make_pair
-typedef vector<vector<int>> VVI;
-typedef vector<vector<bool>> VVB;
-typedef vector<vector<Grid>> VVG;
-typedef pair<double, pair<int, int>> dii;
-
-auto is_valid = [](int r, int c) { return (r >= 0) && (r < ROW) && (c >= 0) && (c < COL); };
-auto not_blocked = [](VVI &grid, int r, int c) { return grid[r][c] != 0; };
-auto is_dst = [](int r, int c, ii dst) { return r == dst.fi && c == dst.se; };
-auto calc_h = [](int r, int c, ii dst) { return ((double)sqrt((r - dst.fi) * (r - dst.fi) + (c - dst.se) * (c - dst.se))); };
-
-void get_path(const VVG &cells, ii dst)
-{
-    printf("Path: ");
-    int r = dst.fi, c = dst.se;
-    stack<ii> path;
-    // partent (i, j)
-    while (!(cells[r][c].parent.fi == r && cells[r][c].parent.se == c))
-    {
-        path.push(mp(r, c));
-        int tmp_r = cells[r][c].parent.fi, tmp_c = cells[r][c].parent.se;
-        r = tmp_r, c = tmp_c;
-    }
-    path.push(mp(r, c)); // push source
-    while (!path.empty())
-    {
-        ii p = path.top();
-        path.pop();
-        printf("(%d,%d) ", p.fi, p.se);
-    }
-    printf("\n");
-}
-
-bool try_go_to(VVI &grid, int &i, int &j, int iNew, int jNew, VVG &cells, set<dii> &pq, VVB &visited, ii &dst)
-{
-    double fNew, hNew, gNew;
-    if (is_valid(iNew, jNew))
-    {
-        if (is_dst(iNew, jNew, dst))
-        {
-            cells[iNew][jNew].parent = {i, j};
-            get_path(cells, dst);
-            return true;
-        }
-        else if (!visited[iNew][jNew] && not_blocked(grid, iNew, jNew))
-        {
[…]

### 2020-06-01 code/cu-gr/build.sh

@@ -1,1 +1,0 @@
-scripts/build.py -o release;

### 2020-06-01 code/cu-gr/sample_run.sh

@@ -1,3 +1,0 @@
-cd run/;
-./iccad19gr -lef ../toys/iccad2019c/ispd18_sample/ispd18_sample.input.lef -def ../toys/iccad2019c/ispd18_sample/ispd18_sample.input.def -output ispd18_test1.solution.guide -threads 20;
-cd ..;

### 2020-06-01 code/cu-gr/src/single_net/MazeRoute.cpp

@@ -1,192 +1,0 @@
-#include "MazeRoute.h"
-
-ostream &operator<<(ostream &os, const Solution &sol) {
-    // modified
-    os << "cost=" << sol.g_cost << ", vertex=" << sol.vertex << ", prev=" << (sol.prev ? sol.prev->vertex : -1);
-    return os;
-}
-
-void MazeRoute::constructGridGraph(const vector<gr::GrBoxOnLayer> &guides) {
-    GuideGridGraphBuilder graphBuilder(grNet, graph, guides);
-    mergedPinAccessBoxes = grNet.getMergedPinAccessBoxes(
-        [](const gr::GrPoint &point) { return gr::PointOnLayer(point.layerIdx, point[X], point[Y]); });
-    graphBuilder.run(mergedPinAccessBoxes);
-}
-
-void MazeRoute::constructGridGraph(const CongestionMap &congMap) {
-    CoarseGridGraphBuilder graphBuilder(grNet, graph, congMap);
-    mergedPinAccessBoxes =
-        grNet.getMergedPinAccessBoxes([&](const gr::GrPoint &point) { return graphBuilder.grPointToPoint(point); });
-    graphBuilder.run(mergedPinAccessBoxes);
-}
-
-db::RouteStatus MazeRoute::run() {
-    vertexCosts.assign(graph.getNodeNum(), Costs(FLT_MAX, FLT_MAX, FLT_MAX));
-    pinSols.assign(mergedPinAccessBoxes.size(), nullptr);
-    const int startPin = 0;
-
-    auto status = route(startPin);
-    if (!db::isSucc(status)) {
-        return status;
-    }
-
-    getResult();
-
-    return status;
-}
-
-db::RouteStatus MazeRoute::route(int startPin) {
-    // define std::priority_queue
-    auto solComp = [](const std::shared_ptr<Solution> &lhs, const std::shared_ptr<Solution> &rhs) {
-        return rhs->f_cost < lhs->f_cost;
-    };
-    std::priority_queue<std::shared_ptr<Solution>, vector<std::shared_ptr<Solution>>, decltype(solComp)> solQueue(
-        solComp);
-
-    auto updateSol = [&](const std::shared_ptr<Solution> &sol) {
-        solQueue.push(sol);
-        if (sol->f_cost < vertexCosts[sol->vertex].f_cost)
[…]

### 2020-06-01 code/cu-gr/src/single_net/MazeRoute.h

@@ -1,49 +1,0 @@
-#pragma once
-
-#include "GridGraph.h"
-#include "multi_net/CongestionMap.h"
-
-class Solution {
-public:
-    db::CostT g_cost;
-    db::CostT f_cost;  // g_cost + h_cost
-    db::CostT h_cost;
-    int vertex;
-    std::shared_ptr<Solution> prev;
-
-    Solution(db::CostT gc, int v, const std::shared_ptr<Solution> &p)
-        : g_cost(gc), f_cost(FLT_MAX), vertex(v), prev(p) {}
-
-    Solution(db::CostT gc, db::CostT hc, db::CostT fc, int v, const std::shared_ptr<Solution> &p)
-        : g_cost(gc), h_cost(hc), f_cost(fc), vertex(v), prev(p) {}
-
-    friend ostream &operator<<(ostream &os, const Solution &sol);
-};
-
-class Costs {
-public:
-    db::CostT g_cost;
-    db::CostT f_cost;  // g_cost + h_cost
-    db::CostT h_cost;
-    Costs(db::CostT gc, db::CostT hc, db::CostT fc) : g_cost(gc), h_cost(hc), f_cost(fc) {}
-};
-class MazeRoute {
-public:
-    MazeRoute(gr::GrNet &grNetData) : grNet(grNetData) {}
-
-    void constructGridGraph(const vector<gr::GrBoxOnLayer> &guides);
-    void constructGridGraph(const CongestionMap &congMap);
-    db::RouteStatus run();
-
-private:
-    gr::GrNet &grNet;
-    GridGraph graph;
-
-    // h_cost first // f_cost second // min cost upper bound for each vertex
-    vector<Costs> vertexCosts;
-    vector<std::shared_ptr<Solution>> pinSols;  // best solution for each pin
-    vector<vector<gr::PointOnLayer>> mergedPinAccessBoxes;
-
-    db::RouteStatus route(int startPin);
-    void getResult();
-};

### 2020-06-01 code/cu-gr/test1_run.sh

@@ -1,3 +1,0 @@
-cd run/;
-./iccad19gr -lef ../toys/iccad2019c/ispd18_sample/ispd18_test1.input.lef -def ../toys/iccad2019c/ispd18_sample/ispd18_test1.input.def -output ispd18_test1.solution.guide -threads 1;
-cd ..;

### 2020-06-01 code/cu-gr/test2_run.sh

@@ -1,3 +1,0 @@
-cd run/;
-./iccad19gr -lef ../toys/iccad2019c/ispd18_sample/ispd18_test2.input.lef -def ../toys/iccad2019c/ispd18_sample/ispd18_test2.input.def -output ispd18_test2.solution.guide -threads 1;
-cd ..;

### 2020-06-01 code/cu-gr/test3_run.sh

@@ -1,3 +1,0 @@
-cd run/;
-./iccad19gr -lef ../toys/iccad2019c/ispd18_sample/ispd18_test3.input.lef -def ../toys/iccad2019c/ispd18_sample/ispd18_test3.input.def -output ispd18_test3.solution.guide -threads 1;
-cd ..;

### 2020-06-01 code/cu-gr/test4_run.sh

@@ -1,3 +1,0 @@
-cd run/;
-./iccad19gr -lef ../toys/iccad2019c/ispd18_sample/ispd18_test4.input.lef -def ../toys/iccad2019c/ispd18_sample/ispd18_test4.input.def -output ispd18_test4.solution.guide -threads 1;
-cd ..;
